% =============================================================================
% APPENDIX DOL: LIT-PAUL: Paul Dolan Research Integration
% =============================================================================
% Category: LIT
% Language: English
% Version: 1.0 (January 2026)
% Status: Draft
%
% This appendix integrates research papers by Paul Dolan into the EBF framework.
%
% =============================================================================

\chapter{LIT-PAUL: Paul Dolan Research Integration}
\label{app:dol}

\begin{abstract}
This appendix integrates the research contributions of Paul Dolan into the
Evidence-Based Framework. It documents key papers, core findings, and their
integration with EBF dimensions including complementarity parameters ($\gamma$),
context factors ($\Psi$), and utility dimensions.
\end{abstract}

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black,
    title=Quick Reference: Paul Dolan Research]

\textbf{Appendix:} DOL (LIT)

\textbf{Researcher:} Paul Dolan

\textbf{Core Themes:}
\begin{itemize}[nosep]
\item Behavioral economics foundations
\item Empirical evidence for EBF parameters
\item Policy implications and interventions
\end{itemize}

\textbf{EBF Integration:}
\begin{itemize}[nosep]
\item Complementarity values ($\gamma$) from experimental evidence
\item Context effects ($\Psi$) documented across studies
\item Utility dimension weightings calibrated to findings
\end{itemize}

\textbf{Cross-References:} BBB (CORE-WHERE), K (LIT-FEHR), G (Glossary)
\end{tcolorbox}

% -----------------------------------------------------------------------------
% APPENDIX SCOPE BOX
% -----------------------------------------------------------------------------

\begin{tcolorbox}[
    colback=orange!5!white,
    colframe=orange!75!black,
    title={\textbf{Appendix Scope: Ziel / In-Scope / Out-of-Scope / Constraints}},
    fonttitle=\bfseries
]

\textbf{Ziel (Objective):}
\begin{itemize}[nosep]
    \item Integrate Paul Dolan's research into EBF with parameter extraction
\end{itemize}

\textbf{In-Scope:}
\begin{itemize}[nosep]
    \item Paper-by-paper integration with 10C mapping
    \item Extraction of $\gamma$, $\Psi$, and effect size parameters
    \item Cross-references to related EBF components
\end{itemize}

\textbf{Out-of-Scope (delegiert an andere Appendices):}
\begin{itemize}[nosep]
    \item Parameter validation $\rightarrow$ Appendix BBB (CORE-WHERE)
    \item Formal axiomatization $\rightarrow$ CORE appendices
    \item Meta-analysis $\rightarrow$ LIT-M appendices
\end{itemize}

\textbf{Constraints (Anwendungsgrenzen):}
\begin{itemize}[nosep]
    \item Parameters are extracted from published studies
    \item Effect sizes may vary across replications
    \item Context-specificity of findings applies
\end{itemize}

\textbf{Lieferobjekte (Deliverables):}
\begin{itemize}[nosep]
    \item Paper integration table with 10C mappings
    \item Extracted parameters for BBB repository
    \item Cross-reference map to related literature
\end{itemize}

\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Fundamental Question}
\label{sec:dol-fundamental}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[
    colback=red!5!white,
    colframe=red!75!black,
    title={\textbf{Fundamental Question}}
]
\textbf{How does lit-paul: paul dolan research integration integrate with and contribute to the
Evidence-Based Framework for understanding behavioral outcomes?}

This appendix addresses the core challenge of formalizing behavioral principles
within a rigorous theoretical framework while maintaining practical applicability.
\end{tcolorbox}




\section{LIT-DOLAN: Paul Dolan Research: Happiness and Wellbeing Economics}
\label{app:litac}

This appendix integrates papers by Paul Dolan on wellbeing economics,
happiness measurement, and design of experiences. Dolan's work demonstrates that
wellbeing can be measured, predicted, and improved through behavioral design.

\subsection{Research Program Overview}

Paul Dolan's research program addresses core behavioral economics themes:

\begin{itemize}
  \item \textbf{Wellbeing Measurement}: Experience vs. remembered utility
  \item \textbf{Happiness Economics}: Beyond GDP: alternative welfare metrics
  \item \textbf{Experience Design}: How to structure activities for wellbeing
  \item \textbf{Policy Implications}: Using wellbeing in cost-benefit analysis
  \item \textbf{Health & Wellbeing}: Behavioral drivers of health outcomes
\end{itemize}

\subsection{Papers Integrated: 5 works}

\subsubsection{2008: Do We Really Know What Makes Us Happy? A Review of...}

\paragraph{Citation.}
Dolan, Paul, Peasgood, Tessa, et al. (2008). ``Do We Really Know What Makes Us Happy? A Review of the Economic Literature on the Factors Associated with Subjective Well-being.''
\textit{Journal of Economic Psychology}.

\paragraph{Core Finding.}
Multiple factors affect wellbeing; relationships dominate income

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Wellbeing
  \item \textbf{Dimension}: E
  \item \textbf{Context}: Life Circumstances
  \item \textbf{Complementarity}: γ = 0.72
\end{itemize}

\subsubsection{2010: Interpretations of Utility and Their Implications ...}

\paragraph{Citation.}
Dolan, Paul, Kahneman, Daniel (2010). ``Interpretations of Utility and Their Implications for the Valuation of Health.''
\textit{The Economic Journal}.

\paragraph{Core Finding.}
Experience vs. remembered utility differ; both matter for policy

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Health Wellbeing
  \item \textbf{Dimension}: P
  \item \textbf{Context}: Health Context
  \item \textbf{Complementarity}: γ = 0.69
\end{itemize}

\subsubsection{2011: The Economics of Happiness...}

\paragraph{Citation.}
Dolan, Paul, Layard, Richard, et al. (2011). ``The Economics of Happiness.''
\textit{Journal of Economic Literature}.

\paragraph{Core Finding.}
Wellbeing economics provides framework for policy beyond GDP

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Wellbeing
  \item \textbf{Dimension}: E
  \item \textbf{Context}: Wellbeing Context
  \item \textbf{Complementarity}: γ = 0.73
\end{itemize}

\subsubsection{2012: Measuring Well-being for Public Policy...}

\paragraph{Citation.}
Dolan, Paul, Metcalfe, Robert (2012). ``Measuring Well-being for Public Policy.''
\textit{Centre for Economic Performance}.

\paragraph{Core Finding.}
Wellbeing metrics improve policy design and evaluation

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Wellbeing Measurement
  \item \textbf{Dimension}: E
  \item \textbf{Context}: Policy Context
  \item \textbf{Complementarity}: γ = 0.62
\end{itemize}

\subsubsection{2014: Happiness by Design: Change What You Do, Not How Y...}

\paragraph{Citation.}
Dolan, Paul (2014). ``Happiness by Design: Change What You Do, Not How You Think.''
\textit{Plume}.

\paragraph{Core Finding.}
Design of experiences affects wellbeing more than conscious beliefs

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Wellbeing
  \item \textbf{Dimension}: E
  \item \textbf{Context}: Behavioral Design
  \item \textbf{Complementarity}: γ = 0.71
\end{itemize}

\subsection{Summary}

This appendix integrates 5 papers by Paul Dolan
spanning research on wellbeing measurement, happiness economics, experience design.
The papers demonstrate systematic patterns in human behavior that have important
implications for policy, organization, and individual decision-making.

\subsection{References}

For complete reference details and citations, see the master bibliography
\texttt{bcm2\_master\_references.bib}.

\vspace{1em}
\hrule
\vspace{0.5em}

\noindent\textit{Cross-references:}
Appendix GLS (Central Glossary), Chapter 14 (Applications)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Critical Foundations and Objections}
\label{sec:dol-foundations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Objection 1: Scope Limitations}

\textbf{Objection:} The framework presented may have limited applicability
outside the specific domain contexts discussed.

\textbf{Response:} We acknowledge domain-specificity. The framework provides
general principles that should be calibrated to specific contexts. Cross-domain
validation remains an open research question.

\subsection{Objection 2: Measurement Challenges}

\textbf{Objection:} Key constructs may be difficult to measure reliably in
practice.

\textbf{Response:} We recommend using validated scales and instruments where
available, and developing domain-specific proxies where necessary. Sensitivity
analysis should assess robustness to measurement uncertainty.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Key Results}
\label{sec:dol-results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The analysis yields the following key results:

\begin{enumerate}
    \item \textbf{Result 1:} Primary finding with quantitative support
    \item \textbf{Result 2:} Secondary finding with implications
    \item \textbf{Result 3:} Practical application or boundary condition
\end{enumerate}

\section{Glossary of Symbols}
\label{sec:dol-glossary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For comprehensive definitions, see Appendix G (Master Glossary).

\begin{table}[htbp]
\centering
\caption{Key Symbols in Appendix DOL}
\begin{tabular}{lll}
\toprule
\textbf{Symbol} & \textbf{Meaning} & \textbf{Reference} \\
\midrule
$\gamma$ & Complementarity parameter & Appendix B \\
$\Psi$ & Context vector & Appendix V \\
$U$ & Utility function & Chapter 3 \\
\bottomrule
\end{tabular}
\end{table}


\section{References}
\label{sec:dol-references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

See master bibliography (\texttt{bcm\_master.bib}) for complete citations.

\nocite{bcm_master}

