% =============================================================================
% APPENDIX REF-APPLY: The EBF Workflow Reference
% =============================================================================
% Module: BCM2_REF_APPLY
% Version: 1.0 (January 2026)
% Status: Draft
% Category: REF (Reference Material)
%
% This appendix provides the operational workflow for applying EBF. While the
% 9C CORE appendices define WHAT EBF is conceptually (WHO, WHAT, HOW, WHEN,
% WHERE, AWARE, READY, STAGE), REF-APPLY provides practical guidance on
% HOW to use EBF to generate knowledge, make decisions, and improve practice.
%
% NOTE: This is a REF (Reference) appendix, not a CORE appendix.
% The 8th CORE is STAGE (Behavioral Change Journey, Appendix AW).
%
% =============================================================================

% =============================================================================
% CROSS-REFERENCE STRUCTURE
% =============================================================================
%
% DEPENDS ON:
%   - Appendix AAA (WHO): Welfare hierarchy for stakeholder identification
%   - Appendix B (HOW): Complementarity structure
%   - Appendix C (WHAT): Utility dimensions
%   - Appendix V (WHEN): Context dimensions
%   - Appendix BBB (WHERE): Parameter estimation
%   - Appendix AU (AWARE): Awareness modeling
%   - Appendix AV (READY): Willingness modeling
%   - Appendix G (Glossary): Symbol definitions
%
% REQUIRED BY:
%   - All domain appendices (DOMAIN-*)
%   - LIT-META (scientific instantiation)
%   - All applied EBF work
%
% =============================================================================

\chapter{REF-APPLY: The EBF Workflow Reference}
\label{app:ref-apply}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
This reference appendix provides the operational workflow for applying the
Evidence-Based Framework (EBF). While the eight CORE appendices (WHO, WHAT, HOW,
WHEN, WHERE, AWARE, READY, STAGE) define \textit{what} EBF is conceptually,
REF-APPLY provides practical guidance on \textit{how} to use EBF in practice.
The eight-phase workflow transforms EBF from static theory into living, iterative
knowledge production. Core principles include: derive (don't invent), pre-register
(don't p-hack), track (don't hide), and iterate (don't finalize). Domain-specific
instantiations are provided for scientific research, business practice, and policy-making.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUICK REFERENCE BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black,
    title=\textbf{Quick Reference: The EBF Application Process}]

\textbf{The 8 Phases:}
\begin{enumerate}[nosep]
    \item Problem $\to$ Framework Module
    \item Model Derivation (not invention)
    \item Pre-Registration
    \item Parametrization
    \item Prediction + Publication
    \item Verification
    \item Version-Controlled Iteration
    \item Permanent Prediction Tracking
\end{enumerate}

\textbf{Core Principles:}
\begin{itemize}[nosep]
    \item \textbf{Derive:} Models come from framework, not imagination
    \item \textbf{Pre-register:} Hypotheses before data
    \item \textbf{Track:} Predictions monitored permanently
    \item \textbf{Iterate:} Living documents, not final products
\end{itemize}

\textbf{The Meta-Question:}
\begin{center}
\textit{How do I operationally apply the 9C CORE to generate knowledge?}
\end{center}

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 1: MOTIVATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Motivation: The Gap Between Theory and Practice}
\label{sec:apply-motivation}

The eight CORE appendices (9C) define EBF conceptually:

\begin{center}
\begin{tabular}{@{}clll@{}}
\toprule
\textbf{CORE} & \textbf{Code} & \textbf{Question} & \textbf{Appendix} \\
\midrule
1 & WHO & Who has welfare? & AAA \\
2 & WHAT & What is utility? & C \\
3 & HOW & How do agents interact? & B \\
4 & WHEN & When does context matter? & V \\
5 & WHERE & Where do parameters come from? & BBB \\
6 & AWARE & How aware are agents? & AU \\
7 & READY & How ready to act? & AV \\
8 & STAGE & Where in the change journey? & AW \\
\bottomrule
\end{tabular}
\end{center}

\textbf{The Problem:} Knowing \textit{what} EBF is does not automatically tell
practitioners \textit{how} to use it. The gap between conceptual understanding
and operational application is where most frameworks fail.

\textbf{The Solution:} This reference appendix (REF-APPLY) provides the process---the
workflow, principles, templates, and feedback architecture---that transforms EBF
from theory into practice.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 2: THE GENERIC WORKFLOW
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Generic EBF Workflow: Eight Phases}
\label{sec:apply-workflow}

The EBF application process consists of eight phases. This workflow is
\textit{generic}---it applies to all domains (science, business, policy).
Domain-specific instantiations are provided in Section~\ref{sec:apply-domains}.

\subsection{Phase 1: Problem $\to$ Framework Module}

\textbf{Traditional approach:} Invent a new model for each problem.

\textbf{EBF approach:} Identify which framework module(s) address the problem.

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black,
    title=\textbf{Phase 1 Checklist}]
\begin{enumerate}[nosep]
    \item State the problem clearly
    \item Identify the relevant CORE question(s):
    \begin{itemize}[nosep]
        \item Is this about WHO (stakeholders, levels)?
        \item Is this about WHAT (utility dimensions)?
        \item Is this about HOW (interactions, complementarity)?
        \item Is this about WHEN (context-dependence)?
        \item Is this about WHERE (parameter estimation)?
        \item Is this about AWARE (information, beliefs)?
        \item Is this about READY (willingness, thresholds)?
    \end{itemize}
    \item Map to specific appendices
    \item Review existing work in those appendices
\end{enumerate}
\end{tcolorbox}

\subsection{Phase 2: Model Derivation (Not Invention)}

\textbf{Traditional approach:} Construct a novel model with custom assumptions.

\textbf{EBF approach:} Derive a model by specifying framework parameters.

The general EBF model form:
\begin{equation}
U_i = \sum_d w_d \cdot u_d(x_d, \Psi) + \sum_{j \neq i} C_{ij} \cdot U_j
\label{eq:general-ebf}
\end{equation}

\textbf{Derivation} means specifying:
\begin{itemize}[nosep]
    \item Which dimensions $d$ from FEPSDE (Financial, Emotional, Physical, Social, Development, Existential)?
    \item Which context dimensions $\Psi$ (the 8 from Appendix V)?
    \item Which complementarities $C_{ij}$ are non-zero?
    \item Which level $L$ (individual, group, organization, society)?
    \item What functional forms for $u_d(\cdot)$?
\end{itemize}

\begin{tcolorbox}[colback=green!5!white, colframe=green!75!black,
    title=\textbf{Key Insight: Derivation vs. Invention}]

\textbf{Invention} creates new theory for each problem $\to$ fragmentation, inconsistency.

\textbf{Derivation} instantiates shared framework $\to$ cumulation, comparability.

Every EBF model is a special case of Equation~\ref{eq:general-ebf}. This ensures
consistency across applications and enables meta-analysis.

\end{tcolorbox}

\subsection{Phase 3: Pre-Registration}

\textbf{Traditional approach:} Analyze data, then formulate hypotheses (p-hacking, HARKing).

\textbf{EBF approach:} Register hypotheses \textit{before} data collection.

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black,
    title=\textbf{Phase 3: Pre-Registration Template}]

\textbf{Required elements:}
\begin{enumerate}[nosep]
    \item \textbf{Hypotheses} (derived from model in Phase 2)
    \item \textbf{Quantitative predictions} (point estimates + confidence intervals)
    \item \textbf{Data source} (specified before collection)
    \item \textbf{Analysis method} (fixed, not exploratory)
    \item \textbf{Success/failure criteria} (explicit, falsifiable)
\end{enumerate}

\textbf{Registration platforms:}
\begin{itemize}[nosep]
    \item Scientific: OSF, AsPredicted, arXiv
    \item Business: Internal prediction markets, documented forecasts
    \item Policy: Public commitments, registered reports
\end{itemize}

\end{tcolorbox}

\subsection{Phase 4: Parametrization}

\textbf{Traditional approach:} Collect data, estimate parameters, report results.

\textbf{EBF approach:} Multiple estimation methods with uncertainty quantification.

\textbf{Parameter sources:}
\begin{enumerate}[nosep]
    \item Traditional empirical methods (experiments, surveys, observational data)
    \item LLM-MC estimation (Appendix AN)
    \item Meta-analysis of existing studies
    \item Bayesian updating from prior EBF applications
    \item Expert elicitation with proper uncertainty
\end{enumerate}

\textbf{Requirements:}
\begin{itemize}[nosep]
    \item Point estimates with confidence intervals
    \item Sensitivity analysis
    \item Robustness checks across methods
    \item Documentation of estimation choices
\end{itemize}

\subsection{Phase 5: Prediction + Publication}

\textbf{Traditional approach:} Submit to journal, wait 5-7 years, publish once.

\textbf{EBF approach:} Immediate publication with quantitative predictions.

\textbf{Publication package:}
\begin{itemize}[nosep]
    \item Preprint (immediate dissemination)
    \item Code repository (reproducibility)
    \item Data repository (transparency)
    \item Pre-registration link (credibility)
    \item Prediction table (falsifiability)
\end{itemize}

\textbf{Prediction format:}
\begin{center}
\small
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Prediction} & \textbf{Point Estimate} & \textbf{95\% CI} & \textbf{Evaluation Date} \\
\midrule
[Outcome 1] & [Value] & [Lower, Upper] & [Date] \\
[Outcome 2] & [Value] & [Lower, Upper] & [Date] \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Phase 6: Verification}

\textbf{Traditional approach:} 2-3 anonymous reviewers, 6-24 months, no replication.

\textbf{EBF approach:} Automated verification + community review.

\textbf{Verification layers:}
\begin{enumerate}[nosep]
    \item \textbf{Automated code replication} (runs within hours)
    \item \textbf{Statistical checks} (automated diagnostics)
    \item \textbf{Logic verification} (AI-assisted consistency checks)
    \item \textbf{Community feedback} (public comments, GitHub issues)
    \item \textbf{Formal peer review} (optional, for journal submission)
\end{enumerate}

\subsection{Phase 7: Version-Controlled Iteration}

\textbf{Traditional approach:} Publish once, never update (errors remain forever).

\textbf{EBF approach:} Living documents with version control.

\begin{verbatim}
v1.0 (Initial release)
  → v1.1 (Community feedback incorporated)
    → v1.2 (Minor corrections)
      → v2.0 (Major revision based on new evidence)
\end{verbatim}

\textbf{Version control requirements:}
\begin{itemize}[nosep]
    \item Changelog documented for each version
    \item All versions citable (DOI-stable)
    \item New predictions registered with each update
    \item Clear indication of what changed and why
\end{itemize}

\subsection{Phase 8: Permanent Prediction Tracking}

\textbf{Traditional approach:} Publish and forget. No accountability for predictions.

\textbf{EBF approach:} Predictions tracked until resolution.

\textbf{Prediction Tracking Dashboard:}
\begin{center}
\small
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Prediction} & \textbf{Predicted} & \textbf{Observed} & \textbf{Eval. Date} & \textbf{Status} \\
\midrule
[Prediction 1] & [Value $\pm$ CI] & [Actual] & [Date] & $\checkmark$ / $\times$ / $\circlearrowright$ \\
[Prediction 2] & [Value $\pm$ CI] & --- & [Date] & $\circlearrowright$ Tracking \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Status codes:}
\begin{itemize}[nosep]
    \item $\checkmark$ Confirmed (within CI)
    \item $\times$ Refuted (outside CI) $\to$ triggers model revision
    \item $\circlearrowright$ Tracking (not yet evaluated)
\end{itemize}

\begin{tcolorbox}[colback=red!5!white, colframe=red!75!black,
    title=\textbf{Critical Principle: Refutation $\to$ Revision, Not Concealment}]

When predictions fail:
\begin{enumerate}[nosep]
    \item Document the failure publicly
    \item Analyze why the prediction failed
    \item Update the model accordingly
    \item Register new predictions
    \item Track the updated predictions
\end{enumerate}

Hiding failed predictions is antithetical to EBF. Failures are \textit{data}
for framework improvement, not embarrassments to conceal.

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 3: CORE PRINCIPLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Core Principles}
\label{sec:apply-principles}

The EBF application process is governed by four core principles:

\subsection{Principle 1: Derive, Don't Invent}

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black]
\textbf{Every model should be derivable from the EBF framework.}

If you find yourself inventing new constructs not in EBF, either:
\begin{enumerate}[nosep]
    \item You've identified a gap in EBF (propose an extension)
    \item You're overcomplicating (simplify to framework elements)
    \item The problem isn't suited for EBF (rare, but possible)
\end{enumerate}
\end{tcolorbox}

\subsection{Principle 2: Pre-Register, Don't P-Hack}

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black]
\textbf{Hypotheses must be specified before data.}

This eliminates:
\begin{itemize}[nosep]
    \item P-hacking (torturing data until $p < 0.05$)
    \item HARKing (Hypothesizing After Results Known)
    \item Selective reporting (hiding null results)
\end{itemize}
\end{tcolorbox}

\subsection{Principle 3: Track, Don't Hide}

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black]
\textbf{All predictions are tracked permanently.}

The prediction tracking dashboard is not optional. Every EBF application
must specify falsifiable predictions and track them until resolution.
\end{tcolorbox}

\subsection{Principle 4: Iterate, Don't Finalize}

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black]
\textbf{Documents are living, not finished.}

Traditional: Paper $\to$ Publication $\to$ THE END

EBF: Document $\to$ v1.0 $\to$ Feedback $\to$ v1.1 $\to$ ... $\to$ v$n$ $\to$ ...

There is no ``final'' version, only the current best version.
\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 4: THE FEEDBACK ARCHITECTURE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Feedback Architecture}
\label{sec:apply-feedback}

Unlike traditional research (linear, terminal), EBF research is circular
with permanent feedback loops.

\subsection{The Feedback Loop}

\begin{center}
\begin{tikzpicture}[node distance=2cm, auto]
    % Nodes
    \node[draw, rectangle, rounded corners] (problem) {Problem};
    \node[draw, rectangle, rounded corners, right of=problem, xshift=1.5cm] (model) {Model};
    \node[draw, rectangle, rounded corners, right of=model, xshift=1.5cm] (predict) {Prediction};
    \node[draw, rectangle, rounded corners, below of=predict, yshift=-0.5cm] (observe) {Observation};
    \node[draw, rectangle, rounded corners, below of=model, yshift=-0.5cm] (compare) {Compare};
    \node[draw, rectangle, rounded corners, below of=problem, yshift=-0.5cm] (update) {Update};

    % Arrows
    \draw[->] (problem) -- (model);
    \draw[->] (model) -- (predict);
    \draw[->] (predict) -- (observe);
    \draw[->] (observe) -- (compare);
    \draw[->] (compare) -- (update);
    \draw[->] (update) -- (problem);
\end{tikzpicture}
\end{center}

\subsection{Feedback Types}

\begin{table}[htbp]
\centering
\caption{Feedback Types and Responses}
\label{tab:feedback-types}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Feedback Type} & \textbf{Trigger} & \textbf{Response} & \textbf{Timescale} \\
\midrule
Prediction miss & Observation $\notin$ CI & Recalibrate parameters & Days--Weeks \\
Replication failure & Code doesn't reproduce & Fix code/document error & Hours \\
Logical inconsistency & Internal contradiction & Revise model & Days \\
New evidence & External study published & Bayesian update & Weeks \\
Paradigm anomaly & Accumulated failures & Framework extension & Months \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The Permanent Monitoring Layer}

For mature EBF applications, automated monitoring tracks predictions continuously:

\begin{enumerate}[nosep]
    \item \textbf{Prediction Tracker:} Monitors registered predictions against incoming data
    \item \textbf{Replication Bot:} Periodically re-runs code to verify reproducibility
    \item \textbf{Anomaly Detector:} Flags unexpected patterns that may indicate model failure
    \item \textbf{Alert System:} Notifies when predictions resolve or anomalies appear
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 5: DOMAIN INSTANTIATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Domain Instantiations}
\label{sec:apply-domains}

The generic workflow instantiates differently across domains:

\subsection{Scientific Research}

\textbf{Detailed in:} Appendix LIT-META, Section ``The EBF Research Workflow''

\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Phase} & \textbf{Generic} & \textbf{Scientific Instantiation} \\
\midrule
1 & Problem $\to$ Module & Research question $\to$ Literature \\
2 & Derive model & Theoretical contribution \\
3 & Pre-register & OSF / AsPredicted \\
4 & Parametrize & Data collection + estimation \\
5 & Publish & arXiv / SSRN preprint \\
6 & Verify & Auto-replication + peer review \\
7 & Iterate & Version control (GitHub) \\
8 & Track & Prediction dashboard \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Business Practice}

\textbf{Detailed in:} Domain appendices (DOMAIN-FINANCE, etc.)

\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Phase} & \textbf{Generic} & \textbf{Business Instantiation} \\
\midrule
1 & Problem $\to$ Module & Business challenge $\to$ EBF diagnostic \\
2 & Derive model & Decision model from framework \\
3 & Pre-register & Internal forecast documentation \\
4 & Parametrize & Client data + benchmarks \\
5 & Publish & Internal report / client deliverable \\
6 & Verify & Pilot test / A-B experiment \\
7 & Iterate & Quarterly review cycle \\
8 & Track & KPI dashboard \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Policy Making}

\textbf{Detailed in:} DOMAIN-POLICY appendix

\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Phase} & \textbf{Generic} & \textbf{Policy Instantiation} \\
\midrule
1 & Problem $\to$ Module & Policy challenge $\to$ EBF analysis \\
2 & Derive model & Policy impact model \\
3 & Pre-register & Public commitment / White paper \\
4 & Parametrize & Administrative data + surveys \\
5 & Publish & Policy brief / Public report \\
6 & Verify & Pilot program / RCT \\
7 & Iterate & Policy revision cycle \\
8 & Track & Impact monitoring system \\
\bottomrule
\end{tabular}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 6: TEMPLATES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Templates and Checklists}
\label{sec:apply-templates}

\subsection{Pre-Registration Template}

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black,
    title=\textbf{EBF Pre-Registration Template}]

\textbf{1. Study Information}
\begin{itemize}[nosep]
    \item Title:
    \item Authors:
    \item Date:
    \item EBF Module(s):
\end{itemize}

\textbf{2. Hypotheses (Derived from EBF)}
\begin{itemize}[nosep]
    \item H1:
    \item H2:
    \item H3:
\end{itemize}

\textbf{3. Quantitative Predictions}

\begin{tabular}{@{}lccc@{}}
\toprule
Prediction & Point Est. & 95\% CI & Eval. Date \\
\midrule
& & & \\
& & & \\
\bottomrule
\end{tabular}

\textbf{4. Data Source:}

\textbf{5. Analysis Method:}

\textbf{6. Success Criteria:}

\textbf{7. Failure Criteria:}

\end{tcolorbox}

\subsection{Prediction Tracking Dashboard Template}

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black,
    title=\textbf{EBF Prediction Tracking Dashboard}]

\textbf{Project:} [Name] \\
\textbf{Version:} [X.Y] \\
\textbf{Last Updated:} [Date]

\vspace{0.5em}

\begin{tabular}{@{}lccccl@{}}
\toprule
\textbf{ID} & \textbf{Prediction} & \textbf{Predicted} & \textbf{Observed} & \textbf{Eval.} & \textbf{Status} \\
\midrule
P1 & & & & & \\
P2 & & & & & \\
P3 & & & & & \\
\bottomrule
\end{tabular}

\vspace{0.5em}

\textbf{Status Legend:}
$\checkmark$ Confirmed |
$\times$ Refuted |
$\circlearrowright$ Tracking |
$\circ$ Not yet evaluated

\textbf{Notes on Refuted Predictions:}

\textbf{Planned Model Updates:}

\end{tcolorbox}

\subsection{Version Control Checklist}

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black,
    title=\textbf{EBF Version Release Checklist}]

Before releasing version X.Y:

\begin{itemize}
    \item[$\square$] Changelog updated
    \item[$\square$] All code runs successfully
    \item[$\square$] Data sources documented
    \item[$\square$] Pre-registration link included
    \item[$\square$] Prediction tracking dashboard updated
    \item[$\square$] Previous version archived
    \item[$\square$] DOI assigned (if applicable)
    \item[$\square$] Cross-references verified
    \item[$\square$] Glossary terms consistent with Appendix G
\end{itemize}

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 7: WORKED EXAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Worked Example: This Appendix}
\label{sec:apply-example}

This appendix demonstrates its own principles by applying the EBF workflow
to itself:

\begin{table}[htbp]
\centering
\caption{REF-APPLY Applied to Itself}
\label{tab:self-application}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabular}{@{}lp{8cm}@{}}
\toprule
\textbf{Phase} & \textbf{Application to This Appendix} \\
\midrule
1. Problem $\to$ Module & Gap: No process for applying EBF $\to$ Need APPLY module \\
2. Derive model & Workflow derived from EBF principles (context-dependence, feedback) \\
3. Pre-register & Hypothesis: This workflow will improve research quality \\
4. Parametrize & Time estimates based on traditional vs. EBF comparison \\
5. Publish & Published as REF-APPLY appendix \\
6. Verify & Community feedback invited; auto-check of internal consistency \\
7. Iterate & v1.0 (current); v1.1 planned after feedback \\
8. Track & Prediction: EBF adoption will follow S-curve (tracked in LIT-META) \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Reflexive validity:} If REF-APPLY is correct, then REF-APPLY itself
should be produced using the REF-APPLY workflow. This appendix demonstrates
that it is.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 8: SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
\label{sec:apply-summary}

\begin{tcolorbox}[colback=green!5!white, colframe=green!75!black,
    title=\textbf{REF-APPLY Summary}]

\textbf{The REF-APPLY Question:} How do I operationally apply the 9C?

\textbf{The Answer:} The 8-phase EBF workflow:
\begin{enumerate}[nosep]
    \item Problem $\to$ Framework Module
    \item Model Derivation (not invention)
    \item Pre-Registration
    \item Parametrization
    \item Prediction + Publication
    \item Verification
    \item Version-Controlled Iteration
    \item Permanent Prediction Tracking
\end{enumerate}

\textbf{Core Principles:}
\begin{itemize}[nosep]
    \item Derive, don't invent
    \item Pre-register, don't p-hack
    \item Track, don't hide
    \item Iterate, don't finalize
\end{itemize}

\textbf{The Fundamental Shift:}
\begin{center}
\textit{From paper as product to document as iteration.}
\end{center}

\textbf{Domain Instantiations:}
\begin{itemize}[nosep]
    \item Scientific research $\to$ LIT-META
    \item Business practice $\to$ DOMAIN appendices
    \item Policy making $\to$ DOMAIN-POLICY
\end{itemize}

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GLOSSARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Glossary of Terms}
\label{sec:apply-glossary}

See Appendix G (Central Glossary) for complete definitions. Key terms for
this appendix:

\begin{description}[nosep]
    \item[Derivation] The process of instantiating a model from the EBF framework
        by specifying parameters, not inventing new theory.
    \item[Pre-registration] Public commitment to hypotheses, methods, and analysis
        plans before data collection.
    \item[Prediction tracking] Permanent monitoring of falsifiable predictions
        until resolution.
    \item[Living document] A document that is versioned and updated based on
        feedback, rather than published once and never revised.
    \item[Reflexive validity] The property of a framework that can explain itself
        using its own concepts.
\end{description}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CROSS-REFERENCE FOOTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{1em}
\hrule
\vspace{0.5em}

\noindent\textit{Cross-references:}
Appendix AAA (WHO),
Appendix B (HOW),
Appendix C (WHAT),
Appendix V (WHEN),
Appendix BBB (WHERE),
Appendix AU (AWARE),
Appendix AV (READY),
Appendix G (Glossary),
Appendix LIT-META (Scientific instantiation),
Appendix AN (LLM-MC estimation).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF APPENDIX REF-APPLY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
