\section{LIT-HAIDT: Jonathan Haidt Research: Moral Psychology and Polarization}
\label{app:litz}

This appendix integrates papers by Jonathan Haidt on moral judgment,
emotional reasoning, and political polarization. Haidt's work demonstrates that moral
judgments are primarily emotional and intuitive, with reasoning following to justify
initial reactions.

\subsection{Research Program Overview}

Jonathan Haidt's research program addresses core behavioral economics themes:

\begin{itemize}
  \item \textbf{Moral Foundations}: Five universal principles underlying morality
  \item \textbf{Emotional Judgment}: Intuition-first moral decision-making
  \item \textbf{Group Polarization}: How groups magnify initial tendencies
  \item \textbf{Political Division}: Why good people are divided by politics
  \item \textbf{Cultural Diversity}: Moral foundations vary across cultures
\end{itemize}

\subsection{Papers Integrated: 4 works}

\subsubsection{2001: The Emotional Dog and Its Rational Tail: A Social ...}

\paragraph{Citation.}
Haidt, Jonathan (2001). ``The Emotional Dog and Its Rational Tail: A Social Intuitionist Approach to Moral Judgment.''
\textit{Psychological Review}.

\paragraph{Core Finding.}
Moral judgment is primarily intuitive; reasoning follows

\paragraph{9C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Moral Behavior
  \item \textbf{Dimension}: E
  \item \textbf{Context}: Moral Culture
  \item \textbf{Complementarity}: γ = 0.77
\end{itemize}

\subsubsection{2007: The New Synthesis in Moral Psychology...}

\paragraph{Citation.}
Haidt, Jonathan (2007). ``The New Synthesis in Moral Psychology.''
\textit{Science}.

\paragraph{Core Finding.}
Five moral foundations underlie all human moral systems

\paragraph{9C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Moral Behavior
  \item \textbf{Dimension}: E
  \item \textbf{Context}: Moral Foundation
  \item \textbf{Complementarity}: γ = 0.71
\end{itemize}

\subsubsection{2012: The Righteous Mind: Why Good People Are Divided by...}

\paragraph{Citation.}
Haidt, Jonathan (2012). ``The Righteous Mind: Why Good People Are Divided by Politics and Religion.''
\textit{Pantheon Books}.

\paragraph{Core Finding.}
Political polarization stems from different moral foundations across groups

\paragraph{9C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Moral Polarization
  \item \textbf{Dimension}: S
  \item \textbf{Context}: Political Context
  \item \textbf{Complementarity}: γ = 0.79
\end{itemize}

\subsubsection{2015: The Righteous Mind: Why Good People Are Divided...}

\paragraph{Citation.}
Haidt, Jonathan (2015). ``The Righteous Mind: Why Good People Are Divided.''
\textit{Lecture Series}.

\paragraph{Core Finding.}
Understanding moral diversity is key to reducing polarization

\paragraph{9C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: Moral Diversity
  \item \textbf{Dimension}: S
  \item \textbf{Context}: Cultural Diversity
  \item \textbf{Complementarity}: γ = 0.68
\end{itemize}

\subsection{Summary}

This appendix integrates 4 papers by Jonathan Haidt
spanning research on moral foundations, emotional judgment, group polarization.
The papers demonstrate systematic patterns in human behavior that have important
implications for policy, organization, and individual decision-making.

\subsection{References}

For complete reference details and citations, see the master bibliography
\texttt{bcm2\_master\_references.bib}.

\vspace{1em}
\hrule
\vspace{0.5em}

\noindent\textit{Cross-references:}
Appendix G (Central Glossary), Chapter 14 (Applications)
