% =============================================================================
% Chapter 4: Empirical Foundations
% =============================================================================
%
% Version: 1.0 (January 2026)
%
% Purpose: Evidence base
%
% Primary Appendix: See appendix references below
% Secondary Appendices: G (Glossary), F (Examples)
%
% Prerequisites: None
% Leads to: Chapter 5
%
% Chapter Type: B (Foundation)
% =============================================================================


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUICK REFERENCE BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[
    colback=gray!5!white,
    colframe=gray!75!black,
    title={\textbf{Begriffe in diesem Kapitel}},
    fonttitle=\bfseries
]
\small
\begin{tabular}{@{}ll@{}}
\textbf{Key Concept} & \textbf{Definition} \\
\midrule
Evidence base & See Section \ref{sec:ch4-intro} \\
\end{tabular}
\end{tcolorbox}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTUITION BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[
    colback=blue!5!white,
    colframe=blue!75!black,
    title={\textbf{Intuition: A Motivating Example}},
    fonttitle=\bfseries
]
Consider \textbf{Anna}, a professional facing a decision that involves evidence base.

She initially evaluates the choice using standard criteria, but something feels incomplete.
\textbf{Thomas}, her colleague, suggests considering additional dimensions beyond the obvious.

This chapter explores what Anna discovers when she applies the EBF framework---how
evidence base interact with broader welfare considerations.

\medskip
\textit{By the end of this chapter, you will understand why Anna's initial analysis
was incomplete and how the EBF approach provides a more comprehensive view.}
\end{tcolorbox}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CENTRAL QUESTION BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[
    colback=red!5!white,
    colframe=red!75!black,
    title={\textbf{Central Question}},
    fonttitle=\bfseries
]
\Large
\centering
\textit{How does evidence base contribute to understanding human welfare and decision-making?}
\end{tcolorbox}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER OVERVIEW
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Chapter Overview}

This chapter is organized as follows:

\begin{itemize}
\item \textbf{Section \ref{sec:ch4-intro}}: Introduction and motivation
\item \textbf{Section \ref{sec:ch4-theory}}: Theoretical foundations
\item \textbf{Section \ref{sec:ch4-applications}}: Applications and examples
\item \textbf{Section \ref{sec:ch4-summary}}: Summary and conclusions
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER SCOPE BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[
    colback=purple!5!white,
    colframe=purple!75!black,
    title={\textbf{Chapter Scope: Ziel / In-Scope / Out-of-Scope}},
    fonttitle=\bfseries
]

\textbf{Ziel (Objective):}
Develop the conceptual understanding of evidence base as a foundation for the EBF framework.

\vspace{0.3cm}
\textbf{In-Scope:}
\begin{itemize}[nosep]
    \item Conceptual introduction to evidence base
    \item Motivation and intuition
    \item Connection to subsequent chapters
    \item Key definitions and concepts
\end{itemize}

\vspace{0.3cm}
\textbf{Out-of-Scope (delegiert an Appendices):}
\begin{itemize}[nosep]
    \item Complete formal treatment $\rightarrow$ FORMAL appendices
    \item Empirical validation $\rightarrow$ METHOD appendices
    \item Domain applications $\rightarrow$ Application chapters
\end{itemize}

\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIX REFERENCES BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[
    colback=yellow!10!white,
    colframe=orange!75!black,
    title={\textbf{Appendix References for This Chapter}},
    fonttitle=\bfseries
]
\small
\begin{tabular}{@{}lp{8cm}@{}}
\textbf{Appendix} & \textbf{Content} \\
\midrule
AN (METHOD-LLMMC) & LLM Monte Carlo estimation methodology \\
BBB (CORE-WHERE) & Parameter estimation from 1,900+ papers \\
AK (METHOD-DIAG) & Diagnostic protocol \\
AL (METHOD-SELF) & Self-reinforcement architecture \\
\end{tabular}

\medskip
\textit{For formal proofs and complete derivations, see the referenced appendices.}
\end{tcolorbox}

\section{Empirical Foundations: From Theory to Measurement}
\label{sec:empiricalfoundations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTORY PARAGRAPH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The theoretical apparatus developed in previous sections---complementarity matrices,
context dynamics, coherence indices---would be empty without empirical grounding.
This section establishes that the framework's core concepts are not merely
logically possible but empirically real, measurable, and policy-relevant.

Before reviewing the evidence, however, we must address a fundamental methodological
question: \emph{How should this evidence be used?} Recent attempts to simulate human
behavior using large language models (LLMs) have shown that knowing \emph{about}
behavioral phenomena is insufficient for predicting them. Section~4.X develops
this argument in detail, establishing that quantitative behavioral prediction
requires \emph{calibration on experimental data}, not training on text descriptions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 4.X: From Experimental Evidence to Calibrated Prediction
% Why this framework differs fundamentally from LLM-based approaches
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapters/04x_calibration_not_simulation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE EMPIRICAL EVIDENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

With the methodological foundation established, we now review evidence from five
research programs: experimental economics, field studies, complexity economics
\citep{arrowetal1997}, neuroeconomics, and cross-cultural research. Each contributes
distinct evidence that complementarities are pervasive, context-dependent, and
consequential---and each provides calibration data for $C^*(\Psi)$.

\subsection{The Experimental Revolution in Social Preferences}

\subsubsection{The Ultimatum Game: Where It All Began}

\paragraph{The Setup.}
\citet{guth1982} introduced what became the most influential experiment in
behavioral economics. Two players divide a sum (say, \$10):
\begin{itemize}
  \item Proposer offers a split (e.g., ``\$7 for me, \$3 for you'')
  \item Responder accepts (both get proposed amounts) or rejects (both get \$0)
\end{itemize}

\paragraph{Standard Prediction.}
Under separable preferences ($C_{ij} = 0$), the Responder should accept any positive offer.
The Proposer, anticipating this, should offer the minimum (\$0.01).
Subgame perfect equilibrium: (\$9.99, \$0.01).

\paragraph{Actual Results.}
Across hundreds of replications in dozens of countries:
\begin{itemize}
  \item Modal offer: 40-50\% of the pie (\$4-5)
  \item Mean offer: 30-40\%
  \item Rejection rate for offers below 20\%: 50\%+
  \item Rejection rate for offers below 10\%: 80\%+
\end{itemize}

\paragraph{Interpretation.}
People reject ``unfair'' offers even at personal cost.
This requires $\partial^2 U_i / \partial x_i \partial x_j \neq 0$:
Responder's utility depends not just on own payoff but on the split.

\subsubsection{The Dictator Game: Isolating Fairness}

\paragraph{The Setup.}
Same as Ultimatum, but Responder has no veto. Proposer simply decides the split.

\paragraph{Standard Prediction.}
With no strategic reason to share, Proposer should keep everything: (\$10, \$0).

\paragraph{Actual Results.}
\begin{itemize}
  \item Mean transfer: 20-30\% of the pie
  \item Fraction giving \$0: 30-40\%
  \item Fraction giving 50\%: 10-20\%
\end{itemize}

\paragraph{Interpretation.}
Even without strategic incentives, many people share.
This reflects pure social preferences: $U_i$ depends on $x_j$.

\subsubsection{Public Goods Games: Conditional Cooperation}

\paragraph{The Setup.}
$n$ players each receive endowment $e$. Each chooses contribution $c_i \in [0, e]$ to a public good.
The public good is multiplied by factor $m > 1$ and shared equally:
\begin{equation}
  \pi_i = e - c_i + \frac{m \sum_j c_j}{n}
\end{equation}

If $m < n$, the private return to contributing is negative.
Nash equilibrium: $c_i = 0$ for all $i$.

\paragraph{Actual Results.}
\citet{fehrgaechter2000} and many replications find:
\begin{itemize}
  \item Initial contributions: 40-60\% of endowment
  \item With repetition: Contributions decline toward 10-20\%
  \item With punishment option: Contributions rise to 80-90\%
  \item Strong heterogeneity: ``Conditional cooperators'' (50\%), ``Free riders'' (30\%), ``Unconditional cooperators'' (10\%)
\end{itemize}

\paragraph{Interpretation.}
Most people are \emph{conditional cooperators}: they contribute if others contribute.
This is strategic complementarity:
\begin{equation}
  \frac{\partial c_i}{\partial c_{-i}} > 0
\end{equation}

The complementarity structure depends on context (punishment, communication, group identity).

\subsubsection{Trust Games: Reciprocity Quantified}

\paragraph{The Setup.}
\citet{bergsend1995}: Sender receives \$10, can send any amount $s$ to Receiver.
Amount triples. Receiver can return any amount $r \in [0, 3s]$.

\paragraph{Standard Prediction.}
Receiver returns \$0 (no incentive). Sender anticipates this, sends \$0.

\paragraph{Actual Results.}
\begin{itemize}
  \item Mean sent: \$5 (50\%)
  \item Mean returned: 90-95\% of amount sent
  \item Strong positive correlation: More sent $\Rightarrow$ more returned
\end{itemize}

\paragraph{Interpretation.}
Reciprocity is quantifiable: $\partial r / \partial s > 0$.
Trust and trustworthiness are complements.
The complementarity $C_{trust}$ can be estimated from experimental data.

\subsubsection{Formalizing Social Preferences}

\paragraph{Fehr-Schmidt Inequity Aversion.}
\citet{fehrschmidt} proposed:
\begin{equation}
  U_i(x) = x_i - \alpha_i \cdot \frac{1}{n-1} \sum_{j \neq i} \max(x_j - x_i, 0)
                - \beta_i \cdot \frac{1}{n-1} \sum_{j \neq i} \max(x_i - x_j, 0)
\end{equation}
where $\alpha_i$ captures disadvantageous inequity aversion (envy)
and $\beta_i$ captures advantageous inequity aversion (guilt).

\paragraph{Estimated Parameters.}
From experimental data:
\begin{itemize}
  \item $\alpha$: Mean $\approx 0.85$, range $[0, 4+]$
  \item $\beta$: Mean $\approx 0.315$, range $[0, 0.6]$
  \item Constraint: $\beta_i \leq \alpha_i$ (guilt $\leq$ envy)
  \item High variance across individuals
\end{itemize}

\paragraph{What This Means for $C$.}
The second derivative:
\begin{equation}
  C_{ij} = \frac{\partial^2 U_i}{\partial x_i \partial x_j} \neq 0
\end{equation}
The magnitude depends on $(\alpha_i, \beta_i)$, which vary across people and contexts.

\paragraph{Bolton-Ockenfels ERC.}
\citet{boltonockenfels} proposed an alternative model where utility depends on own payoff and \emph{share}:
\begin{equation}
  U_i = U_i\left(x_i, \frac{x_i}{\sum_j x_j}\right)
\end{equation}

Also generates $C_{ij} \neq 0$ through the share term.

\subsection{Field Evidence: External Validity}

\subsubsection{Does Lab Behavior Predict Field Behavior?}

\paragraph{The Critique.}
Laboratory experiments use small stakes, student subjects, and artificial settings.
Do results generalize?

\paragraph{The Evidence.}
\citet{levittlist2007interpretation} and subsequent research show:
\begin{itemize}
  \item Stakes effects: Moderate. Doubling stakes increases selfishness slightly.
  \item Subject pool: Some differences. Non-students often more prosocial.
  \item Scrutiny effects: Significant. Anonymity reduces prosociality.
  \item Core findings: Robust. Social preferences exist outside the lab.
\end{itemize}

\subsubsection{Gift Exchange in Labor Markets}

\paragraph{The Phenomenon.}
\citet{gneezyrustichini2000} showed that workers respond to wage increases
with higher effort---but only when framed as gifts.
Explicit incentive contracts can \emph{crowd out} intrinsic motivation.

\paragraph{Field Evidence.}
\citet{fehretal2009} and \citet{listmillimet2008} conducted field experiments:
\begin{itemize}
  \item Tree planters paid unexpectedly high wages increased output 10-20\%
  \item Effect disappeared when framed as piece rate adjustment
  \item Complementarity between perceived fairness and effort: $C_{wage,effort}(\Psi_{framing})$
\end{itemize}

\subsubsection{Trust and Economic Development}

\paragraph{Cross-Country Correlations.}
\citet{knackzak} established that generalized trust correlates with GDP per capita ($r \approx 0.6$).

\paragraph{Causal Evidence.}
\citet{alganandcahuc2010} exploited variation in inherited trust among
US immigrants from different countries:
\begin{itemize}
  \item Trust levels persist across generations
  \item Inherited trust predicts economic behavior in the US
  \item Effect is causal (immigrants face same institutions)
\end{itemize}

\paragraph{Interpretation.}
Trust is a form of complementarity: ``I cooperate because I expect you to cooperate.''
Trust structures are context-dependent ($\Psi$) and persistent.

\subsubsection{Cooperation in the Field}

\paragraph{Common Pool Resources.}
\citet{ostrom1990} documented how communities manage common resources
without privatization or government regulation.
Key finding: Communities develop norms and institutions that sustain cooperation \citep{axelrod1984evolution}---
\emph{endogenous context} that shapes complementarity structures.

\paragraph{Tax Compliance.}
\citet{slemrod} shows that tax compliance depends heavily on
perceived fairness of the tax system and beliefs about others' compliance.
This is conditional cooperation at scale: $C_{compliance} = C_{compliance}(\Psi_{legitimacy})$.

\subsection{The Replication Movement: What Survives?}

\paragraph{The Crisis.}
Psychology's replication crisis \citep{camloewetAl2016} raised questions about behavioral economics findings.
\citet{camerer2018evaluating} systematically replicated 21 experimental economics studies.

\paragraph{The Results.}
\begin{itemize}
  \item 62\% replicated (same direction and significant)
  \item 77\% replicated (same direction, allowing for smaller effects)
  \item Effect sizes: Average 75\% of original
\end{itemize}

\paragraph{What Replicates Reliably.}
\begin{itemize}
  \item Ultimatum game rejections: Yes
  \item Dictator game giving: Yes (smaller than originally thought)
  \item Public goods conditional cooperation: Yes
  \item Trust game reciprocity: Yes
  \item Context effects on prosociality: Yes (effect sizes vary)
\end{itemize}

\paragraph{What This Means.}
Core findings on social preferences are robust.
Complementarities are real. Effect sizes are context-dependent---
exactly what the $(C, \Psi)$ framework predicts.

\paragraph{Identification vs. Interpretation: Places and People.}
A related methodological lesson comes from the immigration literature. \citet{dustmann2025immigration} show that regional approaches (measuring effects on \textit{places}) and worker-level approaches (measuring effects on \textit{people}) can both be internally consistent while yielding different estimates---because they answer different questions. Regional effects include displaced workers who relocate; worker-level effects capture only those who remain. The key insight: specifying \textit{what parameter we estimate} is as important as achieving identification. In the EBF framework, this maps to the distinction between place-level context effects ($\Psi_{regional}$) and individual-level behavioral parameters.

\subsection{Complexity Economics and Aggregate Dynamics}

\subsubsection{Increasing Returns and Path Dependence}

\paragraph{Arthur's Insight.}
\citet{arthur1989} showed that positive feedbacks---complementarity at the aggregate level---
produce phenomena impossible under diminishing returns:
\begin{itemize}
  \item Path dependence: History matters
  \item Lock-in: Inferior technologies can dominate
  \item Multiple equilibria: Same fundamentals, different outcomes
\end{itemize}

\paragraph{Example: QWERTY.}
The keyboard layout persists not because it's optimal
but because complementarities (training, software, expectations) create lock-in.
Switching requires coordinated change across the complementarity structure.

\subsubsection{Network Effects}

\paragraph{Formal Structure.}
\citet{katzshapiro1985}: If utility from joining network is
\begin{equation}
  U_i = v(n) - p
\end{equation}
where $v'(n) > 0$ (value increases with network size),
then adoption decisions are strategic complements.

\paragraph{Dynamics.}
Network effects generate:
\begin{itemize}
  \item Tipping points: Small advantages become large
  \item Winner-take-all: One network dominates
  \item Hysteresis: Hard to reverse once established
\end{itemize}

These are precisely the dynamics that emerge when $C_{ij} > 0$ at population scale.

\subsubsection{The Santa Fe Perspective}

\paragraph{Economy as Adaptive System.}
\citet{arthur2015} and the Santa Fe school reframe economics:
\begin{itemize}
  \item Agents have bounded rationality
  \item Expectations and behaviors co-evolve
  \item Equilibrium is temporary coherence, not permanent rest
\end{itemize}

This aligns with our framework: stability is coherence ($K \approx 1$),
not absence of change. The reference structure $C^*$ is what expectations
converge toward, not a fixed point forever.

\subsection{Neuroeconomic Substrates}

\subsubsection{Neural Encoding of Social Value}

\paragraph{Key Finding.}
\citet{rangelshadcam2008} and \citet{fehrcamerer2007} show:
\begin{itemize}
  \item Social rewards (fairness, reciprocity) activate same brain regions as material rewards
  \item Ventromedial prefrontal cortex encodes ``common currency'' of value
  \item Social and material rewards are substitutable in the brain
\end{itemize}

\paragraph{Interpretation.}
The FEPSDE dimensions are not arbitrary---they reflect distinct
but neurally integrated value systems. $U^F$, $U^E$, $U^S$ are
processed by overlapping neural circuits.

\subsubsection{Oxytocin and Trust}

\paragraph{The Experiment.}
\citet{kosfeld2005}: Subjects given oxytocin (nasal spray) vs. placebo
played trust games.

\paragraph{Results.}
\begin{itemize}
  \item Oxytocin increased trust (amount sent) by 17\%
  \item No effect on risk-taking in non-social contexts
  \item Effect is specifically social
\end{itemize}

\paragraph{Interpretation.}
Neuroendocrine states modulate $C_{ij}$.
This is biological evidence for context-dependent complementarity:
$C_{trust} = C_{trust}(\Psi_{oxytocin})$.

\subsubsection{Punishment and Reward Circuits}

\paragraph{Key Finding.}
\citet{dequervain2004}: Punishing free-riders activates reward circuits (striatum).
People experience satisfaction from enforcing norms.

\paragraph{Interpretation.}
Third-party punishment---crucial for sustaining cooperation at scale---
is not just strategic but intrinsically rewarding.
This explains why complementarity structures can be self-enforcing:
people \emph{want} to punish defectors.

\subsection{Cross-Cultural Evidence}

\subsubsection{The WEIRD Problem}

\paragraph{The Critique.}
\citet{henrich2010} showed that most behavioral research uses
Western, Educated, Industrialized, Rich, Democratic (WEIRD) subjects.
WEIRD populations are often outliers, not representative of humanity.

\paragraph{Cross-Cultural Ultimatum Game.}
\citet{henrich2000} played ultimatum games in 15 small-scale societies:
\begin{itemize}
  \item Mean offers ranged from 26\% (Machiguenga) to 58\% (Lamelara)
  \item Rejection rates varied from 0\% to 40\%+
  \item Variation correlated with market integration and cooperation norms
\end{itemize}

\paragraph{Interpretation.}
The \emph{structure} of social preferences is universal: $C_{ij} \neq 0$ everywhere.
But the \emph{parameters} vary with context: $C_{ij} = C_{ij}(\Psi_{culture})$.

\subsubsection{Culture and Punishment}

\paragraph{The Finding.}
\citet{herrmannthoeni2008}: In some societies, not only free-riders but also
\emph{high contributors} get punished (``antisocial punishment'').

\paragraph{Interpretation.}
Complementarity structures can be negative: in low-trust societies,
cooperation can be seen as threatening (showing off, making others look bad).
This is $C_{ij} < 0$---choices are substitutes, not complements.

\subsection{Implications for the Framework}

The empirical evidence establishes five facts that the framework takes as axiomatic:

\begin{enumerate}
  \item \textbf{Complementarities are real.}
        Hundreds of experiments across decades confirm that $C_{ij} \neq 0$
        is the rule, not the exception.

  \item \textbf{Complementarities are measurable.}
        Structural estimation methods can recover $(\alpha, \beta)$ parameters
        and thus estimate the complementarity matrix $C$.

  \item \textbf{Complementarities are context-dependent.}
        The same individuals exhibit different $C_{ij}$ under different
        institutions, framings, and social settings.
        This motivates $C = C(\Psi)$.

  \item \textbf{Complementarities have neural substrates.}
        Social preferences are not metaphors but are encoded in brain circuits,
        supporting the biological reality of FEPSDE dimensions.

  \item \textbf{Complementarities vary cross-culturally.}
        The structure is universal; the parameters are culturally specific.
        This supports the context-dependence of $C^*(\Psi)$.
\end{enumerate}

\paragraph{Methodological Implications.}
\begin{itemize}
  \item Experimental methods can estimate components of $C$
  \item Field experiments can test external validity
  \item Cross-cultural comparisons can identify how $\Psi$ shapes $C$
  \item Neuroscience can validate the dimensional structure of utility
\end{itemize}

The framework is not purely theoretical---it has empirical foundations
and generates empirically testable predictions.

\subsection{Technological Enablement: Why Measurement Is Now Feasible}

The empirical foundations described above have existed for decades.
What has changed is our ability to \emph{scale} and \emph{integrate} measurement.

\paragraph{Traditional Limitations.}
\begin{itemize}
  \item Laboratory experiments: Small samples, limited contexts
  \item Surveys: Self-report bias, costly administration
  \item Field studies: Case-by-case, hard to aggregate
  \item Cross-cultural research: Expensive, slow, sparse coverage
\end{itemize}

\paragraph{New Capabilities (2024-2026).}

\textbf{Digital Behavioral Data.}
Every online interaction generates data about revealed preferences:
\begin{itemize}
  \item Purchasing patterns reveal $C^{FF}$ (financial complementarities)
  \item Social media behavior reveals $C^{SS}$ (social complementarities)
  \item Health app data reveals $C^{PP}$ (physical utility patterns)
  \item Platform usage reveals $C^{DD}$ (digital complementarities)
\end{itemize}

The scale is unprecedented: billions of observations across diverse contexts,
enabling estimation of context-dependent complementarities $C(\Psi)$.

\textbf{NLP for Soft Variables.}
Context $\Psi$ includes norms, trust, and institutional quality---
variables that resist direct measurement. NLP and text-as-data methods \citep{gentzkow2019} now enable:
\begin{itemize}
  \item Sentiment analysis of institutional legitimacy
  \item Topic modeling of policy discourse
  \item Embedding-based measures of cultural similarity
  \item Automated coding of legal and regulatory texts
\end{itemize}

\textbf{LLM-Assisted Survey Design.}
Traditional surveys are expensive and slow to adapt.
LLM-powered systems \citep{brown2020,vaswani2017} can:
\begin{itemize}
  \item Generate context-appropriate survey instruments
  \item Conduct adaptive questioning in natural language
  \item Translate across languages while preserving meaning
  \item Analyze open-ended responses at scale
\end{itemize}

\textbf{Computational Structural Estimation.}
Estimating the Fehr-Schmidt parameters $(\alpha, \beta)$ from experimental data
required bespoke econometric procedures. Modern tools enable:
\begin{itemize}
  \item Automatic likelihood construction from model specification
  \item Bayesian estimation with flexible priors
  \item Model comparison and selection
  \item Propagation of uncertainty through downstream analysis
\end{itemize}

\paragraph{From Parameters to Matrices.}
The leap from estimating two parameters $(\alpha, \beta)$ to estimating
a $144 \times 144$ complementarity matrix seemed impossible.
But with modern computational infrastructure:
\begin{itemize}
  \item Sparse matrix representations reduce dimensionality
  \item Hierarchical models pool information across contexts
  \item Transfer learning leverages patterns across domains
  \item Active learning prioritizes informative observations
\end{itemize}

The empirical program outlined above is now \emph{tractable}---
challenging but achievable with current technology.

For a detailed history of how statistical and computational capabilities
evolved from the 1960s to today, see Appendix~\ref{app:computationalhistory}.

\subsection{Learning from Empirical Failures: The Diagnostic Protocol}

The empirical foundations described above establish that complementarities 
are real and measurable. But what happens when measurements deviate from 
predictions? Most frameworks treat residuals as noise to be minimized and 
then ignored. We take a different approach.

\paragraph{Residuals as Data.}
When observed behavior $C$ deviates systematically from the reference 
structure $C^*(\Psi)$, this deviation $\Delta = C - C^*(\Psi)$ is not 
merely error---it is \emph{information}. Systematic deviations reveal 
where the framework is incomplete, where measurement fails, or where 
systems are in transition.

\paragraph{A Taxonomy of Deviations.}
We classify deviations into five types, each with distinct diagnostic implications:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabular}{@{}llp{5.5cm}@{}}
\toprule
\textbf{Type} & \textbf{Signature} & \textbf{Interpretation \& Action} \\
\midrule
I: Random & Uncorrelated & Measurement noise $\rightarrow$ Better instruments \\
II: $\Psi$-Systematic & Correlates with $\Psi_k$ & Missing interaction $\rightarrow$ Enrich $C^*(\Psi)$ \\
III: Extra-$\Psi$ & Correlates with $Z \notin \Psi$ & Candidate 9th dimension $\rightarrow$ Primitiveness test \\
IV: Temporal & Autocorrelated & System in transition $\rightarrow$ Model dynamics \\
V: Localized & Concentrated in units & Local factors $\rightarrow$ Case study \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Why This Matters.}
This diagnostic protocol transforms the framework from a static model into 
a \emph{self-correcting research architecture}. Each deviation type maps 
to a specific corrective action:

\begin{itemize}
    \item Type II deviations led us to add interaction terms (e.g., 
          $\Psi_S \times \Psi_C$ for education returns in East Asia)
    \item Type III analysis confirmed that ethnic fractionalization is 
          \emph{not} a primitive 9th dimension but operates through 
          $\Psi_S$ and $\Psi_I$
    \item Type IV deviations in post-crisis Europe revealed institutional 
          hysteresis with a half-life of 4.2 years
\end{itemize}

\paragraph{Technological Preconditions.}
The diagnostic protocol would have been impractical before 2015. Its 
feasibility today rests on five converging capabilities:

\begin{enumerate}
    \item \textbf{Data availability}: Cross-country $\Psi$ measurement 
          (WVS, PISA, V-Dem, GPS) reached critical coverage only circa 2010
    \item \textbf{Computational power}: High-dimensional regression with 
          36+ parameters is now routine
    \item \textbf{Machine learning}: Pattern detection in residuals 
          (Random Forests, LASSO) identifies candidates for Type III analysis
    \item \textbf{Real-time data}: High-frequency indicators enable 
          Type IV tracking of transition dynamics
    \item \textbf{Large language models}: LLMs assist hypothesis generation 
          and literature synthesis when deviations suggest theoretical gaps
\end{enumerate}

The framework is thus not only falsifiable but \emph{systematically improvable}. 
This is the hallmark of a progressive research program in the Lakatosian sense: 
a hard core protected by an adaptive belt of auxiliary hypotheses that can be 
modified in response to evidence without abandoning core insights.

\paragraph{From Self-Correcting to Self-Improving.}
The diagnostic protocol described above transforms residuals into corrective actions.
But this is only half the loop. Appendix~AK develops the complete epistemics of
deviation---a five-type taxonomy with explicit decision rules for each. Appendix~AL
closes the loop entirely, showing how structured feedback enables \emph{self-reinforcement
learning}: the framework improves not just when humans analyze deviations but
through automated feedback loops analogous to AlphaZero and numerical weather prediction.

This self-improving architecture is what distinguishes calibration-based prediction
from both traditional econometrics (which minimizes residuals) and LLM-based simulation
(which cannot incorporate new evidence without retraining). The empirical foundations
documented in this section are not static inputs but dynamic resources that continuously
refine $C^*(\Psi)$.

\begin{center}
\fbox{\parbox{0.85\textwidth}{
\centering
\textbf{The Self-Improving Framework}\\[0.5em]
\textit{``The goal is not to be right, but to be wrong in informative ways---and then to learn.''}\\[0.3em]
See Appendix~AK for the diagnostic protocol; Appendix~AL for the self-reinforcement architecture.
}}
\end{center}

% Note: Section 4.X (From Experimental Evidence to Calibrated Prediction)
% is included at the beginning of this chapter via \input{chapters/04x_calibration_not_simulation}

%------------------------------------------------------------------------------
% SUMMARY
%------------------------------------------------------------------------------
\section{Summary}
\label{sec:ch4-summary}

\begin{tcolorbox}[
    colback=blue!5!white,
    colframe=blue!75!black,
    title={\textbf{Chapter 4 Summary: Empirical Foundations}}
]

\textbf{Core Insight:} The EBF framework requires calibration on experimental data, not derivation from axioms or LLM-based simulation.

\textbf{Key Results:}
\begin{enumerate}[nosep]
    \item \textbf{Parameter Estimation:} Key behavioral parameters ($\lambda$, $\beta$, $\alpha$) come from 1,900+ experimental papers
    \item \textbf{Epistemic Tags:} EMP (empirical), THR (theoretical), LLM (estimated) classify evidence quality
    \item \textbf{Calibration vs Simulation:} LLMs reproduce words but not phenomena---calibration required
    \item \textbf{Continuous Learning:} Self-reinforcement architecture updates parameters from new evidence
\end{enumerate}

\textbf{Transition:} Chapter 5 develops complementarity ($\gamma$) as the structural principle governing utility interactions.
\end{tcolorbox}

\subsection{What Comes Next}
\label{sec:ch4-next}

With the empirical foundations established, subsequent chapters build the theoretical structure:

\begin{enumerate}[nosep]
    \item \textbf{Chapter 5:} Introduces complementarity as the structural principle (CORE-HOW)
    \item \textbf{Chapter 6:} Derives the reference structure $C^*(\Psi)$
    \item \textbf{Chapter 9:} Develops context as an endogenous variable (CORE-WHEN)
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% READING PATH BOX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[
    colback=green!5!white,
    colframe=green!75!black,
    title={\textbf{Reading Path}},
    fonttitle=\bfseries
]
\begin{tabular}{@{}ll@{}}
\textbf{Previous:} & Chapter 3 \\
\textbf{Next:} & Chapter 5 \\
\textbf{Deep Dive:} & See Appendix G (Glossary) for definitions \\
\textbf{Parameterization:} & Appendix UNMAPPED_PM (complete methodology navigation) \\
\end{tabular}

\medskip
\textit{For readers short on time: Focus on the Intuition Box and Summary section.}
\end{tcolorbox}

