%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application Domains Revisited: Awareness Analysis}
\label{subsec:awareness-applications-revisited}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Chapter~\ref{sec:fepsde-utility} Section~\ref{subsec:applications} introduced
nine application domains demonstrating the welfare function. We now revisit
each domain through the Awareness lens, revealing the specific awareness
asymmetries that explain the observed behavioral patterns.

\subsubsection{Overview: The Awareness Diagnosis Framework}

For each domain, we analyze:
\begin{enumerate}
\item \textbf{Awareness Profile:} Which $A$-components are active/inactive?
\item \textbf{System Level:} Which system (SYS 0, 1, 2) dominates?
\item \textbf{Self-Community Asymmetry:} Where does the gradient create problems?
\item \textbf{Active Biases:} Which specific biases are operating?
\item \textbf{Intervention Target:} Which $A$-component must be activated?
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.1: Labor Market Transitions}
\label{subsubsec:awareness-labor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Coal miners reject retraining offers that would increase income by \euro{20,000}.
Despite clear INU gains, total welfare decreases due to IDN and KNU losses.

\paragraph{Awareness Profile.}

\begin{table}[htbp]
\centering
\caption{Labor Transition: Awareness Analysis}
\label{tab:labor-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llcll@{}}
\toprule
\textbf{Component} & \textbf{Content} & \textbf{$A$ Level} & \textbf{System} & \textbf{Why} \\
\midrule
$A^{self}_{INU,F}$ & Higher salary & MEDIUM & SYS 2 & Requires calculation \\
$A^{self}_{INU,P}$ & Safer work & LOW & SYS 2 & Abstract, delayed \\
$A^{self}_{KNU}$ & Leaving community & \textbf{HIGH} & SYS 1 & Emotional, social \\
$A^{self}_{IDN}$ & ``Not a miner anymore'' & \textbf{INSTANT} & SYS 0/1 & Identity threat \\
$A^{comm}_{INU}$ & How others are affected & LOW & SYS 2 & Requires empathy \\
$A^{comm}_{IDN}$ & Community's identity loss & LOW & SYS 2 & Abstract \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{System Level Analysis.}
\begin{itemize}
\item \textbf{SYS 0/1 (Dominant):} Identity threat ($A^{self}_{IDN}$) is instant---the 
moment the miner imagines ``becoming a coder,'' visceral rejection occurs
\item \textbf{SYS 2 (Suppressed):} Financial benefit ($A^{self}_{INU,F}$) requires 
calculation and is easily overridden by SYS 0/1
\item \textbf{Hyper-Dissonance:} When $A^{self}_{IDN}$ triggers strong negative emotion,
$A^{self}_{INU}$ (SYS 2) is structurally suppressed
\end{itemize}

\paragraph{Active Biases.}
\begin{itemize}
\item \textbf{Identity-Protective Cognition:} $A^{self}_{IDN}$ blocks processing of 
$A^{self}_{INU}$ information
\item \textbf{Status Quo Bias:} Current identity requires no awareness; change requires 
massive $A$ activation
\item \textbf{Loss Aversion:} $A^{self}_{IDN}$(loss) >> $A^{self}_{INU}$(gain) due to 
fear > hope asymmetry
\item \textbf{Present Bias:} IDN loss is instant; INU gain is delayed
\end{itemize}

\paragraph{The Critical Asymmetry.}
\begin{equation}
A^{self}_{IDN}(t^*) = 1 \text{ (instant)} \quad \text{vs.} \quad A^{self}_{INU,F,t>0}(t^*) << 1 \text{ (requires SYS 2)}
\end{equation}

The identity threat is \emph{felt immediately}; the financial benefit must be 
\emph{calculated deliberately}. This asymmetry explains rejection.

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Labor Transition: Awareness-Based Interventions}
\label{tab:labor-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A^{self}_{IDN}$ & Identity bridge & ``Energy transition leader'' reduces IDN threat \\
$A^{self}_{INU,F}$ & Make concrete & Show actual paycheck, not abstract ``\euro{20k}'' \\
$A^{self}_{KNU}$ & Collective transition & ``We move together'' maintains community $A$ \\
$A^{comm}_{IDN}$ & Role modeling & Successful transitioners show it's possible \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Labor Transition Awareness Insight:}
The miner isn't ``irrational''---their awareness structure makes IDN loss 
instant (SYS 0/1) while INU gain requires effortful SYS 2 activation.
Successful intervention must either:
\begin{itemize}
\item Reduce $A^{self}_{IDN}$ threat (identity bridge)
\item Elevate $A^{self}_{INU}$ to SYS 1 level (emotional connection to future)
\item Make the transition collective (activate $A^{self}_{KNU}$ positively)
\end{itemize}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.2: Health and Prevention}
\label{subsubsec:awareness-health}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Smokers continue despite knowing health consequences. The discounted future 
benefit barely exceeds immediate costs.

\paragraph{Awareness Profile.}

\begin{table}[htbp]
\centering
\caption{Smoking Cessation: Awareness Analysis}
\label{tab:smoking-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llcll@{}}
\toprule
\textbf{Component} & \textbf{Content} & \textbf{$A$ Level} & \textbf{System} & \textbf{Why} \\
\midrule
$A^{self}_{INU,E,t=0}$ & Craving/withdrawal & \textbf{INSTANT = 1} & SYS 0 & Visceral \\
$A^{self}_{INU,P,t=3}$ & Health damage & LOW & SYS 2 & Abstract, distant \\
$A^{self}_{KNU}$ & Smoking group & HIGH & SYS 1 & Social belonging \\
$A^{self}_{IDN}$ & ``I'm a smoker'' & \textbf{INSTANT} & SYS 0/1 & Identity \\
$A^{comm}_{INU}$ & Family's health worry & LOW & SYS 2 & Requires empathy \\
$A^{comm}_{KNU}$ & Healthcare costs & VERY LOW & SYS 2 & Abstract collective \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{System Level Analysis.}
\begin{itemize}
\item \textbf{SYS 0 (Dominant):} Nicotine craving is visceral ($A = 1$ automatic)
\item \textbf{SYS 1 (Supporting):} Smoking identity and social belonging activated
\item \textbf{SYS 2 (Suppressed):} Health consequences require deliberate activation
and are competing against SYS 0 dominance
\end{itemize}

\paragraph{The Hyper-Dissonance Problem.}
\begin{equation}
A_{SYS0}(\text{craving}) = 1 \quad \Rightarrow \quad A_{SYS2}(\text{health}) < 1
\end{equation}

At the Moment of Truth (wanting a cigarette), the craving \emph{structurally 
suppresses} reflective awareness of health consequences.

\paragraph{Active Biases.}
\begin{itemize}
\item \textbf{Present Bias:} $A_{t=0}$ (craving) instant; $A_{t=3}$ (health) requires SYS 2
\item \textbf{Hot-Cold Empathy Gap:} When not craving (cold), overestimate ability 
to resist; when craving (hot), SYS 0 dominates
\item \textbf{Optimism Bias:} $A^{self}_{INU,P}$ suppressed by hope that ``it won't 
happen to me''
\item \textbf{Hyperbolic Discounting:} Immediate $A$ vastly outweighs future $A$
\end{itemize}

\paragraph{Why Information Campaigns Fail.}
Health information targets $A_{SYS2}$, but:
\begin{equation}
\text{At Moment of Truth: } A_{SYS0} = 1 \quad \Rightarrow \quad A_{SYS2} \text{ suppressed}
\end{equation}

The smoker \emph{knows} the facts (SYS 2 knowledge exists) but is not 
\emph{aware} of them at the decision moment (SYS 0 dominates).

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Smoking Cessation: Awareness-Based Interventions}
\label{tab:smoking-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A_{SYS0}$ reduction & Nicotine replacement & Reduce visceral craving intensity \\
$A^{self}_{IDN}$ & Identity shift & ``I am becoming a non-smoker'' \\
$A^{self}_{KNU}$ & New social group & Non-smoking support community \\
$A^{self}_{INU,P}$ to SYS 1 & Emotional activation & Graphic images, family impact \\
$A^{comm}_{INU}$ & Identifiable victim & ``Your daughter breathes this'' \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Health Awareness Insight:}
The smoker is caught in a SYS 0 trap: craving is visceral ($A = 1$), 
which structurally suppresses SYS 2 health awareness.

\textbf{Effective intervention must:}
\begin{itemize}
\item Reduce SYS 0 intensity (pharmacological support)
\item Elevate health consequences to SYS 1 (emotional, not just factual)
\item Create identity-level change ($A^{self}_{IDN}$: ``non-smoker'')
\item Provide social support ($A^{self}_{KNU}$: new community)
\end{itemize}
Information alone fails because it targets SYS 2, which is suppressed at 
the Moment of Truth.
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.3: Financial Decisions}
\label{subsubsec:awareness-finance}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
People systematically undersave despite knowing the benefits of saving.
Debt is taken on for non-financial utility (emotional, social, identity).

\paragraph{Awareness Profile.}

\begin{table}[htbp]
\centering
\caption{Saving Decision: Awareness Analysis}
\label{tab:saving-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llcll@{}}
\toprule
\textbf{Component} & \textbf{Content} & \textbf{$A$ Level} & \textbf{System} & \textbf{Why} \\
\midrule
$A^{self}_{INU,F,t=0}$ & Consumption now & \textbf{HIGH} & SYS 0/1 & Immediate pleasure \\
$A^{self}_{INU,F,t=3}$ & Retirement security & LOW & SYS 2 & Abstract, 30 years away \\
$A^{self}_{INU,E}$ & Retail therapy & \textbf{INSTANT} & SYS 0 & Emotional regulation \\
$A^{self}_{KNU}$ & Family experiences & HIGH & SYS 1 & Visible, emotional \\
$A^{self}_{IDN}$ & ``Good provider'' & HIGH & SYS 1 & Identity confirmation \\
$A^{comm}_{INU}$ & Family's future security & LOW & SYS 2 & Abstract \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{System Level Analysis.}
\begin{itemize}
\item \textbf{SYS 0/1 (Dominant):} Immediate consumption, emotional spending, 
identity as ``provider'' all operate at SYS 0/1
\item \textbf{SYS 2 (Weak):} Retirement is 30+ years away---maximum temporal 
discounting of awareness
\end{itemize}

\paragraph{The Temporal Awareness Gap.}
\begin{equation}
A^{self}_{INU,F,t=0}(t^*) \approx 1 \quad \text{vs.} \quad A^{self}_{INU,F,t=30years}(t^*) \approx 0
\end{equation}

The present is vivid and automatic; the future is abstract and requires 
deliberate construction.

\paragraph{Active Biases.}
\begin{itemize}
\item \textbf{Present Bias:} $A_{t=0}$ automatic; $A_{t=30}$ requires effortful imagination
\item \textbf{Hyperbolic Discounting:} Awareness decays hyperbolically with time
\item \textbf{Mental Accounting:} Different $A$ for different ``accounts''
\item \textbf{Status Quo Bias:} Current spending pattern requires no $A$; 
saving requires activation
\end{itemize}

\paragraph{Why Spending Isn't ``Irrational.''}
From the awareness perspective, spending serves functions with HIGH $A$:
\begin{itemize}
\item $A^{self}_{INU,E}$: Emotional regulation (SYS 0)
\item $A^{self}_{KNU}$: Family experiences (SYS 1)
\item $A^{self}_{IDN}$: ``I can afford this'' identity (SYS 1)
\end{itemize}

These are not ``irrational''---they are \emph{differently aware}.

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Saving: Awareness-Based Interventions}
\label{tab:saving-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A^{self}_{INU,F,t=3}$ to SYS 1 & Aging avatar & Emotional connection to future self \\
Bypass $A$ requirement & Auto-enrollment & Default removes need for $A$ activation \\
$A^{self}_{IDN}$ & ``Saver'' identity & ``People like you save X\%'' \\
$A^{self}_{KNU}$ & Family framing & ``Your grandchildren's education'' \\
$A^{self}_{INU,F,t=0}$ reframe & ``Pay yourself first'' & Saving = immediate self-investment \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Financial Awareness Insight:}
Undersaving reflects a temporal awareness asymmetry: present consumption 
is SYS 0/1 (automatic), future security is SYS 2 (effortful).

\textbf{The most effective intervention (auto-enrollment) works by 
bypassing awareness entirely}---if saving is the default, no $A$ 
activation is required.

This is the power of designing for habituation (AWX-A10): when the desired 
behavior requires no awareness, it happens automatically.
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.4: Sustainability and Climate}
\label{subsubsec:awareness-climate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Pro-environmental behavior requires personal sacrifice for collective benefit.
INU costs are instant; KNU benefits are never instant.

\paragraph{Awareness Profile.}

\begin{table}[htbp]
\centering
\caption{Climate Action: Awareness Analysis}
\label{tab:climate-awareness-detailed}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llcll@{}}
\toprule
\textbf{Component} & \textbf{Content} & \textbf{$A$ Level} & \textbf{System} & \textbf{Why} \\
\midrule
$A^{self}_{INU,F}$ & Cost of green behavior & \textbf{INSTANT} & SYS 0/1 & Immediate, felt \\
$A^{self}_{INU,E}$ & Inconvenience & \textbf{HIGH} & SYS 0/1 & Effort, discomfort \\
$A^{self}_{KNU}$ & ``For my family's future'' & MEDIUM & SYS 1/2 & Can be activated \\
$A^{self}_{IDN}$ & ``I'm environmentalist'' & Variable & SYS 1 & If identity exists \\
$A^{comm}_{INU}$ & Others affected by climate & LOW & SYS 2 & Abstract, distant \\
$A^{comm}_{KNU}$ & Global collective good & \textbf{NEVER INSTANT} & SYS 2 only & AWX-A37 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{The KNU-Never-Instant Problem.}
This domain perfectly illustrates AWX-A37:

\begin{equation}
A^{comm}_{KNU}(\text{climate benefit}) \text{ CANNOT be instant}
\end{equation}

\begin{itemize}
\item Climate benefit is collective ($KNU$)
\item Collective benefit is to abstract others ($comm$)
\item Abstract collective benefit to abstract others = maximum awareness distance
\end{itemize}

\paragraph{System Level Analysis.}
\begin{itemize}
\item \textbf{SYS 0/1:} Costs (money, effort, inconvenience) are instant
\item \textbf{SYS 2 only:} Benefits (climate mitigation) require deliberate, 
abstract, long-term thinking
\item \textbf{Hyper-Dissonance:} When costs activate SYS 0/1, SYS 2 benefits 
are suppressed
\end{itemize}

\paragraph{Active Biases.}
\begin{itemize}
\item \textbf{Tragedy of the Commons:} $A_{INU}$ instant, $A_{KNU}$ never instant
\item \textbf{Bystander Effect (Global):} ``My action doesn't matter'' = 
diffused $A^{comm}$ across 8 billion
\item \textbf{Temporal Discounting:} Climate effects 30-100 years away = 
$A$ approaching zero
\item \textbf{Construal Level:} Climate is psychologically distant on all 
dimensions (temporal, spatial, social, hypothetical)
\end{itemize}

\paragraph{The Scale Problem Through Awareness.}
\begin{equation}
A^{comm}_{KNU}(\text{my contribution}) = \frac{A^{comm}_{KNU}(\text{total})}{8 \times 10^9} \approx 0
\end{equation}

Even if someone activates $A^{comm}_{KNU}$, their \emph{individual} 
contribution is infinitesimal---awareness of this further reduces motivation.

\paragraph{Why Some People DO Act Pro-Environmentally.}
The awareness framework explains variation:

\begin{itemize}
\item \textbf{High $A^{self}_{IDN}$:} ``I am an environmentalist'' (identity-driven)
\item \textbf{Elevated $A^{self}_{KNU}$:} ``For my grandchildren'' (closer collective)
\item \textbf{$A^{comm}_{INU}$ activated:} Identifiable victim effect (specific 
affected person)
\end{itemize}

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Climate Action: Awareness-Based Interventions}
\label{tab:climate-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A^{self}_{IDN}$ & Identity building & ``Climate-conscious citizen'' \\
$A^{self}_{KNU}$ & Localize & ``Your community,'' ``your children'' \\
$A^{comm}_{INU}$ & Identifiable victim & Specific affected person, not statistics \\
$A^{self}_{INU}$ alignment & Co-benefits & ``Save money AND help climate'' \\
Bypass via social & Social proof & ``73\% of neighbors do this'' \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Climate Awareness Insight:}
Climate action faces the \textbf{maximum awareness asymmetry}:
\begin{itemize}
\item Costs: $A^{self}_{INU}$ = instant (SYS 0/1)
\item Benefits: $A^{comm}_{KNU}$ = never instant (SYS 2 only, AWX-A37)
\end{itemize}

\textbf{This is not a knowledge problem---it's an awareness problem.}
People \emph{know} about climate change; they are not \emph{aware} of it 
at the Moment of Truth (buying a car, choosing a flight, etc.).

\textbf{Effective intervention must:}
\begin{itemize}
\item Convert KNU to IDN (``environmentalist'' identity = instant)
\item Convert $A^{comm}$ to $A^{self}$ (``your grandchildren'')
\item Use identifiable victims (activate SYS 1 empathy)
\item Align INU with KNU (co-benefits)
\end{itemize}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.5: Digital Transformation}
\label{subsubsec:awareness-digital}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Employees resist digital transformation despite efficiency gains.
The identity threat ($A^{self}_{IDN}$) dominates the efficiency benefit ($A^{self}_{INU}$).

\paragraph{Awareness Profile.}

\begin{table}[htbp]
\centering
\caption{Digital Transformation: Awareness Analysis}
\label{tab:digital-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llcll@{}}
\toprule
\textbf{Component} & \textbf{Content} & \textbf{$A$ Level} & \textbf{System} & \textbf{Why} \\
\midrule
$A^{self}_{INU,E}$ & Learning stress & \textbf{INSTANT} & SYS 0 & Immediate discomfort \\
$A^{self}_{INU,F}$ (threat) & Job security fear & \textbf{HIGH} & SYS 1 & Fear-driven \\
$A^{self}_{INU,D}$ (gain) & Better tools & LOW & SYS 2 & Requires experience \\
$A^{self}_{IDN}$ & ``I'm becoming obsolete'' & \textbf{INSTANT} & SYS 0/1 & Identity threat \\
$A^{self}_{KNU}$ & Team disruption & HIGH & SYS 1 & Social bonds threatened \\
$A^{comm}_{INU}$ & Company benefit & LOW & SYS 2 & Abstract \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{System Level Analysis.}
\begin{itemize}
\item \textbf{SYS 0/1 (Dominant):} Identity threat (``obsolete'') and job fear 
are visceral/emotional
\item \textbf{SYS 2 (Suppressed):} Efficiency benefits require imagining a 
future state
\end{itemize}

\paragraph{The Expert's Dilemma.}
For experts in legacy systems:

\begin{equation}
A^{self}_{IDN}(\text{``I am the expert''}) + A^{self}_{INU}(\text{status from expertise}) >> A^{self}_{INU}(\text{new tool benefits})
\end{equation}

The new system \emph{erases} their source of identity and status.

\paragraph{Active Biases.}
\begin{itemize}
\item \textbf{Identity-Protective Cognition:} $A^{self}_{IDN}$ threat blocks 
rational evaluation
\item \textbf{Loss Aversion:} $A$(losing expertise) >> $A$(gaining new skills)
\item \textbf{Status Quo Bias:} Current system requires no $A$; new system 
requires massive $A$ activation
\item \textbf{Sunk Cost:} $A$ for past investment in old skills
\end{itemize}

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Digital Transformation: Awareness-Based Interventions}
\label{tab:digital-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A^{self}_{IDN}$ protection & Expertise bridge & ``Your domain knowledge is essential'' \\
$A^{self}_{INU,D}$ to SYS 1 & Quick wins & Immediate visible benefits \\
$A^{self}_{KNU}$ preservation & Team transition & ``We learn together'' \\
$A^{self}_{IDN}$ new & New identity & ``From Excel expert to data analyst'' \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Digital Transformation Awareness Insight:}
Resistance isn't about technology---it's about identity.

$A^{self}_{IDN}$ (``I'm becoming obsolete'') is \textbf{instant} (SYS 0/1),
while $A^{self}_{INU}$ (efficiency benefits) is \textbf{delayed} (SYS 2).

\textbf{Successful transformation requires:}
\begin{itemize}
\item Protect existing $A^{self}_{IDN}$ (honor past expertise)
\item Build new $A^{self}_{IDN}$ (identity evolution, not replacement)
\item Create early wins (move $A^{self}_{INU}$ to SYS 1)
\item Collective transition (maintain $A^{self}_{KNU}$)
\end{itemize}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.6: Organizational Culture}
\label{subsubsec:awareness-culture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Culture change is slow because it requires changing the $\gamma$-structure
(complementarities). Trust builds slowly.

\paragraph{Awareness Analysis of Trust.}
Trust is fundamentally an awareness phenomenon:

\begin{equation}
\text{Trust} = \text{stable } A^{self}_{KNU} + A^{comm}_{INU} + \text{positive } \gamma_{INU,KNU}
\end{equation}

In high-trust cultures:
\begin{itemize}
\item $A^{self}_{KNU}$ (group welfare) is habitually activated
\item $A^{comm}_{INU}$ (others' individual welfare) is considered
\item These are mutually reinforcing ($\gamma > 0$)
\end{itemize}

In low-trust cultures:
\begin{itemize}
\item $A^{self}_{INU}$ dominates (self-protection)
\item $A^{comm}_{INU}$ is low (assume others are self-interested)
\item $A^{self}_{KNU}$ requires deliberate activation
\end{itemize}

\paragraph{Why Culture Changes Slowly.}
From AWX-A2b (General Awareness as Learning Effect):

\begin{equation}
A_{gen}(t) = \sum_{\tau=0}^{t} \delta A_{mod}(\tau)
\end{equation}

General trust-related awareness builds only through \emph{repeated situational
activations}. Each positive experience adds incrementally; each betrayal 
subtracts substantially (loss aversion in $A$).

\paragraph{Active Biases in Low-Trust Cultures.}
\begin{itemize}
\item \textbf{Confirmation Bias:} $A$ for confirming distrust high; $A$ for 
disconfirming low
\item \textbf{Fundamental Attribution Error:} $A$ for others' bad behavior high;
$A$ for situational factors low
\item \textbf{Self-Fulfilling Prophecy:} Low $A^{comm}_{INU}$ → defensive 
behavior → confirms others' low $A^{comm}_{INU}$
\end{itemize}

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Culture Change: Awareness-Based Interventions}
\label{tab:culture-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A^{comm}_{INU}$ & Leader modeling & Visible trust-giving by leaders \\
$A^{self}_{KNU}$ to habit & Small wins & Low-stakes cooperation builds habit \\
$A^{comm}$ transparency & Transparent systems & Reduce uncertainty about others \\
$A^{self}_{IDN}$ & Shared identity first & ``We'' before behavior change \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Culture Awareness Insight:}
Culture = habitualized patterns of $A^{self}_{KNU}$ and $A^{comm}_{INU}$.

Culture change is slow because:
\begin{itemize}
\item Awareness habits build through repeated activation (AWX-A2b)
\item Loss aversion: one betrayal erases many trust-building moments
\item Confirmation bias: existing $A$ patterns are self-reinforcing
\end{itemize}

\textbf{Speed comes from:}
\begin{itemize}
\item Leadership modeling (high-visibility $A^{comm}$ demonstrations)
\item Structural changes (reduce need for interpersonal $A^{comm}$)
\item Shared identity (elevate $A^{self}_{IDN}$ which pulls $A^{self}_{KNU}$)
\end{itemize}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.7: Education and Human Capital}
\label{subsubsec:awareness-education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Adult learning has high barriers: opportunity costs, ego threat, identity 
conflict (``Students are young people'').

\paragraph{Awareness Profile.}

\begin{table}[htbp]
\centering
\caption{Adult Learning: Awareness Analysis}
\label{tab:education-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llcll@{}}
\toprule
\textbf{Component} & \textbf{Content} & \textbf{$A$ Level} & \textbf{System} & \textbf{Why} \\
\midrule
$A^{self}_{INU,F,t=0}$ & Cost (time, money) & \textbf{HIGH} & SYS 0/1 & Immediate \\
$A^{self}_{INU,C,t=3}$ & Future competence & LOW & SYS 2 & Abstract, delayed \\
$A^{self}_{IDN}$ (threat) & ``I should know this'' & \textbf{INSTANT} & SYS 0/1 & Ego threat \\
$A^{self}_{IDN}$ (conflict) & ``Not a student'' & HIGH & SYS 1 & Role conflict \\
$A^{self}_{KNU}$ & Career benefit for family & MEDIUM & SYS 2 & Can activate \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{The Expert's Learning Paradox.}
For established professionals:

\begin{equation}
A^{self}_{IDN}(\text{``I'm the expert''}) \text{ conflicts with } A^{self}_{IDN}(\text{``I'm a learner''})
\end{equation}

Learning requires adopting a ``beginner'' identity, which \emph{threatens} 
the ``expert'' identity.

\paragraph{Active Biases.}
\begin{itemize}
\item \textbf{Identity-Protective Cognition:} Expert identity blocks 
$A^{self}_{INU}$ for learning benefits
\item \textbf{Status Quo Bias:} Current knowledge requires no $A$; 
learning requires massive $A$ activation
\item \textbf{Present Bias:} Learning costs are now; benefits are later
\item \textbf{Sunk Cost:} $A$ for investment in existing expertise
\end{itemize}

\paragraph{Intervention Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Adult Learning: Awareness-Based Interventions}
\label{tab:education-intervention}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Target $A$} & \textbf{Strategy} & \textbf{Mechanism} \\
\midrule
$A^{self}_{IDN}$ protection & ``Upgrading'' frame & Not learning new, enhancing expertise \\
$A^{self}_{IDN}$ alignment & Peer learning & Adults teaching adults (preserve status) \\
$A^{self}_{INU,C}$ to SYS 1 & Immediate application & Show relevance to current role \\
$A^{self}_{INU,E}$ quick wins & Micro-credentials & Visible progress, reduced ego threat \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Education Awareness Insight:}
Adult learning barriers are primarily \textbf{identity-based}:

$A^{self}_{IDN}$ (``I'm supposed to be the expert'') creates instant 
resistance to learning, which requires adopting a ``beginner'' identity.

\textbf{Identity-safe learning:}
\begin{itemize}
\item Frame as ``enhancement'' not ``remediation''
\item Peer-to-peer (preserve expert status)
\item Immediate application (validate existing expertise)
\item Micro-credentials (visible progress without ``student'' identity)
\end{itemize}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.8: Public Policy}
\label{subsubsec:awareness-policy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Policies often fail because they target the wrong welfare component.
The $\Psi$-first sequence is often violated.

\paragraph{Awareness Analysis of Policy Failure.}
Many policies fail due to awareness asymmetries:

\begin{table}[htbp]
\centering
\caption{Policy Failures: Awareness Diagnosis}
\label{tab:policy-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Policy} & \textbf{Targets} & \textbf{Actual Barrier} & \textbf{$A$ Asymmetry} \\
\midrule
Health info & $A^{self}_{INU,P}$ SYS 2 & $A_{SYS0}$ (craving) & SYS 0 >> SYS 2 \\
Financial incentives & $A^{self}_{INU,F}$ & $A^{self}_{IDN}$ & IDN instant >> INU delayed \\
Carbon tax & $A^{self}_{INU,F}$ (cost) & $A^{comm}_{KNU}$ (benefit) & Self >> Comm; INU >> KNU \\
Retraining subsidy & $A^{self}_{INU,F}$ & $A^{self}_{IDN}$ & IDN instant >> INU delayed \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{The Awareness-Blind Policymaker.}
Policymakers often design for SYS 2:
\begin{itemize}
\item Assume citizens will ``calculate'' benefits
\item Provide information expecting behavioral change
\item Use financial incentives assuming $A^{self}_{INU,F}$ dominates
\end{itemize}

But at citizens' Moment of Truth:
\begin{itemize}
\item SYS 0/1 dominates SYS 2
\item $A^{self}_{IDN}$ and $A^{self}_{KNU}$ often override $A^{self}_{INU,F}$
\item $A^{comm}_{KNU}$ is never instant
\end{itemize}

\paragraph{Awareness-Informed Policy Design.}

\begin{table}[htbp]
\centering
\caption{Policy Design: Awareness Principles}
\label{tab:policy-design}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Principle} & \textbf{Application} \\
\midrule
Match system level & Design for SYS 0/1, not just SYS 2 \\
Match $A$ component & Target the actual barrier (often IDN, not INU) \\
Convert KNU to self & Localize collective benefits \\
Use identifiable victims & Activate SYS 1 empathy, not SYS 2 statistics \\
Design for habit & Remove need for $A$ (defaults, automation) \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Policy Awareness Insight:}
Most policy failures can be diagnosed as \textbf{awareness mismatches}:

\begin{itemize}
\item Policy targets SYS 2; citizens operate in SYS 0/1
\item Policy targets $A^{self}_{INU}$; barrier is $A^{self}_{IDN}$
\item Policy assumes $A^{comm}_{KNU}$; but KNU is never instant
\end{itemize}

\textbf{Awareness-informed policy:}
\begin{itemize}
\item Diagnose which $A$ component is actually relevant at Moment of Truth
\item Design interventions that match the dominant system level
\item Use defaults to bypass $A$ requirements entirely
\end{itemize}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Domain 10.9.9: Marketing and Consumer Behavior}
\label{subsubsec:awareness-marketing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The Puzzle (from Chapter 10).}
Marketing works by manipulating awareness components and reference points.
This raises ethical questions about welfare manipulation.

\paragraph{Marketing as Awareness Engineering.}
Marketing systematically manipulates all six $A$ components:

\begin{table}[htbp]
\centering
\caption{Marketing Techniques as Awareness Manipulation}
\label{tab:marketing-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Technique} & \textbf{Target $A$} & \textbf{System} & \textbf{Mechanism} \\
\midrule
Sex appeal & $A^{self}_{INU,E}$ & SYS 0 & Visceral activation \\
Fear appeal & $A^{self}_{INU,P}$ Pain & SYS 0/1 & Threat activation \\
Social proof & $A^{self}_{KNU}$ & SYS 1 & ``Everyone is doing it'' \\
Celebrity endorsement & $A^{self}_{IDN}$ & SYS 1 & Identity aspiration \\
Scarcity (``Only 3 left!'') & $A^{self}_{INU}$ (loss) & SYS 0 & Loss aversion trigger \\
``For people like you'' & $A^{self}_{IDN}$ & SYS 1 & Identity targeting \\
Identifiable beneficiary & $A^{comm}_{INU}$ & SYS 1 & Empathy activation \\
Community framing & $A^{self}_{KNU}$ & SYS 1 & Belonging appeal \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{The System Level Strategy.}
Effective marketing targets SYS 0/1 to bypass SYS 2:

\begin{equation}
\text{Marketing success} \propto \frac{A_{SYS0/1}(\text{product})}{A_{SYS2}(\text{evaluation})}
\end{equation}

The goal is to activate visceral/emotional awareness before rational 
evaluation can occur.

\paragraph{Active Biases Exploited.}
\begin{itemize}
\item \textbf{Availability Heuristic:} Make product mentally ``available''
\item \textbf{Affect Heuristic:} Create positive feelings → positive judgment
\item \textbf{Social Proof:} Activate $A^{self}_{KNU}$ (``everyone does this'')
\item \textbf{Loss Aversion:} Scarcity triggers $A$(loss) > $A$(gain)
\item \textbf{Identity:} ``This brand is who you are''
\end{itemize}

\paragraph{Ethical Analysis Through Awareness.}

\begin{table}[htbp]
\centering
\caption{Marketing Ethics: Awareness Perspective}
\label{tab:marketing-ethics}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Situation} & \textbf{$A$ Manipulation} & \textbf{Ethical Status} \\
\midrule
Information provision & $A$ for relevant features $\uparrow$ & Welfare-enhancing \\
Preference matching & $A$ for fit with true needs $\uparrow$ & Welfare-enhancing \\
SYS 0/1 hijacking & Bypass $A_{SYS2}$ (evaluation) & Welfare-reducing \\
False $A^{self}_{IDN}$ & ``You need this to be X'' & Welfare-reducing \\
Manufactured scarcity & Artificial $A$(loss) & Welfare-reducing \\
Addictive design & Permanent $A_{SYS0}$ activation & Severely welfare-reducing \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Consumer Defense Through Awareness.}
Understanding the awareness framework enables consumers to:
\begin{itemize}
\item Recognize when SYS 0/1 is being targeted
\item Deliberately activate SYS 2 before purchase decisions
\item Question artificially created $A^{self}_{IDN}$ (``Do I really need this 
to be who I am?'')
\item Notice $A^{self}_{KNU}$ manipulation (``Is everyone really doing this?'')
\end{itemize}

\paragraph{Key Insight.}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black]
\textbf{Marketing Awareness Insight:}
Marketing is \textbf{applied awareness manipulation}:
\begin{itemize}
\item Target SYS 0/1 to bypass SYS 2 evaluation
\item Activate $A^{self}_{IDN}$ (``This is who you are'')
\item Trigger $A$(loss) through artificial scarcity
\item Create $A^{self}_{KNU}$ through social proof
\end{itemize}

\textbf{The ethical criterion:}
Does the marketing increase awareness of \emph{genuine} utility fit,
or does it create \emph{artificial} awareness asymmetries that lead
to purchases misaligned with true welfare?

\textbf{Consumer literacy:}
Understanding the awareness framework is a defense against manipulation.
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Summary: Nine Domains Through the Awareness Lens}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
\centering
\caption{Nine Domains: Awareness Diagnosis Summary}
\label{tab:nine-domains-awareness}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}clll@{}}
\toprule
\textbf{\#} & \textbf{Domain} & \textbf{Key $A$ Asymmetry} & \textbf{Intervention Focus} \\
\midrule
1 & Labor & $A^{self}_{IDN}$ instant >> $A^{self}_{INU}$ delayed & Identity bridge \\
2 & Health & $A_{SYS0}$ (craving) >> $A_{SYS2}$ (health) & Reduce SYS 0; elevate to SYS 1 \\
3 & Finance & $A_{t=0}$ >> $A_{t=30years}$ & Defaults; future self salience \\
4 & Climate & $A^{self}_{INU}$ instant; $A^{comm}_{KNU}$ never & Convert to IDN or self-KNU \\
5 & Digital & $A^{self}_{IDN}$ (threat) >> $A^{self}_{INU}$ (gain) & Protect identity; quick wins \\
6 & Culture & $A^{self/comm}$ build slowly & Leader modeling; small wins \\
7 & Education & $A^{self}_{IDN}$ (expert) blocks learning & Identity-safe framing \\
8 & Policy & SYS 2 design vs. SYS 0/1 reality & Match system level \\
9 & Marketing & Manipulates all $A$ components & Consumer awareness literacy \\
\bottomrule
\end{tabular}
\end{table}

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black, title=Cross-Domain Awareness Patterns]

\textbf{Pattern 1: SYS 0/1 vs. SYS 2}
\begin{itemize}
\item Barriers are usually SYS 0/1 (instant, visceral, emotional)
\item Interventions often mistakenly target SYS 2 (information, calculation)
\end{itemize}

\textbf{Pattern 2: Self vs. Community}
\begin{itemize}
\item $A^{self}$ is high by default
\item $A^{comm}$ requires deliberate activation
\item KNU is \emph{never} instant---this is the deepest asymmetry
\end{itemize}

\textbf{Pattern 3: INU vs. IDN}
\begin{itemize}
\item IDN effects are often instant (identity threat/confirmation)
\item INU effects are often delayed (financial, health benefits)
\item $A^{self}_{IDN}$ frequently overrides $A^{self}_{INU}$
\end{itemize}

\textbf{Pattern 4: Present vs. Future}
\begin{itemize}
\item $A_{t=0}$ is automatic (SYS 0/1)
\item $A_{t>0}$ requires effortful construction (SYS 2)
\item This creates systematic present bias across all domains
\end{itemize}

\textbf{The Master Intervention Principle:}
\begin{center}
\emph{Move the desired outcome's awareness to a faster system level\\
and/or a closer position on the gradient.}
\end{center}

\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF APPLICATIONS REVISITED SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
