\section{Awareness: The Transformation Condition}
\label{sec:awareness}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 11: The Awareness Function (AWX)
% Module 7240 in BEATRIX Architecture
% Integrates: Content Definition + Functional Specification + System Levels
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Chapter~\ref{sec:fepsde-utility} established what \emph{could} generate utility:
144 components across three categories (INU, KNU, IDN), six dimensions (FEPSDE),
four time horizons, and two valences. But this represents \emph{potential} utility.
In any actual decision moment, only a subset of this potential becomes effective.

This chapter introduces the \textbf{Awareness Function}: the necessary condition
for transforming potential utility into effective utility at the Moment of Truth.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Definition: What Is Awareness?}
\label{subsec:awareness-definition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Awareness requires two complementary definitions: a \emph{content definition}
(what awareness is about) and a \emph{functional definition} (how awareness operates).

\subsubsection{The Content Definition}

\begin{definition}[Awareness -- Content]
\label{def:awareness-content}
\textbf{Awareness} is the consciousness of the positive and negative effects 
on one's own utility level (INU, KNU, IDN) and on the utility level (INU, KNU, IDN) 
of a relevant community, that a person has at the moment of decision or 
exhibited behavior.
\end{definition}

\paragraph{In German:}
\textit{Awareness ist das Bewusstsein über die positiven und negativen Effekte 
für das eigene Nutzenlevel (INU, KNU, IDN) und das Nutzenlevel (INU, KNU, IDN) 
einer relevanten Community, die ein Mensch im Moment der Entscheidung / 
des gezeigten Verhaltens hat.}

\subsubsection{The Functional Definition}

\begin{definition}[Awareness -- Function]
\label{def:awareness-function}
\textbf{Awareness} is the necessary condition for transforming potential utility
into effective utility at the Moment of Truth ($t^*$).
\end{definition}

\paragraph{The Core Formula:}
\begin{equation}
\boxed{U_{eff,X}(t^*) = U_{pot,X}(t^*) \times A_X(t^*)}
\label{eq:awareness-transformation}
\end{equation}

where:
\begin{itemize}
\item $U_{pot,X}$: Potential utility of type $X \in \{INU, KNU, IDN\}$
\item $U_{eff,X}$: Effective utility (actually guides behavior)
\item $A_X(t^*)$: Awareness level at Moment of Truth
\item $A_X \in [0, 1]$: Continuous from no awareness to full awareness
\end{itemize}

\subsubsection{How the Two Definitions Connect}

\begin{table}[htbp]
\centering
\caption{Connection: Content and Functional Definitions}
\label{tab:definition-connection}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}lp{5cm}p{5cm}@{}}
\toprule
\textbf{Element} & \textbf{Content Definition} & \textbf{Functional Definition} \\
\midrule
\textbf{What} & Consciousness of effects on utility & Transformation condition \\
\textbf{Target} & Own + Community utility levels & $U_{pot} \rightarrow U_{eff}$ \\
\textbf{Scope} & All three categories (INU, KNU, IDN) & $X \in \{INU, KNU, IDN\}$ \\
\textbf{Valence} & Positive AND negative effects & Gains and Pains in $U_{pot}$ \\
\textbf{Time} & Moment of decision/behavior & $t^*$ (Moment of Truth) \\
\bottomrule
\end{tabular}
\end{table}

The content definition answers \emph{what} awareness is about.
The functional definition answers \emph{how} awareness operates.
Both are essential for understanding and applying the construct.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Moment of Truth}
\label{subsec:moment-of-truth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Definition}

\begin{definition}[Moment of Truth]
\label{def:moment-of-truth}
The \textbf{Moment of Truth} ($t^*$) is the decision point at which potential 
utility can be transformed into behavior through awareness.
\end{definition}

\paragraph{Formal Condition:}
\begin{equation}
A_X(t^*) > 0 \quad \Leftrightarrow \quad \text{Decision active} \wedge \text{Context salience} > \theta_{awareness}
\end{equation}

\subsubsection{Critical Properties}

\paragraph{Property 1: Situativity.}
Awareness operates \emph{only} at $t^*$, not before or after:

\begin{equation}
A_X(t) = 0 \quad \text{for all } t \neq t^*
\end{equation}

This distinguishes awareness from:
\begin{itemize}
\item \textbf{Knowledge}: Can exist without being active
\item \textbf{Attitudes}: Stable but not situation-specific
\item \textbf{Intentions}: Future-oriented, not present-focused
\end{itemize}

\paragraph{Property 2: Contextual Activation.}
Awareness at $t^*$ depends on context:

\begin{equation}
A_{SYS_i}(t^*) = f(C(t^*), Norm(t^*), Emotion(t^*), \sigma_U(t^*))
\end{equation}

where:
\begin{itemize}
\item $C(t^*)$: Current context configuration
\item $Norm(t^*)$: Active social norms
\item $Emotion(t^*)$: Current emotional state
\item $\sigma_U(t^*)$: Utility salience
\end{itemize}

\paragraph{Property 3: No Persistence.}
Awareness does not automatically persist:

\begin{equation}
A_X(t^* + \Delta t) \neq A_X(t^*)
\end{equation}

A new moment requires new activation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Three System Levels: SYS 0, SYS 1, SYS 2}
\label{subsec:system-levels}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Awareness operates across three distinct system levels, following the
tradition of Loewenstein's visceral factors and Kahneman's dual-process theory,
extended to a triple-process model.

\subsubsection{Overview}

\begin{table}[htbp]
\centering
\caption{Three System Levels of Awareness}
\label{tab:system-levels}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Level} & \textbf{Name} & \textbf{Definition} & \textbf{Speed} \\
\midrule
SYS 0 & Instant/Visceral & Automatic activation without conscious processing & Milliseconds \\
SYS 1 & Affective/Emotional & Emotional awareness of meaning and social resonance & Seconds \\
SYS 2 & Reflective/Cognitive & Cognitive awareness of consequences and rules & Minutes \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{SYS 0: Instant Awareness}

\paragraph{Definition.}
Automatic visceral activation without conscious processing.

\paragraph{Formal Condition:}
\begin{equation}
A_{SYS0} = 1 \quad \text{upon immediate sensory or affective reaction}
\end{equation}

\paragraph{Examples:}
\begin{itemize}
\item Pain stimulus → Immediate awareness of physical threat
\item Hunger → Immediate awareness of nutritional need
\item Sexual arousal → Immediate awareness of opportunity/threat
\item Startle reflex → Immediate danger awareness
\end{itemize}

\paragraph{Characteristics:}
\begin{itemize}
\item No cognitive mediation required
\item Evolutionarily hardwired
\item Cannot be suppressed (only regulated after the fact)
\item Dominant over SYS 1 and SYS 2 when activated
\end{itemize}

\subsubsection{SYS 1: Affective Awareness}

\paragraph{Definition.}
Emotional awareness of meaning and social resonance of one's own behavior.

\paragraph{Formal Condition:}
\begin{equation}
A_{SYS1} = f(Emotion_{valence}, Social_{feedback})
\end{equation}

\paragraph{Examples:}
\begin{itemize}
\item Guilt → Awareness of harm caused to others
\item Pride → Awareness of achievement and social standing
\item Shame → Awareness of norm violation and social exposure
\item Compassion → Awareness of others' suffering
\item Envy → Awareness of relative deprivation
\end{itemize}

\paragraph{Characteristics:}
\begin{itemize}
\item Rapid but not instantaneous
\item Socially calibrated
\item Can be influenced by context and framing
\item Interacts with both SYS 0 and SYS 2
\end{itemize}

\subsubsection{SYS 2: Reflective Awareness}

\paragraph{Definition.}
Cognitive awareness of consequences, rules, and normative implications.

\paragraph{Formal Condition:}
\begin{equation}
A_{SYS2} = f(Causal_{understanding}, Rule_{clarity}, Evidence_{clarity})
\end{equation}

\paragraph{Examples:}
\begin{itemize}
\item Calculating ROI before investment → Financial consequence awareness
\item Considering ethical implications → Moral consequence awareness
\item Anticipating others' reactions → Social consequence awareness
\item Weighing long-term health effects → Temporal consequence awareness
\end{itemize}

\paragraph{Characteristics:}
\begin{itemize}
\item Slow and effortful
\item Requires cognitive capacity
\item Vulnerable to depletion and load
\item Can override SYS 0 and SYS 1 (with effort)
\end{itemize}

\subsubsection{System Level Interaction}

\paragraph{The Constraint.}
Awareness cannot be simultaneously maximal in SYS 0 and SYS 2:

\begin{equation}
A_{SYS0}(t^*) = 1 \quad \Rightarrow \quad A_{SYS2}(t^*) < 1 \quad \text{(Hyper-Dissonance Rule)}
\end{equation}

When visceral reactions dominate, reflection is suppressed.

\paragraph{Transition Dynamics.}
Awareness can shift across system levels:

\begin{equation}
SYS0 \rightarrow SYS1 \rightarrow SYS2 \quad \text{(Ascending: from reflex to reflection)}
\end{equation}

\begin{equation}
SYS2 \rightarrow SYS1 \rightarrow SYS0 \quad \text{(Descending: from deliberation to automaticity)}
\end{equation}

\paragraph{Example: Smoking Cessation.}
\begin{enumerate}
\item SYS 0: Craving (visceral urge to smoke)
\item SYS 1: Guilt (emotional response to breaking commitment)
\item SYS 2: Reflection (considering health consequences)
\end{enumerate}

Successful cessation requires SYS 2 awareness to override SYS 0 craving.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Two-Level Awareness Structure: Self and Community}
\label{subsec:two-level-structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From the content definition, awareness encompasses effects on \emph{both}
one's own utility \emph{and} the utility of a relevant community.

\subsubsection{The Complete Awareness Matrix}

\begin{equation}
\boxed{
\mathbf{A} = \begin{pmatrix}
A^{self}_{INU} & A^{self}_{KNU} & A^{self}_{IDN} \\
A^{comm}_{INU} & A^{comm}_{KNU} & A^{comm}_{IDN}
\end{pmatrix}
}
\label{eq:awareness-matrix}
\end{equation}

\begin{table}[htbp]
\centering
\caption{The Complete Awareness Matrix: Six Components}
\label{tab:awareness-matrix-complete}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{}l|ccc@{}}
\toprule
& \textbf{INU} & \textbf{KNU} & \textbf{IDN} \\
\midrule
\textbf{Own utility} & $A^{self}_{INU}$ & $A^{self}_{KNU}$ & $A^{self}_{IDN}$ \\
& Effects on MY welfare & Effects on OUR group & Effects on WHO I AM \\
\midrule
\textbf{Community utility} & $A^{comm}_{INU}$ & $A^{comm}_{KNU}$ & $A^{comm}_{IDN}$ \\
& Effects on THEIR welfare & Effects on THEIR groups & Effects on WHO THEY ARE \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Six Awareness Questions}

\begin{table}[htbp]
\centering
\caption{The Six Awareness Questions}
\label{tab:six-questions}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Component} & \textbf{Question} & \textbf{Focus} \\
\midrule
$A^{self}_{INU}$ & What does this do for ME? & Personal gains/pains \\
$A^{self}_{KNU}$ & What does this do for US? & Group welfare I belong to \\
$A^{self}_{IDN}$ & What does this say about WHO I AM? & Identity confirmation/threat \\
$A^{comm}_{INU}$ & What does this do for THEM? & Others' personal welfare \\
$A^{comm}_{KNU}$ & What does this do for THEIR groups? & Others' collective welfare \\
$A^{comm}_{IDN}$ & What does this do to WHO THEY ARE? & Others' identity \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{The Awareness Gradient}

There is a systematic gradient in default awareness levels:

\begin{equation}
A^{self}_{INU} > A^{self}_{KNU} > A^{self}_{IDN} > A^{comm}_{INU} > A^{comm}_{KNU} > A^{comm}_{IDN}
\end{equation}

\begin{table}[htbp]
\centering
\caption{Default Awareness Levels}
\label{tab:default-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Component} & \textbf{Default Level} & \textbf{Activation Required} \\
\midrule
$A^{self}_{INU}$ & HIGH & Minimal \\
$A^{self}_{KNU}$ & MEDIUM & Group cues \\
$A^{self}_{IDN}$ & LOW-MEDIUM & Value conflict \\
$A^{comm}_{INU}$ & LOW & Perspective-taking \\
$A^{comm}_{KNU}$ & VERY LOW & Extended empathy \\
$A^{comm}_{IDN}$ & VERY LOW & Deep empathy \\
\bottomrule
\end{tabular}
\end{table}

This gradient explains why:
\begin{itemize}
\item Self-interest dominates by default
\item Collective concerns require deliberate activation
\item Others' welfare requires perspective-taking effort
\item Others' identity is rarely considered
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Instant Exception Rule}
\label{subsec:instant-exception}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Not all utility effects require conscious awareness. Some are automatically
activated through SYS 0 or SYS 1 processes.

\subsubsection{The Three Cases}

\begin{table}[htbp]
\centering
\caption{Instant Exception Rules by Utility Category}
\label{tab:instant-exceptions}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Category} & \textbf{Instant Possible?} & \textbf{Condition} & \textbf{Awareness} \\
\midrule
INU & YES & Physiologically immediate & $A_{INU}(t^*) = 1$ automatic \\
IDN & YES & Socially-emotionally immediate & $A_{IDN}(t^*) = 1$ automatic \\
KNU & \textbf{NO} & Always requires awareness & $A_{KNU}(t^*) < 1$ without awareness \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Instant INU}

\begin{axiom}[AWX-A35: Instant INU]
\label{ax:instant-inu}
Physiologically immediate individual utility effects do not require awareness.
\end{axiom}

\paragraph{Formal:}
\begin{equation}
\text{If } U_{pot,INU} \in \{\text{physiologically immediate}\} \Rightarrow A_{INU}(t^*) = 1
\end{equation}

\paragraph{Examples:}
\begin{itemize}
\item Pain → Immediate $U^{INU}_P$ impact
\item Hunger → Immediate $U^{INU}_P$ impact
\item Fatigue → Immediate $U^{INU}_P$ impact
\item Dopamine hit → Immediate $U^{INU}_E$ impact
\item Sexual arousal → Immediate $U^{INU}_E$ impact
\end{itemize}

\subsubsection{Instant IDN}

\begin{axiom}[AWX-A36: Instant IDN]
\label{ax:instant-idn}
Socially-emotionally immediate identity effects do not require awareness.
\end{axiom}

\paragraph{Formal:}
\begin{equation}
\text{If } U_{pot,IDN} \in \{\text{socially-emotionally immediate}\} \Rightarrow A_{IDN}(t^*) = 1
\end{equation}

\paragraph{Examples:}
\begin{itemize}
\item Applause → Immediate identity confirmation
\item Public shaming → Immediate identity threat
\item Group exclusion → Immediate belonging threat
\item Recognition by respected figure → Immediate status boost
\item Visible symbols of status → Immediate identity activation
\end{itemize}

\subsubsection{No Instant KNU}

\begin{axiom}[AWX-A37: No Instant KNU]
\label{ax:no-instant-knu}
Collective utility effects are \textbf{never} instant. All KNU effects require awareness.
\end{axiom}

\paragraph{Formal:}
\begin{equation}
\forall U_{pot,KNU}: A_{KNU}(t^*) < 1 \text{ without explicit awareness}
\end{equation}

\paragraph{Reason:}
Collective welfare is inherently abstract. It cannot be:
\begin{itemize}
\item Felt in the body (unlike INU)
\item Experienced through social-emotional reaction (unlike IDN)
\item Perceived without cognitive mediation
\end{itemize}

\paragraph{Critical Implication:}
\textbf{KNU is always awareness-pflichtig (awareness-mandatory).}

This explains why:
\begin{itemize}
\item Environmental behavior is hard (KNU_Eco requires SYS 2)
\item Public goods are underprovided (KNU_collective invisible)
\item Commons tragedies occur (individual INU instant, collective KNU not)
\end{itemize}

\subsubsection{Mediated Instant KNU}

While direct instant KNU is impossible, KNU can become \emph{indirectly} instant
through IDN or empathy:

\begin{equation}
A_{KNU,instant} = f(A_{IDN,instant}) \quad \text{or} \quad f(Empathy_{immediate})
\end{equation}

\paragraph{Example:}
A parent sees their child in danger:
\begin{itemize}
\item Direct: $U^{KNU}_{family}$ (not instant)
\item Mediated: $U^{IDN}_{parent}$ triggers instant response
\end{itemize}

The parent acts ``for the group'' but through identity, not through direct
collective utility awareness.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Complete Transformation Equation}
\label{subsec:complete-transformation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Full Effective Welfare}

Combining all elements, effective welfare at the Moment of Truth is:

\begin{equation}
\boxed{
Q^{eff}(t^*) = \sum_{j \in \{self, comm\}} \sum_{X \in \{INU, KNU, IDN\}} A^j_X(t^*) \times \omega^j_X \times U^j_{pot,X}(t^*)
}
\label{eq:effective-welfare-complete}
\end{equation}

\paragraph{Expanded Form:}
\begin{align}
Q^{eff}(t^*) = \quad & A^{self}_{INU}(t^*) \cdot \omega^{self}_{INU} \cdot U^{self}_{pot,INU}(t^*) \nonumber \\
+ \quad & A^{self}_{KNU}(t^*) \cdot \omega^{self}_{KNU} \cdot U^{self}_{pot,KNU}(t^*) \nonumber \\
+ \quad & A^{self}_{IDN}(t^*) \cdot \omega^{self}_{IDN} \cdot U^{self}_{pot,IDN}(t^*) \nonumber \\
+ \quad & A^{comm}_{INU}(t^*) \cdot \omega^{comm}_{INU} \cdot U^{comm}_{pot,INU}(t^*) \nonumber \\
+ \quad & A^{comm}_{KNU}(t^*) \cdot \omega^{comm}_{KNU} \cdot U^{comm}_{pot,KNU}(t^*) \nonumber \\
+ \quad & A^{comm}_{IDN}(t^*) \cdot \omega^{comm}_{IDN} \cdot U^{comm}_{pot,IDN}(t^*)
\end{align}

\subsubsection{The Three Multiplicative Factors}

Behavior is determined by the product of three factors:

\begin{equation}
\text{Effective contribution} = A \times \omega \times U_{pot}
\end{equation}

\begin{table}[htbp]
\centering
\caption{Three Factors Determining Behavioral Impact}
\label{tab:three-factors}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Factor} & \textbf{Symbol} & \textbf{Question} & \textbf{Changeability} & \textbf{System} \\
\midrule
Awareness & $A$ & Am I thinking about it? & Fast (situational) & SYS 0-1-2 \\
Weight & $\omega$ & How much do I care? & Slow (values) & Stable trait \\
Potential Utility & $U_{pot}$ & How large is the effect? & Designable & External \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Intervention Implications:}
\begin{itemize}
\item \textbf{Change $A$:} Nudges, framing, reminders, salience (fast, fragile)
\item \textbf{Change $\omega$:} Education, value formation, identity work (slow, lasting)
\item \textbf{Change $U_{pot}$:} Incentive design, policy, environmental change
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 1: Fundamental Axioms}
\label{subsec:axioms-fundamental}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{AWX-A1: Transformation Condition}

\begin{axiom}[AWX-A1: Awareness as Transformation Condition]
\label{ax:awx-a1}
Potential utility becomes effective only when awareness $> 0$ at $t^*$.
\end{axiom}

\begin{equation}
U_{eff,X}(t^*) = U_{pot,X}(t^*) \times A_X(t^*)
\end{equation}

\begin{equation}
A_X(t^*) > 0 \quad \Leftrightarrow \quad \text{Behavior active}
\end{equation}

\paragraph{Sub-axioms:}

\begin{itemize}
\item \textbf{AWX-A1a (Community Relevance):} Awareness includes consciousness 
that own behavior affects the utility of a relevant community.
\begin{equation}
A_{mod}(t) > 0 \Leftrightarrow \exists (U^{KNU}(t) \vee U^{IDN}(t)) \wedge C_{rel}
\end{equation}

\item \textbf{AWX-A1b (External Effects):} Awareness is only behaviorally effective
when effects on collective or identity utility of a relevant community are recognized.

\item \textbf{AWX-A1c (Delayed Individual Utility):} Awareness includes individual
utility with delayed effects that must be made anticipatorily salient.
\begin{equation}
A_{mod}(t) > 0 \Rightarrow U^{INU}(t+h) \text{ salient when } h > \theta_{instant}
\end{equation}
\end{itemize}

\subsubsection{AWX-A2: Moment of Truth}

\begin{axiom}[AWX-A2: Situativity]
\label{ax:awx-a2}
Awareness operates exclusively at the moment of decision.
\end{axiom}

\begin{equation}
A_X(t) = 0 \quad \text{for all } t \neq t^*
\end{equation}

\paragraph{Sub-axioms:}

\begin{itemize}
\item \textbf{AWX-A2a (Situational Activation):} Only context-specific triggered 
awareness is effective.
\begin{equation}
A_{mod}(t) = 1 \text{ only when } Trigger_{ctx}(t) = true
\end{equation}

\item \textbf{AWX-A2b (General Awareness as Learning Effect):} General awareness 
arises exclusively through repeated situational activation.
\begin{equation}
A_{gen}(t) = \sum_{\tau=0}^{t} \delta A_{mod}(\tau)
\end{equation}

\item \textbf{AWX-A2c (Dynamic Salience):} Awareness changes depending on the 
temporal dynamics of perceived context.
\begin{equation}
\sigma_{dyn}(C_i, t) = \sigma_0(C_i) + \rho \cdot \frac{dC_i}{dt}
\end{equation}
\end{itemize}

\subsubsection{AWX-A3: Positive and Negative Impact}

\begin{axiom}[AWX-A3: Dual Valence]
\label{ax:awx-a3}
Awareness necessarily encompasses both positive and negative effects of behavior.
\end{axiom}

\begin{equation}
U_{eff,X}(t^*) = (U_{pot,positive,X} + U_{pot,negative,X}) \times A_X(t^*)
\end{equation}

\subsubsection{AWX-A4: Instant Exceptions}

\begin{axiom}[AWX-A4: Instant Utility Exceptions]
\label{ax:awx-a4}
Certain utility effects occur instantly without awareness (INU\_instant, IDN\_instant).
Collective utility is never instant.
\end{axiom}

\begin{equation}
\text{If } X \in \{INU_{instant}, IDN_{instant}\} \Rightarrow A_X(t^*) = 1
\end{equation}
\begin{equation}
\text{If } X = KNU \Rightarrow \text{Awareness mandatory}
\end{equation}

\subsubsection{AWX-A5: General vs. Situational}

\begin{axiom}[AWX-A5: Situational Primacy]
\label{ax:awx-a5}
Only situational impact-awareness at the Moment of Truth is behaviorally effective.
\end{axiom}

\begin{equation}
A_{general} \neq A_{situational}; \text{ only } A_{situational}(t^*) \text{ relevant}
\end{equation}

\subsubsection{AWX-A6 to AWX-A10}

\begin{itemize}
\item \textbf{AWX-A6 (Individual Differences):} Awareness levels vary between 
individuals due to cognitive, emotional, social, and biological factors.

\item \textbf{AWX-A7 (Context Dependence):} Awareness is completely context-bound.
$A_X(t^*) = f(C(t))$

\item \textbf{AWX-A8 (Capacity Limitation):} Awareness is limited by attention capacity.
$\sum A_X(t^*) \leq Capacity_{limit}$

\item \textbf{AWX-A9 (Salience and Priming):} Awareness arises only when utility 
is salient or activated through priming.

\item \textbf{AWX-A10 (Habituation):} Habitualized behavioral patterns require 
no awareness. When behavior is habitualized $\Rightarrow A_X(t^*) \approx 0$.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 2: Determinants of Awareness}
\label{subsec:axioms-determinants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Twenty determinants influence awareness levels (AWX-A11 to AWX-A30):

\subsubsection{Cognitive Determinants}

\begin{table}[htbp]
\centering
\caption{Cognitive Determinants of Awareness}
\label{tab:cognitive-determinants}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Axiom} & \textbf{Determinant} & \textbf{Effect} & \textbf{Formula} \\
\midrule
AWX-A11 & Attention span & $\uparrow$ with capacity & $A \propto Attention_{capacity}$ \\
AWX-A12 & Cognitive load & $\downarrow$ with load & $A = f(-Cognitive_{load})$ \\
AWX-A13 & Evidence clarity & $\uparrow$ with clarity & $A \propto Evidence_{clarity}$ \\
AWX-A14 & Availability heuristic & $\uparrow$ with availability & $A \propto Availability(X)$ \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Emotional Determinants}

\begin{table}[htbp]
\centering
\caption{Emotional Determinants of Awareness}
\label{tab:emotional-determinants}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Axiom} & \textbf{Determinant} & \textbf{Effect} & \textbf{Formula} \\
\midrule
AWX-A15 & Emotional valence & $\uparrow$ with intensity & $A = f(Emotion_{valence})$ \\
AWX-A16 & Fear & $\uparrow$ for negative impact & $A \propto Fear_{intensity}$ \\
AWX-A17 & Hope & $\uparrow$ for positive impact & $A \propto Hope_{intensity}$ \\
AWX-A18 & Affective resonance & $\uparrow$ with resonance & $A = f(Affect_{resonance})$ \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Social Determinants}

\begin{table}[htbp]
\centering
\caption{Social Determinants of Awareness}
\label{tab:social-determinants}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Axiom} & \textbf{Determinant} & \textbf{Effect} & \textbf{Formula} \\
\midrule
AWX-A19 & Norm pressure & $\uparrow$ with pressure & $A \propto Norm_{pressure}$ \\
AWX-A20 & Social mirroring & $\uparrow$ with visibility & $A \propto Peer_{visibility}$ \\
AWX-A21 & Network effects & $\uparrow$ with exposure & $A \propto Network_{exposure}$ \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Institutional Determinants}

\begin{table}[htbp]
\centering
\caption{Institutional Determinants of Awareness}
\label{tab:institutional-determinants}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Axiom} & \textbf{Determinant} & \textbf{Effect} & \textbf{Formula} \\
\midrule
AWX-A22 & Institutional legitimacy & $\uparrow$ with legitimacy & $A \propto Institutional_{trust}$ \\
AWX-A23 & Institutional trust & $\downarrow$ without trust & $A = f(Institutional_{trust})$ \\
AWX-A24 & Rule clarity & $\uparrow$ with clarity & $A \propto Rule_{clarity}$ \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Cultural and Biological Determinants}

\begin{table}[htbp]
\centering
\caption{Cultural and Biological Determinants}
\label{tab:cultural-biological}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Axiom} & \textbf{Determinant} & \textbf{Effect} & \textbf{Formula} \\
\midrule
AWX-A25 & Cultural narratives & $\uparrow$ with embeddedness & $A \propto Narrative_{strength}$ \\
AWX-A26 & Symbols \& rituals & $\uparrow$ with salience & $A \propto Symbolic_{salience}$ \\
AWX-A27 & Priming effects & $\uparrow$ with priming & $A = f(Priming)$ \\
AWX-A28 & Biological factors & Variable & $A = f(Bio_{traits})$ \\
AWX-A29 & Energy state & $\uparrow$ with energy & $A \propto Energy_{level}$ \\
AWX-A30 & Interactive effects & Multiplicative & $A = f(D_1 \times D_2 \times \ldots)$ \\
\bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 3: Utility-Specific Awareness}
\label{subsec:axioms-utility-specific}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Category Definitions}

\begin{axiom}[AWX-A31: Awareness INU]
\label{ax:awx-a31}
Awareness for individual utility is consciousness that own behavior has 
positive or negative influence on own individual utility.
\end{axiom}

\begin{equation}
U_{eff,INU}(t^*) = U_{pot,INU}(t^*) \times A_{INU}(t^*)
\end{equation}

\begin{axiom}[AWX-A32: Awareness KNU]
\label{ax:awx-a32}
Awareness for collective utility is consciousness that own behavior has 
positive or negative influence on the utility of a community or group.
\end{axiom}

\begin{equation}
U_{eff,KNU}(t^*) = U_{pot,KNU}(t^*) \times A_{KNU}(t^*)
\end{equation}

\begin{axiom}[AWX-A33: Awareness IDN]
\label{ax:awx-a33}
Awareness for identity utility is consciousness that own behavior has 
positive or negative influence on belonging, recognition, or identity.
\end{axiom}

\begin{equation}
U_{eff,IDN}(t^*) = U_{pot,IDN}(t^*) \times A_{IDN}(t^*)
\end{equation}

\subsubsection{Category Differentiation}

\begin{axiom}[AWX-A34: Awareness Hierarchy]
\label{ax:awx-a34}
Awareness differs by utility type: INU is strongest, KNU is weakest, 
IDN is highly context-dependent.
\end{axiom}

\begin{equation}
A_{INU} > A_{IDN} > A_{KNU} \quad \text{(on average)}
\end{equation}

\begin{axiom}[AWX-A41: Conflict Dominance]
\label{ax:awx-a41}
In conflict, INU awareness dominates over IDN, and IDN dominates over KNU.
\end{axiom}

\begin{equation}
A_{INU} > A_{IDN} > A_{KNU} \quad \text{(in conflict)}
\end{equation}

\subsubsection{Awareness Thresholds}

\begin{axiom}[AWX-A44: Awareness Thresholds]
\label{ax:awx-a44}
Awareness thresholds differ by utility type: INU has low threshold, 
KNU has high threshold.
\end{axiom}

\begin{equation}
\theta_{A,INU} < \theta_{A,IDN} < \theta_{A,KNU}
\end{equation}

This means:
\begin{itemize}
\item INU awareness is easily activated
\item IDN awareness requires specific triggers
\item KNU awareness requires substantial effort or cues
\end{itemize}

\subsubsection{Cross-Category Interactions}

\begin{axiom}[AWX-A38 to AWX-A40: Category Interactions]
\label{ax:awx-interactions}
Awareness in one category can increase awareness in another.
\end{axiom}

\begin{align}
A_{KNU}(t^*) &= f(A_{INU}(t^*)) \quad \text{(AWX-A38)} \\
A_{INU}(t^*) &= f(A_{IDN}(t^*)) \quad \text{(AWX-A39)} \\
A_{KNU}(t^*) &= f(A_{IDN}(t^*)) \quad \text{(AWX-A40)}
\end{align}

\paragraph{Example:}
When professional identity is salient ($A_{IDN}$ high), awareness for 
team welfare ($A_{KNU}$) also increases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 4: Complexity and Uncertainty}
\label{subsec:axioms-complexity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Complexity Effects}

\begin{axiom}[AWX-A46: Complexity Reduction]
\label{ax:awx-a46}
Awareness decreases with increasing complexity of the decision situation.
\end{axiom}

\begin{equation}
A_X(t^*) = f(-Complexity)
\end{equation}

\begin{axiom}[AWX-A47: Framing Necessity]
\label{ax:awx-a47}
At high complexity, awareness becomes possible only through simplification, 
framing, or heuristics.
\end{axiom}

\begin{equation}
\text{If } Complexity > \theta \Rightarrow A_X(t^*) = f(Framing)
\end{equation}

\subsubsection{The Failure Awareness Gap}

\begin{axiom}[AWX-A47a: Failure Awareness Gap]
\label{ax:awx-a47a}
Awareness is systematically distorted when failures remain invisible 
communicatively, institutionally, or culturally.
\end{axiom}

\begin{equation}
\Delta A_F = f(VisibilityCost, PowerDistance, -Transparency, -PsychSafety, FeedbackLag, NormShame)
\end{equation}

\begin{equation}
A_{eff}(t^*) = A_{base}(t^*) \times (1 - \Delta A_F)
\end{equation}

\paragraph{Critical Threshold:}
\begin{equation}
\Delta A_F > 0.25 \Rightarrow \text{Perceptual Lock-In (Watchdog Alert)}
\end{equation}

\paragraph{Determinants of the Failure Gap:}
\begin{itemize}
\item $VisibilityCost$: Cost of making failures visible
\item $PowerDistance$: Hierarchical barriers to reporting
\item $Transparency$: Degree of information sharing
\item $PsychSafety$: Safety to report without punishment
\item $FeedbackLag$: Delay between failure and feedback
\item $NormShame$: Cultural stigmatization of failure
\end{itemize}

\subsubsection{Uncertainty Effects}

\begin{table}[htbp]
\centering
\caption{Uncertainty Types and Awareness}
\label{tab:uncertainty-effects}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Axiom} & \textbf{Uncertainty Type} & \textbf{Effect} \\
\midrule
AWX-A48 & Environmental & $A = f(-Uncertainty_{env})$ \\
AWX-A49 & Interpersonal & $A = f(-Uncertainty_{interp})$ \\
AWX-A50 & Institutional & $A = f(-Uncertainty_{inst})$ \\
AWX-A51 & Epistemic & If epistemic uncertainty $\Rightarrow A = 0$ \\
AWX-A52 & Accumulation & Multiple uncertainties compound \\
AWX-A53 & Differentiation & Epistemic $>$ Institutional $>$ Interpersonal $>$ Environmental \\
\bottomrule
\end{tabular}
\end{table}

\begin{axiom}[AWX-A54: Complexity-Uncertainty Interaction]
\label{ax:awx-a54}
Complexity amplifies the effect of uncertainty and reduces awareness disproportionately.
\end{axiom}

\begin{equation}
A_X(t^*) = f(-Complexity \times Uncertainty_{total})
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 5: Time and Dynamics}
\label{subsec:axioms-time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Temporal Properties}

\begin{table}[htbp]
\centering
\caption{Temporal Dynamics of Awareness}
\label{tab:temporal-dynamics}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Axiom} & \textbf{Property} & \textbf{Formal} \\
\midrule
AWX-A56 & Situativity & $A_X(t^*) \neq A_X(t^{**})$ \\
AWX-A57 & Fluctuation & $Var(A_X(t)) > 0$ \\
AWX-A58 & Decay & $A_X(t + \Delta t) = A_X(t) \cdot e^{-\lambda \Delta t}$ \\
AWX-A59 & Reactivation & $A_X(t^*) = f(Trigger_{count}, Trigger_{intensity})$ \\
AWX-A60 & Habitual weakening & $A_X(t^*) \rightarrow 0$ with repetition \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Life Course Effects}

\begin{axiom}[AWX-A61: Life Phase Dependence]
\label{ax:awx-a61}
Awareness levels vary systematically across life phases.
\end{axiom}

\begin{equation}
A_X(t^*) = f(LifePhase)
\end{equation}

\begin{axiom}[AWX-A62: Life Events]
\label{ax:awx-a62}
Certain life events (birth, death, illness, job loss) change awareness abruptly.
\end{axiom}

\begin{equation}
\Delta A_X(t^*) >> 0 \text{ at LifeEvent}
\end{equation}

\begin{axiom}[AWX-A63: Shock Triggers]
\label{ax:awx-a63}
Sudden shock events increase awareness massively and immediately.
\end{axiom}

\begin{equation}
A_X(t^*) = A_X(t^*-1) + Shock_{intensity}
\end{equation}

\subsubsection{Feedback Learning}

\begin{equation}
A_{SYS2}(t+1) = A_{SYS2}(t) + \rho_{feedback} \times \Delta Outcome_{impact}
\end{equation}

Awareness learns from behavioral consequences and corrects its impact estimates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 6: Conflict and Dissonance}
\label{subsec:axioms-conflict}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Defensive Mechanisms}

\begin{axiom}[AWX-A66: Suppression]
\label{ax:awx-a66}
Awareness can be consciously or unconsciously suppressed when it is 
unpleasant or threatening.
\end{axiom}

\begin{equation}
\text{If } Awareness \rightarrow \text{strong negative emotion} \Rightarrow A_X(t^*) \downarrow
\end{equation}

\begin{axiom}[AWX-A67: Cognitive-Emotional Split]
\label{ax:awx-a67}
Individuals can be cognitively informed about an impact without 
developing emotional awareness.
\end{axiom}

\begin{equation}
A_{cognitive} \neq A_{emotional}
\end{equation}

\subsubsection{Distortions}

\begin{axiom}[AWX-A68: Norm Conflict Blockade]
\label{ax:awx-a68}
Awareness can be blocked when different social norms send contradictory signals.
\end{axiom}

\begin{equation}
\text{If } Norm_1 \neq Norm_2 \Rightarrow A_X(t^*) \downarrow
\end{equation}

\begin{axiom}[AWX-A69: False Awareness]
\label{ax:awx-a69}
Misinformation, propaganda, or distorted frames can create awareness 
that is factually false.
\end{axiom}

\begin{equation}
A_X(t^*) \neq Reality_{Impact}
\end{equation}

\subsubsection{Mirror Coherence}

\begin{axiom}[AWX-A70a: Mirror Coherence and Awareness Dissonance]
\label{ax:awx-a70a}
Awareness responds to the difference between self-image ($I_t$) and 
social feedback ($S_t$), measured as Mirror-Gap $\Delta I_t$.
\end{axiom}

\begin{equation}
A_X(t^*) = f(MirrorGap_t)
\end{equation}

\begin{equation}
\frac{\partial A_X}{\partial \Delta I_t} > 0 \text{ for } \Delta I_t < 0.6 \quad \text{(learning)}
\end{equation}

\begin{equation}
\frac{\partial A_X}{\partial \Delta I_t} < 0 \text{ for } \Delta I_t \geq 0.6 \quad \text{(defensive)}
\end{equation}

\paragraph{Thresholds:}
\begin{itemize}
\item $\Delta I < 0.3$: Learning awareness (constructive)
\item $0.3 \leq \Delta I < 0.6$: Transitional
\item $\Delta I \geq 0.6$: Defensive awareness (protective)
\item $\Delta I \geq 0.8$: Overload (Watchdog Alert)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 7: Segments and Player Types}
\label{subsec:axioms-segments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{axiom}[AWX-A71: Segment Dependence]
\label{ax:awx-a71}
Awareness levels vary systematically between segments defined in Module 7257.
\end{axiom}

\begin{equation}
A_X^{Segment_i} \neq A_X^{Segment_j}
\end{equation}

\begin{axiom}[AWX-A72: Player Types]
\label{ax:awx-a72}
Awareness levels differ by player type (cooperative, competitive, strategic).
\end{axiom}

\begin{equation}
A_X(t^*) = f(PlayerType)
\end{equation}

\begin{axiom}[AWX-A73: Cultural Differentiation]
\label{ax:awx-a73}
Awareness levels vary strongly between cultures due to different narratives, 
symbols, and institutions.
\end{axiom}

\begin{equation}
A_X(t^*) = f(Culture)
\end{equation}

\begin{axiom}[AWX-A74: Education Level]
\label{ax:awx-a74}
Awareness levels increase with education and competence levels.
\end{axiom}

\begin{equation}
A_X(t^*) \propto Education_{level}
\end{equation}

\begin{axiom}[AWX-A75: Socioeconomic Status]
\label{ax:awx-a75}
Awareness levels depend on socioeconomic status: resource abundance 
enables higher awareness.
\end{axiom}

\begin{equation}
A_X(t^*) \propto SES
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Axiom Cluster 8: Interaction and Aggregation}
\label{subsec:axioms-aggregation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Group Awareness}

\begin{axiom}[AWX-A76: Individual Aggregation]
\label{ax:awx-a76}
Collective awareness results from aggregating individual awareness values.
\end{axiom}

\begin{equation}
A_{Group}(t^*) = \frac{\sum_i A_i(t^*)}{n}
\end{equation}

\begin{axiom}[AWX-A77: Dynamic Multiplicity]
\label{ax:awx-a77}
Aggregated awareness is non-linear, determined by dynamic weights.
\end{axiom}

\begin{equation}
A_{Group}(t^*) = \sum_i w_i \cdot A_i(t^*), \quad w_i \neq \text{constant}
\end{equation}

\subsubsection{Social Dynamics}

\begin{axiom}[AWX-A78: Awareness Cascades]
\label{ax:awx-a78}
An awareness expression or action can trigger a cascade that increases 
awareness in others.
\end{axiom}

\begin{equation}
\Delta A_j(t^*) = f(A_i(t^*), Influence_{strength})
\end{equation}

\begin{axiom}[AWX-A79: Awareness Spillover]
\label{ax:awx-a79}
Awareness in one domain can strengthen or activate awareness in other domains.
\end{axiom}

\begin{equation}
A_X(t^*) \leftrightarrow A_Y(t^*)
\end{equation}

\begin{axiom}[AWX-A80: Awareness Blockades]
\label{ax:awx-a80}
Toxic communication (hate speech, targeted disinformation) can block 
awareness at the collective level.
\end{axiom}

\begin{equation}
A_{Group}(t^*) = 0 \text{ when } HateSpeech_{intensity} >> \theta
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integration with EBF Architecture}
\label{subsec:awareness-integration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Module Position}

\begin{equation}
\Psi \rightarrow U_{pot} \rightarrow \mathbf{A} \rightarrow U_{eff} \rightarrow WTC \rightarrow Behavior
\end{equation}

\begin{table}[htbp]
\centering
\caption{Awareness Module Integration}
\label{tab:module-integration}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Direction} & \textbf{Modules} & \textbf{Relationship} \\
\midrule
Upstream & 7234\_INU, 7235\_KNU, 7236\_IDN & Provides $U_{pot}$ \\
Upstream & 8904\_KON & Provides context $C$ \\
Upstream & 9493-9495\_UNS & Provides uncertainty \\
Downstream & 7243\_WAX & Receives $U_{eff}$ for willingness \\
Downstream & 7259\_PRB & Receives for probability \\
Governance & 9251\_WATCHDOG & Monitors thresholds \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{The Bias Block}

Awareness is coupled with the Bias Block:

\begin{equation}
Bias_{total} = Bias_{conf} + Bias_{surv} + Bias_{fail} + \kappa(Bias_{conf} \times Bias_{surv} \times Bias_{fail})
\end{equation}

\begin{itemize}
\item $Bias_{conf}$: Overconfidence bias
\item $Bias_{surv}$: Survivorship bias
\item $Bias_{fail}$: Failure awareness gap
\item $\kappa$: Interaction coefficient
\end{itemize}

\paragraph{Watchdog Triggers:}
\begin{itemize}
\item $\Delta A_F > 0.25$: Failure Gap Alert
\item $\kappa > 0.10$: Bias Coupling Anomaly
\item $Bias_{total} > \theta_{Bias}$: Meta Threshold Breach
\end{itemize}

\subsubsection{Meta-Constraints}

\begin{itemize}
\item \textbf{C1:} Awareness is only valid when relevant context ($C_{rel}$) is present
\item \textbf{C2:} Awareness cannot be simultaneously maximal in SYS 0 and SYS 2
\item \textbf{C3:} KNU is always awareness-mandatory; instant KNU is not possible
\item \textbf{C4:} Awareness drops when complexity or uncertainty exceeds threshold
\end{itemize}

\paragraph{Governance Validation:}
\begin{equation}
\sum |\Delta A_{SYS_i}| \leq \theta_{meta} \wedge C1-C4 \text{ fulfilled} \Rightarrow \text{Awareness} = \text{VALID}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundaries: What Awareness Is NOT}
\label{subsec:awareness-boundaries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[htbp]
\centering
\caption{Awareness Boundaries}
\label{tab:awareness-boundaries}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Awareness $\neq$} & \textbf{Reason} \\
\midrule
Knowledge & Information can exist without being active \\
Attitude & Preferential but not real-time behaviorally relevant \\
Motivation & Motivation can exist without impact awareness \\
Information & Communication $\neq$ consciousness of consequences \\
Automatic processes & Exception: Instant INU/IDN \\
Norm enforcement & Conformity can occur without awareness \\
Strategic rationality & Planning $\neq$ impact consciousness \\
Stable trait & Dynamic and context-dependent \\
Utility itself & Mediates utility, doesn't create it \\
Complete behavior control & Necessary but not sufficient condition \\
Visibility & Public communication $\neq$ individual awareness \\
Transparency & Can exist without being perceived \\
Feedback & Creates awareness only when internalized \\
Discourse & Social debates don't create awareness per se \\
Data awareness & Algorithmic display doesn't replace impact consciousness \\
False awareness & Misinterpretations create pseudo-consciousness \\
\bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application Examples}
\label{subsec:awareness-applications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Example 1: Climate Action}

\begin{table}[htbp]
\centering
\caption{Climate Action: Awareness Analysis}
\label{tab:climate-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Component} & \textbf{System} & \textbf{Default $A$} & \textbf{Challenge} \\
\midrule
$A^{self}_{INU}$ (costs) & SYS 2 & HIGH & Immediate, visible \\
$A^{self}_{KNU}$ (family future) & SYS 1-2 & MEDIUM & Abstract \\
$A^{comm}_{INU}$ (others' welfare) & SYS 2 & LOW & Distant others \\
$A^{comm}_{KNU}$ (global community) & SYS 2 & VERY LOW & Abstract collective \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Why Climate Action Is Hard:}
\begin{itemize}
\item Costs = $A^{self}_{INU}$ (high awareness, SYS 0-1)
\item Benefits = $A^{comm}_{KNU}$ (very low awareness, SYS 2 only)
\item KNU is never instant → always requires deliberate awareness
\item Failure Gap: Climate failures are not immediately visible
\end{itemize}

\subsubsection{Example 2: Smoking Cessation}

\begin{table}[htbp]
\centering
\caption{Smoking: System Level Competition}
\label{tab:smoking-systems}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Effect} & \textbf{System} & \textbf{$A$ Level} & \textbf{Valence} \\
\midrule
Craving & SYS 0 & $= 1$ (instant) & Immediate pain if unsatisfied \\
Stress relief & SYS 1 & HIGH & Immediate gain \\
Social fit & SYS 1 & MEDIUM & Context-dependent \\
Health damage & SYS 2 & LOW & Requires reflection \\
Family impact & SYS 2 & LOW & Requires empathy \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Why Cessation Fails:}
SYS 0 (craving, $A = 1$) dominates SYS 2 (health awareness, $A$ low).
The Hyper-Dissonance Rule: when SYS 0 is maximal, SYS 2 is suppressed.

\subsubsection{Example 3: CEO Layoff Decision}

\begin{table}[htbp]
\centering
\caption{CEO Layoff: Two-Level Awareness Analysis}
\label{tab:ceo-awareness}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lccl@{}}
\toprule
\textbf{Component} & \textbf{Default $A$} & \textbf{Should Be} & \textbf{Content} \\
\midrule
$A^{self}_{INU}$ & HIGH & -- & My bonus, reputation \\
$A^{self}_{KNU}$ & MEDIUM & -- & Company survival \\
$A^{self}_{IDN}$ & LOW & HIGHER & Am I a good leader? \\
$A^{comm}_{INU}$ & LOW & \textbf{HIGH} & Employees' income, stress \\
$A^{comm}_{KNU}$ & VERY LOW & \textbf{HIGH} & Employees' families \\
$A^{comm}_{IDN}$ & VERY LOW & \textbf{HIGH} & Employees' professional identity \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Ethical Leadership Requires:}
Deliberate activation of $A^{comm}$ across all three categories.
Without this, decisions optimize for $A^{self}$ only.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Intervention Implications}
\label{subsec:awareness-interventions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Nudges as Awareness Manipulation}

\begin{equation}
Nudge \Rightarrow \Delta A \Rightarrow \Delta U_{eff} \Rightarrow \Delta Behavior
\end{equation}

\begin{table}[htbp]
\centering
\caption{Nudges Mapped to Awareness Components}
\label{tab:nudges-mapping}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Nudge} & \textbf{Target} & \textbf{System} & \textbf{Mechanism} \\
\midrule
``For your health'' & $A^{self}_{INU,P}$ & SYS 2 & Physical awareness \\
``For your family'' & $A^{self}_{KNU}$ & SYS 1-2 & Collective awareness \\
``Be who you want to be'' & $A^{self}_{IDN}$ & SYS 1-2 & Identity awareness \\
Identifiable victim & $A^{comm}_{INU}$ & SYS 1 & Empathy activation \\
Social proof & $A^{self}_{KNU}$ & SYS 1 & Norm awareness \\
Default options & Reduces need for $A$ & SYS 2 bypass & Automaticity \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{The Six-Component Checklist}

For comprehensive behavioral intervention:

\begin{enumerate}
\item Does it activate $A^{self}_{INU}$? (Personal effects)
\item Does it activate $A^{self}_{KNU}$? (Group effects on self)
\item Does it activate $A^{self}_{IDN}$? (Identity relevance)
\item Does it activate $A^{comm}_{INU}$? (Others' personal welfare)
\item Does it activate $A^{comm}_{KNU}$? (Others' groups)
\item Does it activate $A^{comm}_{IDN}$? (Others' identity)
\end{enumerate}

\paragraph{Most interventions are incomplete:}
Typical nudges target 1-2 of 6 components.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Summary: The Awareness Function}
\label{subsec:awareness-summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black, title=Chapter 11 Summary: Awareness]

\textbf{Content Definition:}
Awareness is the consciousness of the positive and negative effects on one's 
own utility level (INU, KNU, IDN) and on the utility level (INU, KNU, IDN) 
of a relevant community, at the moment of decision.

\textbf{Functional Definition:}
Awareness is the necessary condition for transforming potential utility 
into effective utility at the Moment of Truth.

\textbf{The Core Formula:}
$$U_{eff,X}(t^*) = U_{pot,X}(t^*) \times A_X(t^*)$$

\textbf{Three System Levels:}
\begin{itemize}
\item SYS 0: Instant/Visceral (automatic, no reflection)
\item SYS 1: Affective/Emotional (social resonance)
\item SYS 2: Reflective/Cognitive (deliberate, effortful)
\end{itemize}

\textbf{Two-Level Structure:}
$$\mathbf{A} = \begin{pmatrix} A^{self}_{INU} & A^{self}_{KNU} & A^{self}_{IDN} \\ A^{comm}_{INU} & A^{comm}_{KNU} & A^{comm}_{IDN} \end{pmatrix}$$

\textbf{The Instant Exception:}
\begin{itemize}
\item INU\_instant: Automatic ($A = 1$)
\item IDN\_instant: Automatic ($A = 1$)
\item KNU: ALWAYS awareness-mandatory (no instant)
\end{itemize}

\textbf{The Awareness Gradient:}
$$A^{self}_{INU} > A^{self}_{KNU} > A^{self}_{IDN} > A^{comm}_{INU} > A^{comm}_{KNU} > A^{comm}_{IDN}$$

\textbf{Eight Axiom Clusters:}
\begin{enumerate}
\item Fundamental axioms (AWX-A1 to A10)
\item Determinants (AWX-A11 to A30)
\item Utility-specific (AWX-A31 to A45)
\item Complexity \& Uncertainty (AWX-A46 to A55)
\item Time \& Dynamics (AWX-A56 to A65)
\item Conflict \& Dissonance (AWX-A66 to A70)
\item Segments \& Player Types (AWX-A71 to A75)
\item Interaction \& Aggregation (AWX-A76 to A80)
\end{enumerate}

\textbf{Failure Awareness Gap:}
$$\Delta A_F = f(VisibilityCost, PowerDistance, -Transparency, -PsychSafety, FeedbackLag)$$

\textbf{Integration:}
$$\Psi \rightarrow U_{pot} \rightarrow \mathbf{A} \rightarrow U_{eff} \rightarrow WTC \rightarrow Behavior$$

\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF CHAPTER 11
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
