% =============================================================================
% APPENDIX FEH: LIT-FEHR: Ernst Fehr Research Integration
% =============================================================================
% Module: BCM2_LIT_FEHR
% Version: 1.0 (January 2026)
% Status: Final
% Language: English
%
% Comprehensive documentation of Ernst Fehr's scientific contributions,
% their integration into the Evidence-Based Framework (EBF), extractable
% parameters, cases, and practical implications for practitioners.
%
% SSOT Reference: data/researcher-registry.yaml (RES-FEHR-E)
% =============================================================================

% =============================================================================
% CROSS-REFERENCE STRUCTURE
% =============================================================================
%
% CHAPTER LINKAGE:
% - Primary Chapter: Chapter 10 (CORE-WHAT: Social Preferences)
% - Secondary Chapters: Chapter 5 (CORE-WHO), Chapter 11 (CORE-HOW), Chapter 9 (CORE-WHEN)
%
% DEPENDENCIES:
% - Appendix UNMAPPED_C (CORE-WHAT): Utility dimensions U^S
% - Appendix UNMAPPED_BBB (CORE-WHERE): Parameter repository
% - Appendix UNMAPPED_B (CORE-HOW): Complementarity γ
%
% DEPENDENTS:
% - Appendix UNMAPPED_FRM (LIT-FEHR-METHOD): Methodological integration
% - All DOMAIN appendices using social preference parameters
%
% =============================================================================

\begin{tcolorbox}[colback=purple!5!white, colframe=purple!75!black,
    title=Chapter Linkage]

\textbf{Primary Chapter:} Chapter 10: Social Preferences and Other-Regarding Behavior
\begin{itemize}[nosep]
\item Section 10.2: Inequity Aversion $\leftrightarrow$ This Appendix Section \ref{sec:feh-inequity}
\item Section 10.3: Strong Reciprocity $\leftrightarrow$ This Appendix Section \ref{sec:feh-reciprocity}
\item Section 10.4: Gift Exchange $\leftrightarrow$ This Appendix Section \ref{sec:feh-gift}
\end{itemize}

\textbf{Secondary Chapters:}
\begin{itemize}[nosep]
\item Chapter 5: CORE-WHO --- preference type heterogeneity
\item Chapter 9: CORE-WHEN --- context effects on social preferences
\item Chapter 11: CORE-HOW --- complementarity in cooperation mechanisms
\end{itemize}

\textbf{Reading Guide:}
\begin{itemize}[nosep]
\item For conceptual overview: Read Chapter 10 first
\item For formal parameter values: This appendix provides calibration
\item For methodology: See Appendix UNMAPPED_FRM (LIT-FEHR-METHOD)
\end{itemize}

\end{tcolorbox}


\chapter{LIT-FEHR: Ernst Fehr Research Integration}
\label{app:feh}


\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black,
    title=Quick Reference: Appendix UNMAPPED_FEH]

\textbf{Appendix:} FEH (LIT-FEHR)

\textbf{Registry ID:} RES-FEHR-E

\textbf{Core Question:} How do Ernst Fehr's contributions enable behavioral economics
in EBF, and which parameters can be estimated from his research?

\textbf{Key Concepts:}
\begin{itemize}[nosep]
\item Inequity Aversion ($\alpha$, $\beta$)
\item Strong Reciprocity
\item Gift Exchange
\item Preference Heterogeneity
\end{itemize}

\textbf{Key Parameters:}
\begin{align}
\alpha &= 0.85 \quad [0.5, 4.0] \quad \text{(disadvantageous inequity aversion)} \\
\beta &= 0.315 \quad [0.0, 0.6] \quad \text{(advantageous inequity aversion)} \\
\gamma_{\text{trust,contract}} &> 0 \quad \text{(complementarity in cooperation)}
\end{align}

\textbf{Cross-References:} C (CORE-WHAT), BBB (CORE-WHERE), FRM (METHOD), B (CORE-HOW)
\end{tcolorbox}


\begin{abstract}
This appendix documents the comprehensive research contributions of Ernst Fehr
(h-index: 157, 180,000+ citations) to behavioral economics and their integration
into the Evidence-Based Framework (EBF). Fehr's work provides the empirical
foundation for EBF's treatment of social preferences, establishing that utility
includes other-regarding components ($U^S$) with measurable parameters. The appendix
catalogs 144 integrated papers, documents non-integrated papers with evaluation,
and provides practitioners with actionable parameter estimates and case examples.
\end{abstract}


\begin{tcolorbox}[
    colback=orange!5!white,
    colframe=orange!75!black,
    title={\textbf{Appendix Scope: Ziel / In-Scope / Out-of-Scope / Constraints}},
    fonttitle=\bfseries
]

\textbf{Ziel (Objective):}
\begin{itemize}[nosep]
    \item Document Ernst Fehr's scientific contributions and their integration into EBF
\end{itemize}

\textbf{In-Scope:}
\begin{itemize}[nosep]
    \item Scientific contributions to economics (5 key areas)
    \item EBF framework contributions (5 CORE dimensions)
    \item Extractable parameters with confidence intervals
    \item Cases and worked examples from Fehr's papers
    \item Practical implications for behavior change practitioners
    \item Paper bibliography (integrated and non-integrated with evaluation)
\end{itemize}

\textbf{Out-of-Scope (delegiert an andere Appendices):}
\begin{itemize}[nosep]
    \item Formal derivations of Fehr-Schmidt model $\rightarrow$ Appendix D (FORMAL)
    \item Methodological critique (integration vs. falsifiability) $\rightarrow$ Appendix UNMAPPED_FRM
    \item Parameter repository details $\rightarrow$ Appendix UNMAPPED_BBB (CORE-WHERE)
    \item Context framework details $\rightarrow$ Appendix UNMAPPED_V (CORE-WHEN)
\end{itemize}

\textbf{Constraints (Anwendungsgrenzen):}
\begin{itemize}[nosep]
    \item Parameters are population averages; individual variation is substantial
    \item Laboratory estimates may differ from field contexts (external validity)
    \item Neuroeconomics papers excluded from EBF scope
\end{itemize}

\textbf{Lieferobjekte (Deliverables):}
\begin{itemize}[nosep]
    \item Table of extractable parameters with sources
    \item Type distribution for population heterogeneity
    \item Worked examples for practitioner application
    \item Complete paper bibliography with integration decisions
\end{itemize}

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Fundamental Question}
\label{sec:feh-fundamental}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Why This Matters}

Ernst Fehr is among the most influential economists of the past three decades,
with an h-index of 157 and over 180,000 citations. His research has fundamentally
challenged the homo economicus assumption that dominated economics, demonstrating
empirically that:

\begin{enumerate}
    \item People care about fairness, not just their own payoffs
    \item Cooperation can emerge and persist even among strangers
    \item Context (institutions, norms, culture) shapes behavior systematically
    \item Population heterogeneity in preferences explains seemingly contradictory findings
\end{enumerate}

For the Evidence-Based Framework, Fehr's contributions are foundational. Without
his empirical parameters ($\alpha$, $\beta$), EBF cannot calibrate social preference
models. Without his experimental methods, EBF cannot validate predictions.

\subsection{The Core Problem}

How do we systematically integrate 343 publications spanning 35+ years into a
coherent framework for behavioral interventions?

\begin{tcolorbox}[colback=red!5!white, colframe=red!75!black,
    title=The Fundamental Question]
\textbf{Which of Fehr's contributions provide extractable parameters, testable
theories, or replicable cases for EBF---and which remain outside scope?}
\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Principles (Axioms)}
\label{sec:feh-axioms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Fehr's research program is built on foundational methodological principles that
guide EBF integration:

\begin{itemize}
    \item \textbf{AX-F1 (Experimental Validity):} Behavioral claims require controlled
    experimental evidence, not just observational data or introspection.

    \item \textbf{AX-F2 (Incentive Compatibility):} Experimental subjects must face
    real monetary consequences; hypothetical choices systematically differ from
    consequential ones.

    \item \textbf{AX-F3 (Heterogeneity):} Population distributions of preferences
    (e.g., $\alpha$, $\beta$) must be estimated, not assumed homogeneous.

    \item \textbf{AX-F4 (Context Sensitivity):} Social preferences vary with
    institutional context ($\Psi$); lab findings require field validation.

    \item \textbf{AX-F5 (Parsimony):} Models should use minimal parameters to explain
    observed behavior; the Fehr-Schmidt model uses only $\alpha$ and $\beta$.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Key Results}
\label{sec:feh-results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following empirically validated results form the foundation for EBF parameter
estimation:

\begin{enumerate}
    \item \textbf{R1:} Approximately 40\% of subjects exhibit inequity aversion
    ($\alpha > 0$ or $\beta > 0$) in standard dictator and ultimatum games.

    \item \textbf{R2:} The median value of $\alpha = 0.85$ (disadvantageous inequity
    aversion) is robust across 15+ countries and 50+ replications.

    \item \textbf{R3:} Strong reciprocity (costly punishment of defectors) persists
    even in one-shot anonymous interactions, contradicting pure self-interest.

    \item \textbf{R4:} Gift exchange effects on effort provision range from 10-40\%
    above equilibrium predictions in lab and field settings.

    \item \textbf{R5:} Context ($\Psi$) modulates social preferences: competitive
    framing reduces cooperation by 20-30\% compared to cooperative framing.
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scientific Contributions to Economics}
\label{sec:feh-economics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Ernst Fehr's contributions to economics span five major areas, each with
lasting impact on theory and practice.

%------------------------------------------------------------------------------
\subsection{Inequity Aversion Model (Fehr-Schmidt 1999)}
\label{sec:feh-inequity}
%------------------------------------------------------------------------------

The Fehr-Schmidt model \citep{fehr1999theory} fundamentally redefined utility
by incorporating distributional concerns:

\begin{equation}
U_i(x) = x_i - \alpha_i \cdot \frac{1}{n-1} \sum_{j \neq i} \max\{x_j - x_i, 0\}
       - \beta_i \cdot \frac{1}{n-1} \sum_{j \neq i} \max\{x_i - x_j, 0\}
\label{eq:fehr-schmidt}
\end{equation}

Where:
\begin{itemize}[nosep]
    \item $x_i$ = material payoff to agent $i$
    \item $\alpha_i$ = sensitivity to \textit{disadvantageous} inequity (being behind)
    \item $\beta_i$ = sensitivity to \textit{advantageous} inequity (being ahead)
\end{itemize}

\textbf{Key constraint:} $\alpha_i \geq \beta_i$ and $0 \leq \beta_i < 1$

\paragraph{Impact.} With 19,000+ citations, this is the most cited behavioral
economics model. It explains:
\begin{itemize}[nosep]
    \item Ultimatum game rejections (even with real stakes)
    \item Public goods provision with punishment
    \item Wage compression in labor markets
    \item Resistance to ``unfair'' price increases
\end{itemize}

%------------------------------------------------------------------------------
\subsection{Strong Reciprocity}
\label{sec:feh-reciprocity}
%------------------------------------------------------------------------------

Fehr's work on strong reciprocity \citep{fehr2002strong, gaechter2002altruistic}
demonstrates that humans cooperate and punish defectors even when:
\begin{itemize}[nosep]
    \item The interaction is one-shot (no reputation effects)
    \item Partners are anonymous (no social pressure)
    \item Punishment is costly to the punisher
\end{itemize}

\textbf{Definition:} Strong reciprocity = propensity to cooperate with cooperators
and punish defectors, even at personal cost, in anonymous one-shot interactions.

\paragraph{Key finding.} In public goods games with punishment, cooperation
stabilizes at 80-95\%, compared to 20-40\% without punishment. The presence
of strong reciprocators transforms group dynamics.

%------------------------------------------------------------------------------
\subsection{Gift Exchange and Efficiency Wages}
\label{sec:feh-gift}
%------------------------------------------------------------------------------

The gift exchange literature \citep{fehr1993reciprocity, fehr1998reciprocity}
provides experimental validation for efficiency wage theory:

\begin{itemize}[nosep]
    \item Workers respond to higher wages with higher effort (reciprocity)
    \item This effect persists even without monitoring or reputation
    \item Firms can sustain above-market wages profitably
\end{itemize}

\textbf{EBF implication:} Monetary incentives interact with social preferences.
A wage increase can be a ``gift'' eliciting reciprocal effort, not just a
price for labor.

%------------------------------------------------------------------------------
\subsection{Experimental Methods}
\label{sec:feh-methods}
%------------------------------------------------------------------------------

Fehr pioneered and standardized key experimental paradigms:

\begin{table}[htbp]
\centering
\caption{Experimental Games Standardized by Fehr's Research}
\label{tab:feh-games}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Game} & \textbf{Measures} & \textbf{Key Finding} \\
\midrule
Ultimatum Game & Fairness rejection threshold & Modal offer 40-50\% \\
Dictator Game & Pure altruism/fairness & Mean transfer 20-30\% \\
Trust Game & Trust and trustworthiness & 50\% trusted, 30\% returned \\
Public Goods + Punishment & Cooperation sustainability & 80-95\% with punishment \\
Gift Exchange Game & Wage-effort reciprocity & Positive correlation \\
\bottomrule
\end{tabular}
\end{table}

%------------------------------------------------------------------------------
\subsection{Behavioral Contract Theory}
\label{sec:feh-contracts}
%------------------------------------------------------------------------------

More recent work \citep{fehr2007competition} integrates behavioral assumptions
into mechanism design, showing that optimal contracts must account for:
\begin{itemize}[nosep]
    \item Heterogeneity in social preferences
    \item Reference-dependent utility
    \item Loss aversion in effort provision
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Contributions to the EBF Framework}
\label{sec:feh-ebf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Fehr's research maps onto multiple CORE dimensions of EBF:

%------------------------------------------------------------------------------
\subsection{CORE-WHAT: Social Utility Component}
%------------------------------------------------------------------------------

Fehr establishes that utility is not unidimensional:

\begin{equation}
U = U^F + U^S + U^P + U^E + U^{ID}
\end{equation}

His work provides the foundation for $U^S$ (social utility), demonstrating:
\begin{itemize}[nosep]
    \item People have preferences over distributions, not just own payoffs
    \item Fairness concerns are measurable via $\alpha$ and $\beta$
    \item Social comparison is a fundamental driver of satisfaction
\end{itemize}

\textbf{EBF Integration:} Appendix UNMAPPED_C (CORE-WHAT) incorporates Fehr-Schmidt
parameters as default social preference calibration.

%------------------------------------------------------------------------------
\subsection{CORE-HOW: Complementarity in Cooperation}
%------------------------------------------------------------------------------

Fehr's work reveals positive complementarity ($\gamma > 0$) between cooperation
mechanisms:

\begin{equation}
\gamma(\text{trust}, \text{contract}) > 0
\end{equation}

Trust and formal contracts are \textit{complements}, not substitutes. The
recent Nature paper on ``Super-additive Cooperation'' \citep{efferson2024superadditive}
demonstrates:

\begin{equation}
\gamma(\text{repetition}, \text{competition}) > 0 \quad \text{(super-additive)}
\end{equation}

\textbf{EBF Integration:} Appendix UNMAPPED_B (CORE-HOW) uses these findings to justify
bundled interventions.

%------------------------------------------------------------------------------
\subsection{CORE-WHEN: Context Effects}
%------------------------------------------------------------------------------

Fehr's banking culture research \citep{cohn2014business, cohn2015evidence}
demonstrates systematic context effects:

\begin{itemize}[nosep]
    \item $\Psi_{\text{norm}}$: Social norms shift behavior significantly
    \item $\Psi_{\text{culture}}$: Professional identity affects honesty
    \item $\Psi_{\text{inst}}$: Institutional rules shape cooperation
\end{itemize}

\textbf{Key finding:} The \textit{same} individuals behave differently when
their professional (vs. personal) identity is salient.

%------------------------------------------------------------------------------
\subsection{CORE-WHO: Preference Heterogeneity}
%------------------------------------------------------------------------------

Fehr's work reveals that the population is not a representative agent but
a \textit{mixture of types}:

\begin{table}[htbp]
\centering
\caption{Type Distribution from Fehr's Research}
\label{tab:feh-types}
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Type} & \textbf{Proportion} & \textbf{$\alpha$} & \textbf{$\beta$} \\
\midrule
Selfish & 30\% & 0 & 0 \\
Moderate & 30\% & 0.5 & 0.25 \\
Fair & 30\% & 1.0 & 0.5 \\
Strongly Fair & 10\% & $>1$ & $>0.5$ \\
\bottomrule
\end{tabular}
\end{table}

\textbf{EBF Implication:} Interventions must account for heterogeneity.
A policy optimal for ``fair'' types may backfire for ``selfish'' types.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extractable Parameters}
\label{sec:feh-parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following parameters can be reliably estimated from Fehr's research:

\begin{table}[htbp]
\centering
\caption{EBF Parameters from Fehr's Research}
\label{tab:feh-params}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{@{}lccll@{}}
\toprule
\textbf{Parameter} & \textbf{Point Est.} & \textbf{Range} & \textbf{Source} & \textbf{Appendix} \\
\midrule
$\alpha$ (disadvantageous) & 0.85 & [0.5, 4.0] & \citet{fehr1999theory} & BBB \\
$\beta$ (advantageous) & 0.315 & [0.0, 0.6] & \citet{fehr1999theory} & BBB \\
Punishment cost ratio & 3:1 & [2:1, 4:1] & \citet{fehr2002strong} & BBB \\
Trust rate (baseline) & 0.50 & [0.40, 0.60] & Trust Game meta & BBB \\
Reciprocity rate & 0.30 & [0.20, 0.40] & Trust Game meta & BBB \\
Gift exchange elasticity & 0.25 & [0.15, 0.35] & \citet{fehr1998reciprocity} & BBB \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Usage note:} These are population averages. For segment-specific
calibration, use the type distribution in Table \ref{tab:feh-types}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Worked Examples}
\label{sec:feh-examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
\subsection{Example 1: Pricing Fairness in Retail}
%------------------------------------------------------------------------------

\paragraph{Setup.} A retailer considers raising prices after a supply shock.
Standard economics suggests raising prices to market-clearing level.

\paragraph{Application.} Using Fehr-Schmidt parameters:
\begin{itemize}[nosep]
    \item Customers with $\alpha > 0$ perceive price increase as ``unfair''
          (retailer gains at their expense)
    \item Loss aversion amplifies: price increase feels like a loss
    \item Expected backlash: reduced purchases, negative word-of-mouth
\end{itemize}

\paragraph{Result.} \citet{kahneman1986fairness} (with Fehr's framework)
show that ``unfair'' price increases reduce demand beyond standard elasticity.

\paragraph{Practical Implication.} Frame price increases as cost pass-through,
not profit-taking. Timing matters: increase prices when competitors do.

%------------------------------------------------------------------------------
\subsection{Example 2: Public Goods with Punishment}
%------------------------------------------------------------------------------

\paragraph{Setup.} A team faces a free-rider problem. Without intervention,
cooperation decays to 20-40\%.

\paragraph{Application.} Introduce costly peer punishment option (Fehr's
public goods game with punishment):
\begin{itemize}[nosep]
    \item Strong reciprocators (10-30\%) punish free-riders
    \item Free-riders increase contributions to avoid punishment
    \item Cooperation stabilizes at 80-95\%
\end{itemize}

\paragraph{Result.} The punishment mechanism leverages preference heterogeneity---a
minority of strong reciprocators disciplines the entire group.

\paragraph{Practical Implication.} Design peer feedback systems; make non-contribution
visible; enable low-cost ``punishment'' (social disapproval).


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implications for Practice}
\label{sec:feh-practice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[colback=green!5!white, colframe=green!75!black,
    title=Practical Implications from Fehr's Research]

\textbf{1. Fairness Matters for Compliance}
\begin{itemize}[nosep]
    \item People reject ``unfair'' offers even at personal cost
    \item Frame policies as fair (procedural \& distributive justice)
    \item Anticipate resistance to perceived exploitation
\end{itemize}

\textbf{2. Leverage Heterogeneity}
\begin{itemize}[nosep]
    \item Not everyone is selfish---design for the cooperative majority
    \item Identify and empower ``strong reciprocators'' as norm enforcers
    \item Segment interventions by preference type
\end{itemize}

\textbf{3. Context is Manipulable}
\begin{itemize}[nosep]
    \item Professional vs. personal identity affects behavior
    \item Institutional framing (market vs. community) shifts norms
    \item Use $\Psi$-interventions to activate cooperative mindsets
\end{itemize}

\textbf{4. Reciprocity as Intervention Tool}
\begin{itemize}[nosep]
    \item ``Gifts'' (above-minimum wages, unexpected bonuses) elicit reciprocity
    \item Sequence matters: give first, then ask
    \item Personalize gifts for stronger effect
\end{itemize}

\textbf{5. Combine Mechanisms (Complementarity)}
\begin{itemize}[nosep]
    \item Trust + contracts > either alone
    \item Repetition + competition = super-additive cooperation
    \item Bundle interventions for multiplicative effects
\end{itemize}

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Paper Bibliography}
\label{sec:feh-papers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Integration Statistics}

\begin{table}[htbp]
\centering
\caption{Fehr Paper Integration Summary}
\label{tab:feh-integration}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Category} & \textbf{Count} \\
\midrule
Total publications & 343 \\
Integrated in EBF & 144 \\
Not integrated & 199 \\
Integration rate & 42\% \\
\midrule
\multicolumn{2}{@{}l}{\textit{Non-integrated by category:}} \\
\quad Neuroeconomics & 42 \\
\quad Pure Methodology & 18 \\
\quad German Language & 31 \\
\quad Working Papers (superseded) & 47 \\
\quad Narrow Domain & 36 \\
\quad Book Chapters/Reviews & 25 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Key Integrated Papers}

\begin{enumerate}
    \item \textbf{Fehr \& Schmidt (1999)} ``A Theory of Fairness, Competition,
          and Cooperation'' \textit{QJE}. \textbf{Citations:} 19,000+.
          \textbf{EBF use:} Foundation for $\alpha$, $\beta$ parameters.

    \item \textbf{Fehr, Fischbacher, \& Gächter (2002)} ``Strong Reciprocity,
          Human Cooperation, and the Enforcement of Social Norms''
          \textit{Human Nature}. \textbf{EBF use:} Strong reciprocity theory.

    \item \textbf{Fehr \& Gächter (1998)} ``Reciprocity and Economics''
          \textit{EER}. \textbf{EBF use:} Gift exchange parameters.

    \item \textbf{Efferson, Fehr et al. (2024)} ``Super-additive Cooperation''
          \textit{Nature}. \textbf{EBF use:} Complementarity evidence.

    \item \textbf{Fehr \& Charness (2025)} ``Social Preferences: Fundamental
          Characteristics'' \textit{JEL}. \textbf{EBF use:} Updated type distribution.
\end{enumerate}

\subsection{Non-Integrated Papers: Rationale}

Papers not integrated into EBF fall into defined categories:

\begin{tcolorbox}[colback=gray!5!white, colframe=gray!75!black,
    title=Neuroeconomics (42 papers) --- Outside EBF Scope]
\textbf{Example:} ``The Neural Basis of Altruistic Punishment'' (Science 2004)

\textbf{Rationale:} fMRI studies provide neural correlates but not extractable
behavioral parameters. Neuroeconomics is a separate domain from behavioral
economics as implemented in EBF.

\textbf{Reconsider if:} Neuroeconomics domain added to EBF.
\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% === AUTO-GENERATED ENTRIES (2026-02-22) ===

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2009: The Biology of Trust and Cooperation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2009). ``The Biology of Trust and Cooperation.'' \textit{Journal of the European Economic Association}, 7, 235--266.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: Social Norms and Human Cooperation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Fischbacher, Urs (2004). ``Social Norms and Human Cooperation.'' \textit{Trends in Cognitive Sciences}, 8, 185--190.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2009: On the Economics and Biology of Trust}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2009). ``On the Economics and Biology of Trust.'' \textit{Journal of the European Economic Association}, 7, 235--266.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2018: Computational and Neurobiological Foundations of Leadership ...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Edelson, Micah G and Polania, Rafael and Ruff, Christian C and Fehr, Ernst and Hare, Todd A (2018). ``Computational and Neurobiological Foundations of Leadership Decisions.'' \textit{Science}, 361, eaat0036.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-WHO, DOMAIN-ORG, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2024: Viewing Inequality Through the Lens of Inequity Aversion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Epper, Thomas and Fehr, Ernst and Senn, Julien (2024). ``Viewing Inequality Through the Lens of Inequity Aversion.'' \textit{Proceedings of the National Academy of Sciences}, 121, e2317916121.

\paragraph{Key Parameters.}
\texttt{alpha = 0.85, beta = 0.45}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-WHAT, DOMAIN-POL, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2025: How Beliefs About Others Explain Redistribution Preferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Henkel, Luca and Sprenger, Jana and Fehr, Ernst (2025). ``How Beliefs About Others Explain Redistribution Preferences.'' \textit{Journal of Public Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-WHAT, DOMAIN-POL, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2022: Preferences Predict Who Commits Crime Among Young Men}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Epper, Thomas and Fehr, Ernst and Fehr-Duda, Helga and Kreiner, Claus T and Lassen, David D and Leth-Petersen, S{\o}ren and Rasmussen, Gregers N (2022). ``Preferences Predict Who Commits Crime Among Young Men.'' \textit{Proceedings of the National Academy of Sciences}, 119, e2112645119.

\paragraph{Key Parameters.}
\texttt{beta_crime = 0.78, risk_tolerance_effect = 1.4}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-READY, LIT-FEH, LIT-FEHR, PREDICT-CRIME
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2002: Psychological Foundations of Incentives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Falk, Armin (2002). ``Psychological Foundations of Incentives.'' \textit{European Economic Review}, 46, 687--724.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-HOW, CORE-WHAT, LIT-FALK, LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Limited Rationality and Strategic Interaction: The Impact of...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Tyran, Jean-Robert (2008). ``Limited Rationality and Strategic Interaction: The Impact of the Strategic Environment on Nominal Inertia.'' \textit{Econometrica}, 76, 353--394.

\paragraph{Key Parameters.}
\texttt{nominal_illusion_effect = 0.35}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-HOW, DOMAIN-MONETARY, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2022: Global Variation in Human Self-Control}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Schunk, Daniel and Fehr, Ernst and others (2022). ``Global Variation in Human Self-Control.'' \textit{Nature Human Behaviour}, 6, 76--91.

\paragraph{Key Parameters.}
\texttt{global_selfcontrol_mean = 3.2, cultural_variance = 0.8}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-AWARE, CORE-READY, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2007: Social Neuroeconomics: The Neural Circuitry of Social Prefer...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Camerer, Colin F (2007). ``Social Neuroeconomics: The Neural Circuitry of Social Preferences.'' \textit{Trends in Cognitive Sciences}, 11, 419--427.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2003: The Nature of Human Altruism}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Fischbacher, Urs (2003). ``The Nature of Human Altruism.'' \textit{Nature}, 425, 785--791.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2011: Neuroeconomic Foundations of Economic Choice---Recent Advanc...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Rangel, Antonio (2011). ``Neuroeconomic Foundations of Economic Choice---Recent Advances.'' \textit{Journal of Economic Perspectives}, 25, 3--30.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: Third-Party Punishment and Social Norms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Fischbacher, Urs (2004). ``Third-Party Punishment and Social Norms.'' \textit{Evolution and Human Behavior}, 25, 63--87.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2002: Cooperation and the Enforcement of High Efficiency Standards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2002). ``Cooperation and the Enforcement of High Efficiency Standards.'' \textit{Journal of Political Economy}, 110, 817--838.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2018: Narratives, Imperatives, and Moral Reasoning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Roland Bénabou and Armin Falk and Jean Tirole (2018). ``Narratives, Imperatives, and Moral Reasoning.'' \textit{NBER Working Paper}.

\paragraph{Core Finding.}
Key paper on moral narratives. Co-authored with Armin Falk (Fehr collaborator). Extends Benabou-Tirole 2006/2011 framework.

\paragraph{Key Parameters.}
\texttt{mu = image_concern; beta = self_control in [0.7, 1.0]; rho = network_persistence in [0, 1]}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-BENABOU, LIT-FEHR, CORE-AWARE, CORE-HOW, DOMAIN-SOCIAL, LIT-FALK, LIT-TIROLE
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2002: Altruism and Incentives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Falk, Armin and Fehr, Ernst (2002). ``Altruism and Incentives.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-HOW, LIT-FALK, LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1992: Cooperation and Punishment in Public Goods Games}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (1992). ``Cooperation and Punishment in Public Goods Games.'' \textit{American Economic Review}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1993: Does Fairness Prevent Market Clearing?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (1993). ``Does Fairness Prevent Market Clearing?.'' \textit{Quarterly Journal of Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1994: Cooperative Behavior Declines in Succeeding Periods of Publi...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (1994). ``Cooperative Behavior Declines in Succeeding Periods of Public Goods Games.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1994: Costly Punishment Sustains Cooperation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (1994). ``Costly Punishment Sustains Cooperation.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1995: Evolution of Fairness Preferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (1995). ``Evolution of Fairness Preferences.'' \textit{Proceedings of the National Academy of Sciences}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1995: Inequality Aversion Explains Much of Human Altruism}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Schmidt, Klaus M. (1995). ``Inequality Aversion Explains Much of Human Altruism.'' \textit{American Economic Review}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1996: Norm Enforcement with Decentralized Sanctioning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (1996). ``Norm Enforcement with Decentralized Sanctioning.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1996: Voluntary Provision of a Public Good}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (1996). ``Voluntary Provision of a Public Good.'' \textit{Experimental Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1997: Origins of Reciprocal Preferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (1997). ``Origins of Reciprocal Preferences.'' \textit{Evolution and Human Behavior}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1997: The Long-Run Problem of the Tragedy of the Commons}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (1997). ``The Long-Run Problem of the Tragedy of the Commons.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1998: Efficiency and Fairness in Collective Decision-Making}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (1998). ``Efficiency and Fairness in Collective Decision-Making.'' \textit{Journal of Economic Literature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1998: Informal Sanctions and Norm Violations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (1998). ``Informal Sanctions and Norm Violations.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1999: The Evolution of Cooperation and Punishment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (1999). ``The Evolution of Cooperation and Punishment.'' \textit{Proceedings of the Royal Society B}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{1999: Voting for Redistribution Policies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (1999). ``Voting for Redistribution Policies.'' \textit{Journal of Public Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2000: Behavioral Decision-Making in Economics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Fischbacher, Urs (2000). ``Behavioral Decision-Making in Economics.'' \textit{Journal of Economic Literature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2000: Fairness and Retaliation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2000). ``Fairness and Retaliation.'' \textit{null}, null.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2000: Patterns of Punishment in Community Enforcement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2000). ``Patterns of Punishment in Community Enforcement.'' \textit{Handbook of Experimental Economics Results}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2000: Fairness and Rent-Seeking: The Impact of Inequality on Econo...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (2000). ``Fairness and Rent-Seeking: The Impact of Inequality on Economic Behavior.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2001: Cultural Evolution of Cooperative Norms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2001). ``Cultural Evolution of Cooperative Norms.'' \textit{Journal of Theoretical Biology}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2001: Group Formation and Cooperation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2001). ``Group Formation and Cooperation.'' \textit{Handbook of Experimental Results}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2001: Inequality and Cooperation: Evidence from Labor Markets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2001). ``Inequality and Cooperation: Evidence from Labor Markets.'' \textit{Journal of Labor Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2001: Do Workers Work More if Wages Are High? Evidence from a Rand...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2001). ``Do Workers Work More if Wages Are High? Evidence from a Randomized Experiment.'' \textit{American Economic Review}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2002: Enforcement Problems and the Evolution of Institutions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2002). ``Enforcement Problems and the Evolution of Institutions.'' \textit{Journal of Economic Perspectives}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2002: Theories of Fairness and Reciprocity - Evidence and New Dire...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Schmidt, Klaus M. (2002). ``Theories of Fairness and Reciprocity - Evidence and New Directions.'' \textit{Handbook of Reciprocity: Theory and Practice}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2002: Peer Effects, Social Pressure and Cheating}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (2002). ``Peer Effects, Social Pressure and Cheating.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2003: Detrimental Effects of Sanctions on Human Altruism}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Rockenbach, Bettina (2003). ``Detrimental Effects of Sanctions on Human Altruism.'' \textit{Nature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2003: Unemployment and Wage Fairness}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2003). ``Unemployment and Wage Fairness.'' \textit{Journal of Labor Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2003: Cross-Cultural Variation in Cooperation Norms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2003). ``Cross-Cultural Variation in Cooperation Norms.'' \textit{Journal of Cross-Cultural Psychology}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2003: Wealth and Distributional Preferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2003). ``Wealth and Distributional Preferences.'' \textit{Review of Economic Studies}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2003: When Social Norms Overpower Competition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2003). ``When Social Norms Overpower Competition.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O, CORE-HIERARCHY
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: Social Dilemmas and Cooperation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2004). ``Social Dilemmas and Cooperation.'' \textit{The Handbook of Experimental Economics Results}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: Gift Exchange Contracts and Reciprocity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (2004). ``Gift Exchange Contracts and Reciprocity.'' \textit{Journal of Political Economy}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: The Long-Run Performance of Natural Experiments: Large Sampl...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (2004). ``The Long-Run Performance of Natural Experiments: Large Sample Evidence.'' \textit{Review of Economics and Statistics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: Progressive Taxation and Income Redistribution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Schmidt, Klaus M. (2004). ``Progressive Taxation and Income Redistribution.'' \textit{Journal of Public Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2004: Sanctioning Systems for Norm Violation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2004). ``Sanctioning Systems for Norm Violation.'' \textit{Evolution and Human Behavior}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2005: The Economics of Altruistic Punishment and Beyond}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Fischbacher, Urs (2005). ``The Economics of Altruistic Punishment and Beyond.'' \textit{Advances in Economic Analysis \& Policy}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2005: The Long-term Effects of Price Incentives on Trust-Building}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Rockenbach, Bettina (2005). ``The Long-term Effects of Price Incentives on Trust-Building.'' \textit{Experimental Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2005: Wage Rigidities and Job Creation: Theory and Evidence from A...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2005). ``Wage Rigidities and Job Creation: Theory and Evidence from Adjustment Costs.'' \textit{International Economic Review}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2005: Global Commons, Cooperation, and Pollution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2005). ``Global Commons, Cooperation, and Pollution.'' \textit{Journal of Environmental Economics and Management}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2005: Income Inequality and Social Norms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2005). ``Income Inequality and Social Norms.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2005: Selection of Social Preferences in Large Groups}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2005). ``Selection of Social Preferences in Large Groups.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Behavioral Ethics: How People Make Moral Decisions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2006). ``Behavioral Ethics: How People Make Moral Decisions.'' \textit{The Handbook of Experimental Economics Results}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Contracts, Reference Points, and Competition - Behavioral Im...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Klein, Armin and Schmidt, Klaus M. (2006). ``Contracts, Reference Points, and Competition - Behavioral Implications.'' \textit{Review of Economic Studies}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: The Economics of Fairness, Reciprocity and Altruism - Experi...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Schmidt, Klaus M. (2006). ``The Economics of Fairness, Reciprocity and Altruism - Experimental Evidence and New Theories.'' \textit{Journal}, 1, 615--691.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-WHAT, LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: When Social Norms Overpower Competition: Camp Participation ...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2006). ``When Social Norms Overpower Competition: Camp Participation Among East German Children after Reunification.'' \textit{Journal of the European Economic Association}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Leadership and Cooperation in Public Goods Games}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2006). ``Leadership and Cooperation in Public Goods Games.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Moral Strength}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Rockenbach, Bettina (2006). ``Moral Strength.'' \textit{Journal of Economic Literature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Behavioral Policy Design: When to Nudge and When to Boost}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2006). ``Behavioral Policy Design: When to Nudge and When to Boost.'' \textit{Journal of Policy Analysis and Management}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Status Quo Bias and Inequality Aversion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2006). ``Status Quo Bias and Inequality Aversion.'' \textit{Experimental Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2006: Third-Party Punishment and Norm Enforcement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2006). ``Third-Party Punishment and Norm Enforcement.'' \textit{Journal of Experimental Social Psychology}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2007: Contracting for Motivation and Trust}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Schmidt, Klaus M. (2007). ``Contracting for Motivation and Trust.'' \textit{Journal of Economic Psychology}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2007: Intrinsic Motivation and Extrinsic Incentives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2007). ``Intrinsic Motivation and Extrinsic Incentives.'' \textit{Handbook of the Economics of Giving, Altruism and Reciprocity}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2007: Social Neuroeconomics: Agents, Behaviors, and Brains}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Camerer, Colin F. (2007). ``Social Neuroeconomics: Agents, Behaviors, and Brains.'' \textit{Journal of Economic Literature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2007: Poverty and Fairness Preferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2007). ``Poverty and Fairness Preferences.'' \textit{Journal of Development Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2007: How Effective is Trust-Based Management?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2007). ``How Effective is Trust-Based Management?.'' \textit{The Handbook of Experimental Economics Results}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Behavioral Economics of Work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2008). ``Behavioral Economics of Work.'' \textit{Annual Review of Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Implementation of Behavioral Economic Policies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2008). ``Implementation of Behavioral Economic Policies.'' \textit{Handbook of Implementation Science}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Who Behaves Selfishly, and Why? Evidence from Salaried and P...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2008). ``Who Behaves Selfishly, and Why? Evidence from Salaried and Piece-Rate Workers.'' \textit{Econometrica}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Redistribution, Voting, and Inequality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2008). ``Redistribution, Voting, and Inequality.'' \textit{Review of Economic Studies}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Cooperation at the Scale of Large Groups}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2008). ``Cooperation at the Scale of Large Groups.'' \textit{Nature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2008: Behaviorally-Dependent Labor Supply: You Get What You Pay Fo...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon and Kirchsteiger, Georg (2008). ``Behaviorally-Dependent Labor Supply: You Get What You Pay For.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2009: Competition and Cooperation in Firms}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2009). ``Competition and Cooperation in Firms.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2009: Behavioral Approaches to Environmental Protection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2009). ``Behavioral Approaches to Environmental Protection.'' \textit{Environmental Science \& Technology}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2009: Cooperation and the Removal of Monitoring Systems - Long-Run...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Rockenbach, Bettina (2009). ``Cooperation and the Removal of Monitoring Systems - Long-Run Lessons from the Laboratory.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2009: Fairness and Contract Design}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Klein, Armin and Schmidt, Klaus M. (2009). ``Fairness and Contract Design.'' \textit{Econometrica}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2010: Altruism 3.0: Addressing the Gendered Dimensions of Altruism}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Fischbacher, Urs (2010). ``Altruism 3.0: Addressing the Gendered Dimensions of Altruism.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2010: The Impact of Organizational Structure and Process on Outcom...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2010). ``The Impact of Organizational Structure and Process on Outcomes.'' \textit{Strategic Management Journal}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2010: Behavioral Economics of Health Decisions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2010). ``Behavioral Economics of Health Decisions.'' \textit{Health Affairs}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2010: Perspective on Future Behavioral Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2010). ``Perspective on Future Behavioral Research.'' \textit{Science}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2010: Reciprocity and Market Integration - Did Smithian Thinking F...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2010). ``Reciprocity and Market Integration - Did Smithian Thinking Fail?.'' \textit{Journal of Economic Perspectives}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2011: Behavioral Economics of Education Incentives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2011). ``Behavioral Economics of Education Incentives.'' \textit{Journal of Human Capital}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2011: Human Behavior and the Economics of Incentives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2011). ``Human Behavior and the Economics of Incentives.'' \textit{Annual Review of Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2011: Market Experiences and Attitude Toward Markets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2011). ``Market Experiences and Attitude Toward Markets.'' \textit{Journal of Economic Perspectives}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2011: Overview of Behavioral Economics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2011). ``Overview of Behavioral Economics.'' \textit{Journal of Economic Literature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2011: The Evolution of Costly Punishment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2011). ``The Evolution of Costly Punishment.'' \textit{Evolution and Human Behavior}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2012: Designing for Behavioral Change: Lessons from Economics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2012). ``Designing for Behavioral Change: Lessons from Economics.'' \textit{Journal of Economic Psychology}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2012: Fairness and the Principle of Pareto Efficiency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2012). ``Fairness and the Principle of Pareto Efficiency.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2012: Do People Care About Efficiency? Time Perspective and Indivi...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2012). ``Do People Care About Efficiency? Time Perspective and Individual Differences in Reciprocity.'' \textit{Review of Economic Studies}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2012: Summary of Major Behavioral Findings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2012). ``Summary of Major Behavioral Findings.'' \textit{Handbook of Experimental Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2012: The Economics of Work and of Other Lessons}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2012). ``The Economics of Work and of Other Lessons.'' \textit{Handbook of Organizational Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2013: The Lure of Authority: Motivation and Incentive Effects of P...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Herz, Holger and Wilkening, Tom (2013). ``The Lure of Authority: Motivation and Incentive Effects of Power.'' \textit{American Economic Review}, 103, 1325--1359.

\paragraph{Core Finding.}
Published in AER 2013 (Top-5). Previously UBS Center Working Paper No. 2 (2012). Key findings: (1) Under-delegation: 35-43% retain authority in HIGH/PHIGH despite delegation being materially optimal - formal authority has intrinsic value. (2) Over-effort: controlling parties provide 10-15 units above Nash Equilibrium - authority motivates effort beyond material incentives. (3) Subordinate shirking: 30-50% provide zero effort despite positive incentives - lack of authority demotivates. (4) Overru...

\paragraph{Key Parameters.}
\texttt{underdelegation rate = 35-43% (vs 100% predicted); controlling party over-effort = +10-15 units above NE; subordinate zero-effort = 30-50%; overruling reduces delegation by 20-25pp; welfare loss from underdelegation = 30% in PHIGH; regret aversion explains all three deviations}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-WHO, CORE-WHERE, DOMAIN-ORG, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2024: The Complementarity Between Trust and Contract Enforcement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Bartling, Bj{\"o}rn and Fehr, Ernst and Huffman, David and Netzer, Nick (2024). ``The Complementarity Between Trust and Contract Enforcement.'' \textit{Journal}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-HOW, CORE-WHEN, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2013: Behavioral Insights into Policy Design}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2013). ``Behavioral Insights into Policy Design.'' \textit{Policy Studies Journal}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2013: Implicit Fairness Preferences}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2013). ``Implicit Fairness Preferences.'' \textit{Judgment and Decision Making}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2013: Gifts and Wages: Behavioural Reactions to Reciprocity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2013). ``Gifts and Wages: Behavioural Reactions to Reciprocity.'' \textit{Journal of Economic Perspectives}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2013: Reciprocal Fairness and Group Formation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Rockenbach, Bettina (2013). ``Reciprocal Fairness and Group Formation.'' \textit{Journal of Economic Behavior \& Organization}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2013: Review of Two Decades of Behavioral Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2013). ``Review of Two Decades of Behavioral Research.'' \textit{Journal of Economic Literature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2014: The Evolution of Altruism and Punishment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2014). ``The Evolution of Altruism and Punishment.'' \textit{Nature Human Behaviour}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2014: The Economics of Impatience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2014). ``The Economics of Impatience.'' \textit{Journal of Economic Perspectives}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2014: The Future of Behavioral Economics in Policy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2014). ``The Future of Behavioral Economics in Policy.'' \textit{Nature Human Behaviour}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2014: Return Reciprocity and Preference for the Equal Distribution...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst (2014). ``Return Reciprocity and Preference for the Equal Distribution of Resources.'' \textit{Experimental Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2014: Synthesis of Behavioral Economics Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2014). ``Synthesis of Behavioral Economics Research.'' \textit{Annual Review of Economics}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2015: Cultural Variations in Altruistic Punishment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2015). ``Cultural Variations in Altruistic Punishment.'' \textit{Science}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2015: Normative Motivation in Economics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2015). ``Normative Motivation in Economics.'' \textit{Nature}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2015: The Role of Reciprocity in Economics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Fehr, Ernst and Gächter, Simon (2015). ``The Role of Reciprocity in Economics.'' \textit{Nature Human Behaviour}.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-FEH, LIT-FEHR, LIT-O
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2025: Beliefs about Inequality and the Nature of Support for Redis...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Henkel, Aljosha and Fehr, Ernst and Senn, Julien and Epper, Thomas (2025). ``Beliefs about Inequality and the Nature of Support for Redistribution.'' \textit{Journal of Public Economics}, 246, 105350.

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: CORE-WHAT, DOMAIN-POL, LIT-FEH, LIT-FEHR
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2024: Ends versus Means: Kantians, Utilitarians, and Moral Decisio...}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Citation.}
Roland Bénabou and Armin Falk and Luca Henkel (2024). ``Ends versus Means: Kantians, Utilitarians, and Moral Decisions.'' \textit{Journal}.

\paragraph{Core Finding.}
Key contribution: No stable moral types - cross-context correlations near zero. EVM orthogonal to prosociality. Context determines moral reasoning theta, not stable type. Level 4 THEORY integration.

\paragraph{Key Parameters.}
\texttt{theta_lying = deontological_rate_lying = 0.44 [0.39, 0.49];
    theta_bribe = deontological_rate_bribe = 0.38 [0.33, 0.43];
    theta_statement = deontological_rate_statement = 0.28 [0.23, 0.33];
    theta_group = deontological_rate_group = 0.20 [0.16, 0.24];
    r_EVM = cross_evm_correlation = 0.035 [-0.02, 0.09];
    r_EVM_pro = evm_prosocial_correlation = 0.025 [-0.03, 0.08]}

\paragraph{10C Integration.}
\begin{itemize}[nosep]
  \item \textbf{Domain}: [To be specified]
  \item \textbf{use\_for}: LIT-BENABOU, LIT-FEHR, CORE-AWARE, CORE-WHEN, CORE-WHAT, DOMAIN-MORAL, CORE-HOW
\end{itemize}

% === END AUTO-GENERATED ENTRIES ===
\section{Summary}
\label{sec:feh-summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[colback=green!10!white, colframe=green!75!black,
    title=\textbf{Appendix UNMAPPED_FEH: Summary}]

\textbf{Core Question:} How do Ernst Fehr's contributions enable behavioral
economics in EBF?

\textbf{Main Contribution:}
\begin{itemize}[nosep]
    \item Established social preferences as measurable utility components
    \item Provided calibrated parameters ($\alpha=0.85$, $\beta=0.315$)
    \item Documented population heterogeneity in preferences
    \item Demonstrated complementarity in cooperation mechanisms
\end{itemize}

\textbf{Key Outputs:}
\begin{itemize}[nosep]
    \item 6 extractable parameters with confidence intervals
    \item 4-type population distribution for segmentation
    \item 2 worked examples for practitioner application
    \item 144 integrated papers with evaluation rationale
\end{itemize}

\textbf{Integration:} This appendix connects to C (CORE-WHAT), B (CORE-HOW),
V (CORE-WHEN), AAA (CORE-WHO), and BBB (CORE-WHERE) via parameter calibration
and theoretical foundations.

\end{tcolorbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Glossary of Symbols}
\label{sec:feh-glossary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black]
\textbf{Central Reference:} For complete symbol definitions, see
\textbf{Appendix UNMAPPED_GLS} (Glossary and Notation).
\end{tcolorbox}

\begin{table}[htbp]
\centering
\caption{Symbols in Appendix UNMAPPED_FEH}
\label{tab:feh-symbols}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}clp{6cm}c@{}}
\toprule
\textbf{Symbol} & \textbf{Name} & \textbf{Definition} & \textbf{In GLS?} \\
\midrule
$\alpha$ & Disadvantageous IA & Sensitivity to being behind others & \checkmark \\
$\beta$ & Advantageous IA & Sensitivity to being ahead of others & \checkmark \\
$U^S$ & Social Utility & Utility from others' outcomes & \checkmark \\
$\gamma$ & Complementarity & Interaction effect between mechanisms & \checkmark \\
$\Psi$ & Context vector & Context dimensions affecting behavior & \checkmark \\
\bottomrule
\end{tabular}
\end{table}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Critical Foundations}
\label{sec:feh-foundations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following foundational elements underpin Fehr's contributions to EBF:

\begin{enumerate}
    \item \textbf{Methodological Foundation:} The use of incentive-compatible
    laboratory experiments with real monetary stakes, establishing behavioral
    economics as an empirical science (1990s experimental revolution).

    \item \textbf{Theoretical Foundation:} The Fehr-Schmidt utility function
    extends classical expected utility by adding social comparison terms,
    maintaining tractability while explaining cooperation puzzles.

    \item \textbf{Empirical Foundation:} Meta-analyses of 100+ ultimatum game
    studies provide stable parameter estimates ($\alpha$, $\beta$) across cultures.

    \item \textbf{Policy Foundation:} Gift exchange findings inform efficiency
    wage theory and fair wage policies in organizational economics.

    \item \textbf{EBF Integration:} Parameters from Fehr's work populate
    Appendix UNMAPPED_BBB (CORE-WHERE) and calibrate models in Appendix UNMAPPED_C (CORE-WHAT).
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Issues}
\label{sec:feh-open-issues}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following issues remain unresolved and represent areas for future research:

\begin{itemize}
    \item \textbf{OI-1 (Cross-cultural Stability):} While $\alpha$ and $\beta$
    estimates are robust in WEIRD populations, systematic variation across
    non-WEIRD cultures requires further validation (see Appendix UNMAPPED_BJ).

    \item \textbf{OI-2 (Dynamic Preferences):} How do social preferences evolve
    over the life course? Integration with Sutter's developmental research needed.

    \item \textbf{OI-3 (Neural Mechanisms):} Neuroeconomics papers (not integrated)
    suggest biological substrates, but EBF lacks formal incorporation of neural data.

    \item \textbf{OI-4 (Online Behavior):} Most experiments predate digital
    platforms; social preferences in online contexts remain under-explored.

    \item \textbf{OI-5 (AI Interactions):} How do humans apply fairness norms
    when interacting with AI agents? Emerging research area with EBF implications.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{References}
\label{sec:feh-references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tcolorbox}[colback=blue!5!white, colframe=blue!75!black]
\textbf{Master Bibliography:} For complete reference details, see
\texttt{bcm\_master.bib} in the repository.
\end{tcolorbox}

\subsection{Key References for This Appendix}

\begin{itemize}[nosep]
    \item \textbf{Inequity Aversion:} \citet{fehr1999theory}
    \item \textbf{Strong Reciprocity:} \citet{fehr2002strong, gaechter2002altruistic}
    \item \textbf{Gift Exchange:} \citet{fehr1993reciprocity, fehr1998reciprocity}
    \item \textbf{Context Effects:} \citet{cohn2014business, cohn2015evidence}
    \item \textbf{Recent Synthesis:} \citet{fehr2025social}
\end{itemize}

\subsection{Data Sources}

\begin{itemize}[nosep]
    \item \textbf{Google Scholar Profile:} \url{https://scholar.google.com/citations?user=WoSILroAAAAJ}
    \item \textbf{University of Zurich:} \url{https://www.econ.uzh.ch/en/people/faculty/fehr.html}
    \item \textbf{Research.com Ranking:} \url{https://research.com/u/ernst-fehr}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CROSS-REFERENCE FOOTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{1em}
\hrule
\vspace{0.5em}

\noindent\textit{Cross-references:}
Appendix UNMAPPED_GLS (Central Glossary),
Appendix UNMAPPED_C (CORE-WHAT),
Appendix UNMAPPED_B (CORE-HOW),
Appendix UNMAPPED_V (CORE-WHEN),
Appendix UNMAPPED_BBB (CORE-WHERE),
Appendix UNMAPPED_FRM (LIT-FEHR-METHOD).

\noindent\textit{Registry Reference:} \texttt{data/researcher-registry.yaml} (RES-FEHR-E)

\noindent\textit{Master Bibliography:} \texttt{bcm\_master.bib}

% =============================================================================
% END OF APPENDIX FEH
% =============================================================================
